\begin{longtable}{|c|p{5.2cm}|p{3cm}|p{3cm}|p{8cm}|}
\hline
	\textbf{Year} &
	\textbf{Exhibitor} &
	\textbf{Champion} &
	\textbf{Name} &
	\textbf{Notes} 
	\tabularnewline
\hline
\endhead
	$1982$ &
	\raggedright S. Bain \& Co, Quoyholmslie, Stromness\sindex[exhibitor]{Bain, S. \& Co, Quoyholmslie, Stromness} &
	\raggedright 4yo CH bull &
	\raggedright - &
	\raggedright Bought at Perth.
	\tabularnewline
\hline
	$1983$ &
	\multicolumn{4}{c|}{No entries forward.}
	\tabularnewline
\hline
	$1984$ &
	\raggedright G. T. \& S. Coghill, Muce, Birsay\sindex[exhibitor]{Coghill, G. T. \& S., Muce, Birsay} &
	\raggedright CH calf &
	\raggedright Hekra Vera\sindex[beef]{Hekra Vera} &
	\raggedright By Tottenhall Hublo, out of Acton Oenone; born 1/4/1984.
	\tabularnewline
\hline
	$1985$ &
	\raggedright J. \& S. Hay, East Howe, Birsay\sindex[exhibitor]{Hay, J. \& S., East Howe, Birsay} &
	\raggedright CH bull &
	\raggedright Blelack Unique\sindex[beef]{Blelack Unique} &
	\raggedright By Fairweather Robspier, out of Blelack cow.
	\tabularnewline
\hline
	$1986$ &
	\raggedright W. G. Kirkpatrick \& Sons, Newhall, Stromness\sindex[exhibitor]{Kirkpatrick, W. G. \& Sons, Newhall, Stromnes} &
	\raggedright CH bull &
	\raggedright Ballieston Universe\sindex[beef]{Ballieston Universe} &
	\raggedright By Wincote Jasper, out of Sway Ninette; bred by W. R. Baillie, Biggings, Toab; sire was supreme champion at 1978 \& 1982 County Show.
	\tabularnewline
\hline
	$1987$ &
	\raggedright G. T. \& S. Coghill, Muce, Birsay\sindex[exhibitor]{Coghill, G. T. \& S., Muce, Birsay} &
	\raggedright 3yo CH cow &
	\raggedright Cirrus Vanda\sindex[beef]{Cirrus Vanda} &
	\raggedright By Scottish Mercury; bought at Perth in February 1987.
	\tabularnewline
\hline
	$1988$ &
	\raggedright G. T. \& S. Coghill, Muce, Birsay\sindex[exhibitor]{Coghill, G. T. \& S., Muce, Birsay} &
	\raggedright CH heifer in calf &
	\raggedright Hekra Buanco\sindex[beef]{Hekra Buanco} &
	\raggedright By Bowerhouse Topper, out of Mornview Tamar.
	\tabularnewline
\hline
	$1989$ &
	\raggedright Messrs Davidson, Skaill Farm, Sandwick\sindex[exhibitor]{Davidson, Messrs, Skaill Farm, Sandwick} &
	\raggedright - &
	\raggedright - &
	\raggedright -
	\tabularnewline
\hline
	$1990$ &
	\raggedright D. W. Sinclair \& Co, Unigarth, Sandwick\sindex[exhibitor]{Sinclair, D. W. \& Co, Unigarth, Sandwick} &
	\raggedright 2yo CH bull &
	\raggedright Royston Democrat\sindex[beef]{Royston Democrat} &
	\raggedright By Glenleary Attenhall.
	\tabularnewline
\hline
	$1991$ &
	\raggedright J. \& N. Isbister, New Moan, Harray\sindex[exhibitor]{Isbister, J. \& N., New Moan, Harray} &
	\raggedright CH heifer calf* &
	\raggedright New Moan Goldie\sindex[beef]{New Moan Goldie} &
	\raggedright By Balthalock Dalesman, out of Brampton Victoria.
	\tabularnewline
\hline
	$1992$ &
	\raggedright I. R. Scott, Howe, Harray\sindex[exhibitor]{Scott, I. R., Howe, Harray} &
	\raggedright 8yo SM cow in calf &
	\raggedright Hockenhull Pauline\sindex[beef]{Hockenhull Pauline} &
	\raggedright Bought at Perth.
	\tabularnewline
\hline
	$1993$ &
	\raggedright S. \& F. Nicolson, Stenaday, Harray\sindex[exhibitor]{Nicolson, S. \& F., Stenaday, Harray} &
	\raggedright 2yo LM heifer in calf &
	\raggedright Mountrock Golden\sindex[beef]{Mountrock Golden} &
	\multirow{2}{8cm}{By Dali, out of Mountrock Bessie.}
	\tabularnewline
\cline{1-4}
	$1994$ &
	\raggedright S. \& F. Nicolson, Stenaday, Harray\sindex[exhibitor]{Nicolson, S. \& F., Stenaday, Harray} &
	\raggedright 3yo LM cow &
	\raggedright Mountrock Golden\sindex[beef]{Mountrock Golden} &
	\tabularnewline
\hline
	$1995$ &
	\raggedright Garson Farms, Sandwick\sindex[exhibitor]{Garson Farms, Sandwick} &
	\raggedright 2yo CH heifer in calf* &
	\raggedright Garson Isla\sindex[beef]{Garson Isla} &
	\raggedright By Brampton Consort, out of Gredington Caniche.
	\tabularnewline
\hline
	$1996$ &
	\raggedright Garson Farms, Sandwick\sindex[exhibitor]{Garson Farms, Sandwick} &
	\raggedright 3yo CH bull* &
	\raggedright Garson Impression\sindex[beef]{Garson Impression} &
	\raggedright By Brampton Ace, out of Gredington Francesca.
	\tabularnewline
\hline
	$1997$ &
	\raggedright G. T. \& S. Coghill, Muce, Birsay\sindex[exhibitor]{Coghill, G. T. \& S., Muce, Birsay} &
	\raggedright 2yo LM heifer in calf &
	\raggedright Holly Little Gem\sindex[beef]{Holly Little Gem} &
	\raggedright By Hartside Glen, out of Holly Topas.
	\tabularnewline
\hline
	$1998$ &
	\raggedright G. T. \& S. Coghill, Muce, Birsay\sindex[exhibitor]{Coghill, G. T. \& S., Muce, Birsay} &
	\raggedright 5yo CH cow &
	\raggedright New Moan Iris\sindex[beef]{New Moan Iris} &
	\raggedright By Balthayoak Dalesman, out of New Moan Emma; bought from Jim Isbister, New Moan, Harray in October 1997; supreme champion in 1998.
	\tabularnewline
\hline
	$1999$ &
	\raggedright L. Muir, Midhouse, Harray\sindex[exhibitor]{Muir, L., Midhouse, Harray} &
	\raggedright 7yo LM cow &
	\raggedright Poplars Heidi\sindex[beef]{Poplars Heidi} &
	\raggedright By Galbinny Ethan, out of Cowbridge Beauty; bred by Mrs R. Keeling, Poplars Farm, North Stowmarket, Suffolk; bought at annual LM sale, Carlisle, May 1999; supreme champion in 1999.
	\tabularnewline
\hline
	$2000$ &
	\raggedright G. T. \& S. Coghill, Muce, Birsay\sindex[exhibitor]{Coghill, G. T. \& S., Muce, Birsay} &
	\raggedright 7yo CH cow &
	\raggedright New Moan Iris\sindex[beef]{New Moan Iris} &
	\raggedright By Balthayoak Dalesman, out of New Moan Emma; bought from Jim Isbister, New Moan, Harray in October 1997; supreme champion in 1998.
	\tabularnewline
\hline
	$2001$ &
	\multicolumn{4}{c|}{No show due to Foot \& Mouth outbreak.}
	\tabularnewline
\hline
	$2002$ &
	\raggedright L. Spence, Spengar, Sandwick\sindex[exhibitor]{Spence, L., Spengar, Sandwick} &
	\raggedright 1yo CH bull* &
	\raggedright Spengar Sambhar\sindex[beef]{Spengar Sambhar} &
	\raggedright By Brampton Four-Star, out of Mortimer's Lauren; born April 2001.
	\tabularnewline
\hline
	$2003$ &
	\raggedright Garson Farms, Sandwick\sindex[exhibitor]{Garson Farms, Sandwick} &
	\raggedright 1yo CH heifer &
	\raggedright Airdlin Treasure\sindex[beef]{Airdlin Treasure} &
	\raggedright By Airdlin Ploughman, out of Maerdy Limpet; bought at Perth February 2003.
	\tabularnewline
\hline
	$2004$ &
	\raggedright R. J. Taylor, Brencherhouse, Birsay\sindex[exhibitor]{Taylor, R. J., Brencherhouse, Birsay} &
	\raggedright $3\frac{1}{2}$yo LM cow &
	\raggedright Elrick Saffron\sindex[beef]{Elrick Saffron} &
	\raggedright By Rydale Paragon, out of an Elrick cow; bre by Michael Massie.
	\tabularnewline
\hline
	$2005$ &
	\raggedright G. \& C. Flett, Leary, Birsay\sindex[exhibitor]{Flett, G. \& C., Leary, Birsay} &
	\raggedright 10mo LM heifer calf* &
	\raggedright Leary Velvet\sindex[beef]{Leary Velvet} &
	\raggedright By Middledale Perfectionist, out of Leary Randy.
	\tabularnewline
\hline
	$2006$ &
	\raggedright Messrs Davidson, Skaill, Sandwick\sindex[exhibitor]{Davidson, Messrs, Skaill, Sandwick} &
	\raggedright 16mo CH heifer* &
	\raggedright Skaill Abbie\sindex[beef]{Skaill Abbie} &
	\raggedright By Nectragerc, out of Perche; supreme champion, 2006.
	\tabularnewline
\hline
	$2007$ &
	\multicolumn{4}{c|}{No Show due to Foot \& Mouth outbreak.}
	\tabularnewline
\hline
	$2008$ &
	\raggedright  &
	\raggedright  &
	\raggedright  &
	\raggedright 
	\tabularnewline
\hline
	$2009$ &
	\raggedright L. Muir, Midhouse, Harray\sindex[exhibitor]{Muir, L., Midhouse, Harray} &
	\raggedright 16mo LM heifer &
	\raggedright Clarkton Diamond\sindex[beef]{Clarkton Diamond} &
	\raggedright By Ormeb, out of Clarkton Sabrina.
	\tabularnewline
\hline
\end{longtable}
