\begin{longtable}{|c|p{5.2cm}|p{3cm}|p{3cm}|p{8cm}|}
\hline
	\textbf{Year} &
	\textbf{Exhibitor} &
	\textbf{Champion} &
	\textbf{Name} &
	\textbf{Notes} 
	\tabularnewline
\hline
\endhead
	$1980$ &
	\raggedright Mr W. G. Findlay, 10 Warren's Walk, Kirkwall\sindex[exhibitor]{Findlay, Mr W. G., 10 Warren's Walk, Kirkwall} &
	\raggedright 3yo bay filly* &
	\raggedright Dot\sindex[horse]{Dot} &
	\raggedright By Baron Volla; standard Hackney cross; 14.1 hh.
	\tabularnewline
\hline
	$1981$ &
	\raggedright Mr W. G. Findlay, 10 Warren's Walk, Kirkwall\sindex[exhibitor]{Findlay, Mr W. G., 10 Warren's Walk, Kirkwall} &
	\raggedright 4yo bay filly* &
	\raggedright Dotty\sindex[horse]{Dotty} &
	\raggedright 
	\tabularnewline
\hline
	$1982$ &
	\raggedright Mrs D. Wishart, Westquoy, Orphir\sindex[exhibitor]{Wishart, Mrs D., Westquoy, Orphir} &
	\raggedright 4yo filly* &
	\raggedright Westqouy Flower\sindex[horse]{Westqouy Flower} &
	\raggedright By TH stallion Unseen, out of Appaloosa x TH mare Jessia.
	\tabularnewline
\hline
\pagebreak
	$1983$ &
	\raggedright Mrs Rena Paterson, Veltigar, Tankerness\sindex[exhibitor]{Paterson, Mrs Rena, Veltigar, Tankerness} &
	\raggedright 1yo CD filly &
	\raggedright Highfield Maid Marion\sindex[horse]{Highfield Maid Marion} &
	\multirow{5}{8cm}{By Barnahill Ringleader, out of Dykes Heatherbell; bought privately in Banff, June 1983; Champion at 1985 East Mainland show.}
	\tabularnewline
\cline{1-4}
	$1984$ &
	\raggedright Mrs Rena Paterson, Veltigar, Tankerness\sindex[exhibitor]{Paterson, Mrs Rena, Veltigar, Tankerness} &
	\raggedright 2yo CD filly &
	\raggedright Highfield Maid Marion\sindex[horse]{Highfield Maid Marion} &
	\tabularnewline
\cline{1-4}
	$1985$ &
	\raggedright Mrs Rena Paterson, Veltigar, Tankerness\sindex[exhibitor]{Paterson, Mrs Rena, Veltigar, Tankerness} &
	\raggedright 3yo CD filly-in-foal &
	\raggedright Highfield Maid Marion\sindex[horse]{Highfield Maid Marion} &
	\tabularnewline
\cline{1-4}
	$1986$ &
	\raggedright Mrs Rena Paterson, Veltigar, Tankerness\sindex[exhibitor]{Paterson, Mrs Rena, Veltigar, Tankerness} &
	\raggedright 4yo CD yeld mare &
	\raggedright Highfield Maid Marion\sindex[horse]{Highfield Maid Marion} &
	\tabularnewline
\cline{1-4}
	$1987$ &
	\raggedright Mrs Rena Paterson, Veltigar, Tankerness\sindex[exhibitor]{Paterson, Mrs Rena, Veltigar, Tankerness} &
	\raggedright 5yo CD mare &
	\raggedright Highfield Maid Marion\sindex[horse]{Highfield Maid Marion} &
	\tabularnewline
\hline
	$1988$ &
	\raggedright Mrs I. Scott, Roeberry Farm, South Ronaldsay\sindex[exhibitor]{Scott, Mrs I., Roeberry Farm, South Ronaldsay} &
	\raggedright 9yo mare &
	\raggedright Great Flare\sindex[horse]{Great Flare} &
	\raggedright By Bunny Boy, out of Great Girl.
	\tabularnewline
\hline
	$1989$ &
	\raggedright N. Robertson, Shorelands, George St., Kirkwall\sindex[exhibitor]{Robertson, N., Shorelands, George St., Kirkwall} &
	\raggedright 10yo broad mare &
	\raggedright Rosslyn Fairy Ring\sindex[horse]{Rosslyn Fairy Ring} &
	\raggedright By Oakley Eleven Up, out of Mynyddback Fairy.
	\tabularnewline
\hline
	$1990$ &
	\raggedright E. Simpson, Weaverhall, Stromness\sindex[exhibitor]{Simpson, E., Weaverhall, Stromness} &
	\raggedright 7yo &
	\raggedright Kontiki\sindex[horse]{Kontiki} &
	\raggedright By Gainsborough Comet, out of Suzie.
	\tabularnewline
\hline
	$1991$ &
	\raggedright J. S. Baillie, Sebay, Tankerness\sindex[exhibitor]{Baillie, J. S., Sebay, Tankerness} &
	\raggedright 5yo SH yeld &
	\raggedright Fiona of Sebay\sindex[horse]{Fiona of Sebay} &
	\raggedright By Wells Shergar, out Westpark Faith; champion at 1991 East Mainland.
	\tabularnewline
\hline
	$1992$ &
	\raggedright R. Manson, West Clumley, Sandwick\sindex[exhibitor]{Manson, R., West Clumley, Sandwick} &
	\raggedright 1yo CD colt* &
	\raggedright West Clumley Daniel\sindex[horse]{West Clumley Daniel} &
	\multirow{2}{8cm}{By Collissie Benedictine, out of Star Lady Margaret; champion at 1993 Dounby show.}
	\tabularnewline
\cline{1-4}
	$1993$ &
	\raggedright R. Manson, West Clumley, Sandwick\sindex[exhibitor]{Manson, R., West Clumley, Sandwick} &
	\raggedright 2yo CD colt* &
	\raggedright West Clumley Daniel\sindex[horse]{West Clumley Daniel} &
	\tabularnewline
\hline
	$1994$ &
	\raggedright J. S. Baillie, Sebay, Tankerness\sindex[exhibitor]{Baillie, J. S., Sebay, Tankerness} &
	\raggedright 2yo Sh mare* &
	\raggedright Eileen of Sebay\sindex[horse]{Eileen of Sebay} &
	\raggedright By Cullerne Edward, out of Ella of Bayview.
	\tabularnewline
\hline
	$1995$ &
	\raggedright E. Metcalf, Work Farm, St. Ola\sindex[exhibitor]{Metcalf, E., Work Farm, St. Ola} &
	\raggedright 9yo CD mare &
	\raggedright Mill Queen of Rothesay\sindex[horse]{Mill Queen of Rothesay} &
	\raggedright By Ayton Perfection, out of Eskeckraggen Lady Jane; bought in June 1994 at Barnahill sale for top price of £2600; won 11 championships all over Scotland in 1992.
	\tabularnewline
\hline
	$1996$ &
	\raggedright E. A. \& D. Leonard, Park Cottage, Berstane Road, Kirkwall\sindex[exhibitor]{Leonard, E. A. \& D., Park Cottage, Berstane Road, Kirkwall} &
	\raggedright 7yo TH x bay mare &
	\raggedright Millbrex Discovery\sindex[horse]{Millbrex Discovery} &
	\raggedright -
	\tabularnewline
\hline
	$1997$ &
	\raggedright Inga Scott, Braebuster, Deerness\sindex[exhibitor]{Scott, Inga, Braebuster, Deerness} &
	\raggedright 6yo mare &
	\raggedright Kingsford Happy\sindex[horse]{Kingsford Happy} &
	\raggedright By Thornwood Royalist, out of Kingsford Blue Mink; 14.2 hands.
	\tabularnewline
\hline
	$1998$ &
	\raggedright G. \& E. Coltherd, Annfield, Holm\sindex[exhibitor]{Coltherd, G. \& E., Annfield, Holm} &
	\raggedright 4yo CD yield mare &
	\raggedright Roughland M'Lady\sindex[horse]{Roughland M'Lady} &
	\raggedright By Mollen Hillhead, out of Roughlands Queen of Carron.
	\tabularnewline
\hline
	$1999$ &
	\raggedright J. \& M. Slater, Millquoy, Stenness\sindex[exhibitor]{Slater, J. \& M., Millquoy, Stenness} &
	\raggedright 10yo SH mare &
	\raggedright Stow Drummer Girl\sindex[horse]{Stow Drummer Girl} &
	\raggedright By Wells Renown, out of Drum Video; bought in 1996 at Aberdeen sales; champion at 2002 Dounby show.
	\tabularnewline
\hline
	$2000$ &
	\raggedright Diane Walker, Brake House, Stenness\sindex[exhibitor]{Walker, Diane, Brake House, Stenness} &
	\raggedright 4yo x gelding* &
	\raggedright Hooch\sindex[horse]{Hooch} &
	\raggedright By Dutch Warm Blood Secundus, out of Taboo.
	\tabularnewline
\hline
	$2001$ &
	\multicolumn{4}{c|}{No Show due to Foot \& Mouth outbreak.}
	\tabularnewline
\hline
	$2002$ &
	\raggedright J. \& M. Slater, Millquoy, Stenness\sindex[exhibitor]{Slater, J. \& M., Millquoy, Stenness} &
	\raggedright 14yo SH mare &
	\raggedright Stow Drummer Girl\sindex[horse]{Stow Drummer Girl} &
	\raggedright By Wells Renown, out of Drum Video; bought in 1996 at Aberdeen sales; champion at 2002 Dounby show.
	\tabularnewline
\hline
	$2003$ &
	\raggedright J. \& L. Cromarty, Roadside, Toab\sindex[exhibitor]{Cromarty, J. \& L., Roadside, Toab} &
	\raggedright 5yo SH yield mare &
	\raggedright Bayview First Class\sindex[horse]{Bayview First Class} &
	\raggedright By Millhouse First Class, out of Linglass Suzie; champion at 2000(?) East Mainland show.
	\tabularnewline
\hline
	$2004$ &
	\raggedright D. Walker, Bracke House, Stenness\sindex[exhibitor]{Walker, D., Bracke House, Stenness} &
	\raggedright 5yo gelding &
	\raggedright Badger\sindex[horse]{Badger} &
	\raggedright By a Fresian stallion, out of an Irish mare; champion at 2004 Dounby Show.
	\tabularnewline
\hline
	$2005$ &
	\raggedright J. \& M. Slater, Millquoy, Stenness\sindex[exhibitor]{Slater, J. \& M., Millquoy, Stenness} &
	\raggedright 3yo SH filly &
	\raggedright Millquoy Drummies Dawn\sindex[horse]{Millquoy Drummies Dawn} &
	\raggedright -
	\tabularnewline
\hline
	$2006$ &
	\raggedright P. Casey, Gaitnip Farm, St. Ola\sindex[exhibitor]{Casey, P., Gaitnip Farm, St. Ola} &
	\raggedright 4yo THx gelding &
	\raggedright Knight\sindex[horse]{Knight} &
	\raggedright By Dault Prince, out of Queen of Cloone.
	\tabularnewline
\hline
\end{longtable}
