\begin{longtable}{|c|p{5.2cm}|p{3cm}|p{3cm}|p{8cm}|}
\hline
	\textbf{Year} &
	\textbf{Exhibitor} &
	\textbf{Champion} &
	\textbf{Name} &
	\textbf{Notes} 
	\tabularnewline
\hline
\endhead
	$1936$ &
	\raggedright James Gaddie, The Bu', Holm\sindex[exhibitor]{Gaddie, James, The Bu', Holm} &
	\raggedright Cross bred polled cow &
	\raggedright - &
	\raggedright Supreme champion 1936.
	\tabularnewline
\hline
	$1937$ &
	\raggedright James Esson, Holm of Grimbister, Firth\sindex[exhibitor]{Esson, James, Holm of Grimbister, Firth} &
	\raggedright Cross bred polled cow &
	\raggedright - &
	\raggedright Supreme champion 1937.
	\tabularnewline
\hline
	$1938$ &
	\raggedright James Esson, Holm of Grimbister, Firth\sindex[exhibitor]{Esson, James, Holm of Grimbister, Firth} &
	\raggedright Cross cow &
	\raggedright - &
	\raggedright -
	\tabularnewline
\hline
	$1939$ &
	\raggedright James Flett, Kingshouse, Harray\sindex[exhibitor]{Flett, James, Kingshouse, Harray} &
	\raggedright AA heifer in calf* &
	\raggedright Annuity 3rd of Kingshouse\sindex[beef]{Annuity 3rd of Kingshouse} &
	\raggedright By Pundit of Kingshouse; supreme champion in 1939 and at 1939 Dounby Show.
	\tabularnewline
\hline
	\multicolumn{5}{|c|}{$1940-1944$  No show due to war.}
	\tabularnewline
\hline
	$1945$ &
	\raggedright ? &
	\raggedright  &
	\raggedright  &
	\raggedright 
	\tabularnewline
\hline
	$1946$ &
	\raggedright James Gaddie, Holm\sindex[exhibitor]{Gaddie, James, Holm} &
	\raggedright - &
	\raggedright - &
	\raggedright -
	\tabularnewline
\hline
	$1947$ &
	\raggedright A. A. Baikie, Hall of Tankerness\sindex[exhibitor]{Baikie, A. A., Hall of Tankerness} &
	\raggedright 7yo cross bred polled cow &
	\raggedright - &
	\raggedright Supreme champion at 1947 County show, at East Mainland Show 1946-47, and 1949.
	\tabularnewline
\hline
	$1948$ &
	\raggedright John D. Clouston, Quatquoy, Firth\sindex[exhibitor]{Clouston, John D., Quatquoy, Firth} &
	\raggedright Cross bred polled cow &
	\raggedright - &
	\raggedright Supreme champion in 1948.
	\tabularnewline
\hline
	$1949$ &
	\raggedright Mrs Baikie, Hall of Tankerness\sindex[exhibitor]{Baikie, Mrs, Hall of Tankerness} &
	\raggedright 9yo cross bred blue cow &
	\raggedright - &
	\raggedright Supreme champion at 1947 and 1949 County show and 1949 East Mainland Show.
	\tabularnewline
\hline
	$1950$ &
	\raggedright Flett Bros, Kingshouse, Harray\sindex[exhibitor]{Flett Bros, Kingshouse, Harray} &
	\raggedright AA heifer &
	\raggedright - &
	\raggedright -
	\tabularnewline
\hline
	$1951$ &
	\raggedright Messrs T. Smith \& Son, Lower Cornquoy, Holm\sindex[exhibitor]{Smith, Messrs T. \& Son, Lower Cornquoy, Holm} &
	\raggedright Black cross cow &
	\raggedright - &
	\raggedright -
	\tabularnewline
\hline
	$1952$ &
	\raggedright Mr James Baillie, Sebay, Tankerness\sindex[exhibitor]{Baillie, Mr James, Sebay, Tankerness} &
	\raggedright 2yo cross heifer in calf &
	\raggedright - &
	\raggedright -
	\tabularnewline
\hline
	$1953$ &
	\raggedright Messrs Bain \& Smith, Hall of Tankerness\sindex[exhibitor]{Bain, Messrs Bain \& Smith, Hall of Tankerness}\sindex[exhibitor]{Smith, Messrs Bain \& Smith, Hall of Tankerness} &
	\raggedright 7yo AA cow &
	\raggedright Myrtle March Mad\sindex[beef]{Myrtle March Mad} &
	\raggedright By Envoy of Derculich; supreme champion in 1953, and at 1953 East Mainland Show.
	\tabularnewline
\hline
	$1954$ &
	\raggedright Messrs Flett Bros, Kingshouse, Harray\sindex[exhibitor]{Flett Bros, Kingshouse, Harray} &
	\raggedright 5yo SH cow &
	\raggedright - &
	\raggedright By Ashcreavie White Knight; bred at Philorth; roan; supreme champion in 1954 and at 1954 Dounby Show.
	\tabularnewline
\hline
	$1955$ &
	\raggedright John D. Clouston, Quatquoy, Firth\sindex[exhibitor]{Clouston, John D., Quatquoy, Firth} &
	\raggedright 7yo cross polled black cow &
	\raggedright - &
	\raggedright Supreme champion in 1955 and at 1955 Dounby Show.
	\tabularnewline
\hline
	$1956$ &
	\raggedright W. Flett, Northbigging, Harray\sindex[exhibitor]{Flett, W., Northbigging, Harray} &
	\raggedright 9yo blue polled cross cow &
	\raggedright - &
	\raggedright Supreme champion in 1956
	\tabularnewline
\hline
	$1957$ &
	\raggedright W. Ritch, Kierfiold, Sandwick\sindex[exhibitor]{Ritch, W., Kierfiold, Sandwick} &
	\raggedright 5yo cross cow in calf &
	\raggedright - &
	\raggedright Bred at Hurtiso, Rousay; supreme champion in 1956 and at 1956 Rousay Show, and 1957 Dounby Show.
	\tabularnewline
\hline
	$1958$ &
	\raggedright J. G. Garrioch, Breckan, Costa, Evie\sindex[exhibitor]{Garrioch, J. G., Breckan, Costa, Evie} &
	\raggedright 2yo SH heifer in calf &
	\raggedright - &
	\raggedright By Calrossie Claymore.
	\tabularnewline
\hline
	$1959$ &
	\raggedright Messrs Flett Bros, Kingshouse\sindex[exhibitor]{Flett Bros, Kingshouse} &
	\raggedright 5yo black cross polled cow &
	\raggedright - &
	\raggedright Supreme champion in 1959.
	\tabularnewline
\hline
	$1960$ &
	\raggedright W. Ritch, Kierfiold, Sandwick\sindex[exhibitor]{Ritch, W., Kierfiold, Sandwick} &
	\raggedright 8yo blue-grey cow &
	\raggedright - &
	\raggedright Previous champion at County show and twice at Dounby show (years not given).
	\tabularnewline
\hline
	$1961$ &
	\raggedright Messrs M. C. Wood \& Sons, Garson, Sandwick\sindex[exhibitor]{Wood, Messrs M. C. \& Sons, Garson, Sandwick} &
	\raggedright 8yo black polled cross cow in calf &
	\raggedright - &
	\raggedright Supreme champion in 1961.
	\tabularnewline
\hline
	$1962$ &
	\raggedright A. A. Learmonth, Howe, Shapinsay\sindex[exhibitor]{Learmonth, A. A., Howe, Shapinsay} &
	\raggedright 5yo black polled cow* &
	\raggedright - &
	\raggedright Supreme champion at Shapinsay show 1960-1962.
	\tabularnewline
\hline
	$1963$ &
	\raggedright T. Dearness, Southfield, Burray\sindex[exhibitor]{Dearness, T., Southfield, Burray} &
	\raggedright 4yo AA cow &
	\raggedright Butora of Kincardine\sindex[beef]{Butora of Kincardine} &
	\multirow{2}{8cm}{By Bessort of Kincardine, out of Buto if Kincardine; bought at Kincardine dispersal sale in 1961; supreme champion in 1963 and at 1962 \& 1963 'Hope Show.}
	\tabularnewline
\cline{1-4}
	$1964$ &
	\raggedright T. Dearness, Southfield, Burray\sindex[exhibitor]{Dearness, T., Southfield, Burray} &
	\raggedright 4yo AA cow &
	\raggedright Butora of Kincardine\sindex[beef]{Butora of Kincardine} &
	\tabularnewline
\hline
	$1965$ &
	\raggedright R. R. Johnston, Trumland Farm, Rousay\sindex[exhibitor]{Johnston, R. R., Trumland Farm, Rousay} &
	\raggedright 2yo AA heifer &
	\raggedright Corbairdy Even Crescent\sindex[beef]{Corbairdy Even Crescent} &
	\raggedright By Earl of Cairnfield; bought at Cobairdy dispersal sale for 270gns; grand dam, Even Girl III, was twice champion at the Royal Highland Show.
	\tabularnewline
\hline
	$1966$ &
	\raggedright R. R. Johnston, Trumland Farm, Rousay\sindex[exhibitor]{ohnston, R. R., Trumland Farm, Rousay} &
	\raggedright 3yo AA cow &
	\raggedright Corbairdy Even Crescent\sindex[beef]{Corbairdy Even Crescent} &
	\raggedright 
	\tabularnewline
\hline
	$1967$ &
	\raggedright J. S. Baillie, Sebay, Tankerness\sindex[exhibitor]{Baillie, J. S., Sebay, Tankerness} &
	\raggedright 3yo AA cow in calf &
	\raggedright Effective of Oykell\sindex[beef]{Effective of Oykell} &
	\multirow{2}{8cm}{By Boshun of Haymount.}
	\tabularnewline
\cline{1-4}
	$1968$ &
	\raggedright J. S. Baillie, Sebay, Tankerness\sindex[exhibitor]{Baillie, J. S., Sebay, Tankerness} &
	\raggedright 4yo AA cow &
	\raggedright Oykell Effective\sindex[beef]{Oykell Effective} &
	\tabularnewline
\hline
	$1969$ &
	\raggedright D. Work \& Son, Ness, Shapinsay\sindex[exhibitor]{Work, D. \& Son, Ness, Shapinsay} &
	\raggedright 2yo black polled cross heifer in calf &
	\raggedright - &
	\raggedright By Jewra Eric of Buchaam.
	\tabularnewline
\hline
	$1970$ &
	\raggedright D. Swannie, Midhouse, South Ronaldsay\sindex[exhibitor]{Swannie, D., Midhouse, South Ronaldsay} &
	\raggedright 8yo cow &
	\raggedright - &
	\raggedright By Drummer of Fordhouse; roan; champion at 1970 'Hope show.
	\tabularnewline
\hline
	$1971$ &
	\raggedright ? &
	\raggedright  &
	\raggedright  &
	\raggedright 
	\tabularnewline
\hline
	$1972$ &
	\raggedright W. Voy, Milldam, Tankerness\sindex[exhibitor]{Voy, W., Milldam, Tankerness} &
	\raggedright 6yo cross cow &
	\raggedright - &
	\raggedright By Western Lovat Edmundo.
	\tabularnewline
\hline
	$1973$ &
	\raggedright J. S. Baillie, Sebay, Tankerness\sindex[exhibitor]{Baillie, J. S., Sebay, Tankerness} &
	\raggedright 3yo AA cow &
	\raggedright Ermonax of Eastfield\sindex[beef]{Ermonax of Eastfield} &
	\raggedright By Juanamax Eric of Douneside.
	\tabularnewline
\hline
	$1974$ &
	\raggedright D. Swannie, Midhouse, South Ronaldsay\sindex[exhibitor]{Swannie, D., Midhouse, South Ronaldsay} &
	\raggedright 12yo cow &
	\raggedright - &
	\raggedright Coloured cross champion for 4th time.
	\tabularnewline
\hline
	$1975$ &
	\raggedright J. S. Baillie, Sebay, Tankerness\sindex[exhibitor]{Baillie, J. S., Sebay, Tankerness} &
	\raggedright 8yo black cross cow in calf* &
	\raggedright - &
	\raggedright By Wester Lovat Eanomo.
	\tabularnewline
\hline
	$1976$ &
	\raggedright J. \& E. Flett, Northbigging, Harray\sindex[exhibitor]{Flett, J. \& E., Northbigging, Harray} &
	\raggedright - &
	\raggedright - &
	\raggedright Reserve champion?
	\tabularnewline
\hline
	$1977$ &
	\raggedright R. Flett, Fidge, Twatt\sindex[exhibitor]{Flett, R., Fidge, Twatt} &
	\raggedright 7yo blue-grey cow in milk* &
	\raggedright Stella\sindex[beef]{Stella} &
	\raggedright By Eurite of Inchoch, out of homebred cow; supreme champion at 1976 Dounby Show.
	\tabularnewline
\hline
	$1978$ &
	\raggedright D. Work \& Son, Ness, Shapinsay\sindex[exhibitor]{Work, D. \& Son, Ness, Shapinsay} &
	\raggedright 7yo cow in milk* &
	\raggedright - &
	\multirow{2}{8cm}{By SH bull Cavans Pablo, out of homebred cross cow; champion at Shapinsay show 1978-1980.}
	\tabularnewline
\cline{1-4}
	$1979$ &
	\raggedright D. Work \& Son, Ness, Shapinsay\sindex[exhibitor]{Work, D. \& Son, Ness, Shapinsay} &
	\raggedright 8yo cow in milk* &
	\raggedright - &
	\tabularnewline
\hline
	$1980$ &
	\raggedright J. S. Baillie, Sebay, Tankerness\sindex[exhibitor]{Baillie, J. S., Sebay, Tankerness} &
	\raggedright - &
	\raggedright - &
	\raggedright It is suggested but not made clear that this animal was also best AA cow.
	\tabularnewline
\hline
	$1981$ &
	\raggedright J. S. Baillie, Sebay, Tankerness\sindex[exhibitor]{Baillie, J. S., Sebay, Tankerness} &
	\raggedright 8yo AA cow in calf &
	\raggedright Ethlinkage of Eastfield\sindex[beef]{Ethlinkage of Eastfield} &
	\raggedright By Gentle Junior of Sturton.
	\tabularnewline
\hline
	$1982$ &
	\raggedright M. C. Wood \& Son, Garson, Sandwick\sindex[exhibitor]{Wood, M. C. \& Son, Garson, Sandwick} &
	\raggedright 5yo AAx cow in milk* &
	\raggedright - &
	\raggedright By Haymount, out of AAx cow.
	\tabularnewline
\hline
	$1983$ &
	\raggedright D. W. Sinclair \& Co, Unigarth, Sandwick\sindex[exhibitor]{Sinclair, D. W. \& Co, Unigarth, Sandwick} &
	\raggedright 9yo AA cow in milk* &
	\raggedright Primlass of Unigarth\sindex[beef]{Primlass of Unigarth} &
	\raggedright By Elprovost of Eastfield, out of Pearl of Unigarth; supreme champion in 1983.
	\tabularnewline
\hline
	$1984$ &
	\raggedright W. R. Baillie, Biggings, Toab\sindex[exhibitor]{Baillie, W. R., Biggings, Toab} &
	\raggedright 8yo CHx cow &
	\raggedright Snowflake\sindex[beef]{Snowflake} &
	\raggedright By Kairsknowe Festival, out of CH cow Kathleen; supreme champion in 1984.
	\tabularnewline
\hline
	$1985$ &
	\raggedright J. S. Baillie, Sebay, Tankerness\sindex[exhibitor]{Baillie, J. S., Sebay, Tankerness} &
	\raggedright 3yo AA cow &
	\raggedright Princess of Broompark\sindex[beef]{Princess of Broompark} &
	\raggedright By Ballycaher Noble, out of Princess 6th of Kinermony; bought from Charlie Ross, Broompark, Ross-shire; supreme champion in 1987.
	\tabularnewline
\hline
	$1986$ &
	\raggedright W. G. Kirkpatrick \& Sons, Newhall, Stromness\sindex[exhibitor]{Kirkpatrick, W. G. \& Sons, Newhall, Stromness} &
	\raggedright 4yo cow in milk &
	\raggedright - &
	\raggedright By CHx bull Ron, out of AAx cow; bought from J. \& H. Flett, Boardhouse, Birsay.
	\tabularnewline
\hline
	$1987$ &
	\raggedright J. S. Baillie, Sebay, Tankerness\sindex[exhibitor]{Baillie, J. S., Sebay, Tankerness} &
	\raggedright 5yo AA cow &
	\raggedright Princess of Broompark\sindex[beef]{Princess of Broompark} &
	\raggedright By Ballycaher Noble, out of Princess 6th of Kinermony; bought from Charlie Ross, Broompark, Ross-shire; supreme champion in 1987.
	\tabularnewline
\hline
	$1988$ &
	\raggedright J. \& H. Flett, Boardhouse, Birsay\sindex[exhibitor]{Flett, J. \& H., Boardhouse, Birsay} &
	\raggedright AAx cow in calf* &
	\raggedright - &
	\raggedright By AA bull Proud Laddie of Carmains, out of AAx cow.
	\tabularnewline
\hline
	$1989$ &
	\raggedright J. S. Baillie, Sebay, Tankerness\sindex[exhibitor]{Baillie, J. S., Sebay, Tankerness} &
	\raggedright 3yo AA cow &
	\raggedright Princess of Broompark\sindex[beef]{Princess of Broompark} &
	\raggedright By Ballycaher Noble, out of Princess 6th of Kinermony; bought from Charlie Ross, Broompark, Ross-shire; supreme champion in 1987.
	\tabularnewline
\hline
	$1990$ &
	\raggedright Messrs Davidson, Skaill, Sandwick\sindex[exhibitor]{Davidson, Messrs, Skaill, Sandwick} &
	\raggedright 2yo AA heifer in calf &
	\raggedright Nicks Delia\sindex[beef]{Nicks Delia} &
	\multirow{2}{8cm}{By DMM Esoteric, out of Tomil Delia; supreme champion in 1990 \& 1991.}
	\tabularnewline
\cline{1-4}
	$1991$ &
	\raggedright Messrs Davidson, Skaill, Sandwick\sindex[exhibitor]{Davidson, Messrs, Skaill, Sandwick} &
	\raggedright 3yo AA cow &
	\raggedright Nicks Delia\sindex[beef]{Nicks Delia} &
	\tabularnewline
\hline
	$1992$ &
	\raggedright Messrs Davidson, Skaill, Sandwick\sindex[exhibitor]{Davidson, Messrs, Skaill, Sandwick} &
	\raggedright 2yo AA heifer* &
	\raggedright Skaill Delia\sindex[beef]{Skaill Delia} &
	\raggedright By Windover Justifier, out of Nicks Delia.
	\tabularnewline
\hline
	$1993$ &
	\raggedright J. Thomson, Garth, South Ronaldsay\sindex[exhibitor]{Thomson, J., Garth, South Ronaldsay} &
	\raggedright 16mo CHx heifer &
	\raggedright Caledonia\sindex[beef]{Caledonia} &
	\raggedright By CH bull Allanfauld Vagabond, out of LMx cow; supreme champion in 1993 and at 1993 'Hope Show.
	\tabularnewline
\hline
	$1994$ &
	\raggedright T. \& J. Leslie, Quoymorhouse, Shapinsay\sindex[exhibitor]{Leslie, T. \& J., Quoymorhouse, Shapinsay} &
	\raggedright 14mo LMx heifer* &
	\raggedright Little Mo\sindex[beef]{Little Mo} &
	\raggedright By LM bull Greenbank Frank, out of homebred LMx cow.
	\tabularnewline
\hline
	$1995$ &
	\raggedright J. Baillie, Sebay, Tankerness\sindex[exhibitor]{Baillie, J., Sebay, Tankerness} &
	\raggedright 8yo AA cow &
	\raggedright Jan Erica of Little Kilry\sindex[beef]{Jan Erica of Little Kilry} &
	\raggedright By Euroe H48 of Newcairnie, out of Rashiehall Juana Erica H13; supreme champion in 1995.
	\tabularnewline
\hline
	$1996$ &
	\raggedright Messrs Davidson, Skaill, Sandwick\sindex[exhibitor]{Davidson, Messrs, Skaill, Sandwick} &
	\raggedright 2yo AA heifer in calf* &
	\raggedright Skaill Delia T2\sindex[beef]{Skaill Delia T2} &
	\raggedright By Rito 2100, out of Skaill Delia O2.
	\tabularnewline
\hline
	$1997$ &
	\raggedright R. \& J. Johnson, Hewan, Shapinsay\sindex[exhibitor]{Johnson, R. \& J., Hewan, Shapinsay} &
	\raggedright 7yo cross cow in calf* &
	\raggedright - &
	\raggedright By Newhouse Banker, out of homebred cross cow; supreme champion in 1997.
	\tabularnewline
\hline
	$1998$ &
	\raggedright G. T. \& S. Coghill, Muce, Birsay\sindex[exhibitor]{Coghill, G. T. \& S., Muce, Birsay} &
	\raggedright 5yo CH cow in milk &
	\raggedright New Moan Iris\sindex[beef]{New Moan Iris} &
	\raggedright By Balthayoak Dalesman, out of New Moan Emma; bought from Jim Isbister, New Moan, Harray, in October 1997; supreme champion in 1998 and at 1998 Dounby Show.
	\tabularnewline
\hline
	$1999$ &
	\raggedright Messrs Davidson, Skaill, Sandwick\sindex[exhibitor]{Davidson, Messrs, Skaill, Sandwick} &
	\raggedright 1yo AA heifer* &
	\raggedright Skaill Diana\sindex[beef]{Skaill Diana} &
	\raggedright By Edinburgh of The Moss, out of Skaill Diana R4; supreme champion in 1999. 
	\tabularnewline
\hline
	$2000$ &
	\raggedright Messrs Davidson, Skaill, Sandwick\sindex[exhibitor]{Davidson, Messrs, Skaill, Sandwick} &
	\raggedright 8yo AA cow in calf* &
	\raggedright Skaill Diana P8\sindex[beef]{Skaill Diana P8} &
	\raggedright By Canadian AI bull MVHF Extra, out of Nicks Delia; supreme champion in 2000.
	\tabularnewline
\hline
	$2001$ &
	\multicolumn{4}{c|}{No Show due to Foot \& Mouth outbreak.}
	\tabularnewline
\hline
	$2002$ &
	\raggedright R. J. Taylor, Brencherhouse, Birsay\sindex[exhibitor]{Taylor, R. J., Brencherhouse, Birsay} &
	\raggedright November 2001 black LMx heifer* &
	\raggedright Taylor's Touch of Class\sindex[beef]{Taylor's Touch of Class} &
	\raggedright By AI bull Ronick Hawk, out of homebred BBxLM cow; supreme champion in 2002 and at 2002 Dounby Show.
	\tabularnewline
\hline
	$2003$ &
	\raggedright John Hepburn, Burnside, Tankerness\sindex[exhibitor]{Hepburn, John, Burnside, Tankerness} &
	\raggedright 2yo AA heifer in calf* &
	\raggedright Newlot Esmerelda\sindex[beef]{Newlot Esmerelda} &
	\raggedright By Galacantry Predator, out of Esmerelda 6th of Newlot; supreme champion at 2003 East Mainland Show.
	\tabularnewline
\hline
	$2004$ &
	\raggedright W. R. Baillie, Biggings, Toab\sindex[exhibitor]{Baillie, W. R., Biggings, Toab} &
	\raggedright 17mo CH heifer* &
	\raggedright Ballieston Topsy\sindex[beef]{Ballieston Topsy} &
	\raggedright By Moyness President, out of Ballieston Maiden.
	\tabularnewline
\hline
	$2005$ &
	\raggedright Messrs Davidson, Skaill, Sandwick\sindex[exhibitor]{Davidson, Messrs, Skaill, Sandwick} &
	\raggedright 2yo AA heifer* &
	\raggedright Skaill Diana\sindex[beef]{Skaill Diana} &
	\raggedright By Skaill Express, out of Skaill Diana.
	\tabularnewline
\hline
\end{longtable}
