\begin{longtable}{|c|p{5.2cm}|p{3cm}|p{3cm}|p{8cm}|}
\hline
	\textbf{Year} &
	\textbf{Exhibitor} &
	\textbf{Champion} &
	\textbf{Name} &
	\textbf{Notes} 
	\tabularnewline
\hline
\endhead
	$1936$ &
	\raggedright James Gaddie, The Bu', Holm\sindex[exhibitor]{Gaddie, James, The Bu', Holm} &
	\raggedright Cross bred polled cow &
	\raggedright - &
	\raggedright -
	\tabularnewline
\hline
	$1937$ &
	\raggedright James Esson, Holm of Grimbister, Firth\sindex[exhibitor]{Esson, James, Holm of Grimbister, Firth} &
	\raggedright Cross bred polled cow &
	\raggedright - &
	\raggedright -
	\tabularnewline
\hline
	$1938$ &
	\raggedright James Ritch, Hatston, St. Ola\sindex[exhibitor]{Ritch, James, Hatston, St. Ola} &
	\raggedright 2yo AA stot &
	\raggedright - &
	\raggedright -
	\tabularnewline
\hline
	$1939$ &
	\raggedright James Flett, Kingshouse, Harray\sindex[exhibitor]{Flett, James, Kingshouse, Harray} &
	\raggedright AA heifer in calf* &
	\raggedright Annuity 3rd of Kingshouse\sindex[beef]{Annuity 3rd of Kingshouse} &
	\raggedright By Pundit of Kingshouse; supreme champion at 1939 Dounby Show.
	\tabularnewline
\hline
	\multicolumn{5}{|c|}{$1940-1944$  No show due to war.}
	\tabularnewline
\hline
	$1945$ &
	\raggedright ? &
	\raggedright  &
	\raggedright  &
	\raggedright 
	\tabularnewline
\hline
	$1946$ &
	\raggedright James Gaddie, Holm\sindex[exhibitor]{Gaddie, James, Holm} &
	\raggedright - &
	\raggedright - &
	\raggedright -
	\tabularnewline
\hline
	$1947$ &
	\raggedright A. Baikie, Tankerness\sindex[exhibitor]{Baikie, A., Tankerness} &
	\raggedright 7yo cross bred polled cow &
	\raggedright - &
	\raggedright -
	\tabularnewline
\hline
	$1948$ &
	\raggedright John D. Clouston, Quatquoy, Firth\sindex[exhibitor]{Clouston, John D., Quatquoy, Firth} &
	\raggedright Cross bred polled cow &
	\raggedright - &
	\raggedright -
	\tabularnewline
\hline
	$1949$ &
	\raggedright Mrs Baikie, Hall of Tankerness\sindex[exhibitor]{Baikie, Mrs, Hall of Tankerness} &
	\raggedright 9yo cross bred blue cow &
	\raggedright - &
	\raggedright Supreme champion at 1947 County show and 1949 East Mainland Show.
	\tabularnewline
\hline
	$1950$ &
	\raggedright P. Davidson, Skaill, Sandwick\sindex[exhibitor]{Davidson, P., Skaill, Sandwick} &
	\raggedright 4yo SH bull &
	\raggedright Ascreavie White Knight\sindex[beef]{Ascreavie White Knight} &
	\multirow{3}{8cm}{By Ascreavie Pusk, out of Calrossie Madge Ramsden; bought by Philorth herd at Perth for 800gns; bought by Skaill from Philorth; supreme champion at Dounby Show 1950-1952.}
	\tabularnewline
\cline{1-4}
	$1951$ &
	\raggedright P. Davidson, Skaill, Sandwick\sindex[exhibitor]{Davidson, P., Skaill, Sandwick} &
	\raggedright 5yo SH bull &
	\raggedright Ascreavie White Knight\sindex[beef]{Ascreavie White Knight} &
	\tabularnewline
\cline{1-4}
	$1952$ &
	\raggedright P. Davidson, Skaill, Sandwick\sindex[exhibitor]{Davidson, P., Skaill, Sandwick} &
	\raggedright 6yo SH bull &
	\raggedright Ascreavie White Knight\sindex[beef]{Ascreavie White Knight} &
	\tabularnewline
\hline
	$1953$ &
	\raggedright Messrs Bain \& Smith, Hall of Tankerness\sindex[exhibitor]{Bain, Messrs Bain \& Smith, Hall of Tankerness}\sindex[exhibitor]{Smith, Messrs Bain \& Smith, Hall of Tankerness} &
	\raggedright 7yo AA cow &
	\raggedright Myrtle March Mad\sindex[beef]{Myrtle March Mad} &
	\raggedright By Envoy of Derculich; supreme champion at 1953 East Mainland Show.
	\tabularnewline
\hline
	$1954$ &
	\raggedright Messrs Flett Bros, Kingshouse, Harray\sindex[exhibitor]{Flett Bros, Kingshouse, Harray} &
	\raggedright 5yo SH cow &
	\raggedright Philorth Apple Blossom\sindex[beef]{Philorth Apple Blossom} &
	\raggedright By Ascreavie White Knight, out of Philorth Orange Sunshine; dark roan; supreme champion at 1954 Dounby Show.
	\tabularnewline
\hline
	$1955$ &
	\raggedright John D. Clouston, Quatquoy, Firth\sindex[exhibitor]{Clouston, John D., Quatquoy, Firth} &
	\raggedright 7yo cross polled black cow &
	\raggedright - &
	\raggedright Supreme champion at 1955 Dounby Show.
	\tabularnewline
\hline
	$1956$ &
	\raggedright W. Flett, Northbigging, Harray\sindex[exhibitor]{Flett, W., Northbigging, Harray} &
	\raggedright 9yo blue polled cross cow &
	\raggedright - &
	\raggedright -
	\tabularnewline
\hline
	$1957$ &
	\raggedright W. Ritch, Kierfiold, Sandwick\sindex[exhibitor]{Ritch, W., Kierfiold, Sandwick} &
	\raggedright 5yo cross cow in calf &
	\raggedright - &
	\raggedright Bred at Hurtiso, Rousay; supreme champion at 1956 Rousay Show, and 1957 Dounby Show.
	\tabularnewline
\hline
	$1958$ &
	\raggedright Eric Laird, Weddell, Burray\sindex[exhibitor]{Laird, Eric, Weddell, Burray} &
	\raggedright 8mo AA bull &
	\raggedright - &
	\raggedright By Emmigrant of Durculloch, out of Gay Eric of Badmington.
	\tabularnewline
\hline
	$1959$ &
	\raggedright Messrs Flett Bros, Kingshouse\sindex[exhibitor]{Flett Bros, Kingshouse, Harray} &
	\raggedright 5yo black cross polled cow &
	\raggedright - &
	\raggedright -
	\tabularnewline
\hline
	$1960$ &
	\raggedright G. T. Wylie, Swartland, Sandwick\sindex[exhibitor]{Wylie, G. T., Swartland, Sandwick} &
	\raggedright 5yo AA bull &
	\raggedright Newhouse Jewbilant Eric\sindex[beef]{Newhouse Jewbilant Eric} &
	\raggedright Bought at Perth in Feb 1960 for 500gns; previously stock bull at Lindertis herd; supreme champion at 1960 Dounby Show.
	\tabularnewline
\hline
	$1961$ &
	\raggedright Messrs M. C. Wood \& Sons, Garson, Sandwick\sindex[exhibitor]{Wood, Messrs M. C. \& Sons, Garson, Sandwick} &
	\raggedright 8yo black polled cross cow in calf &
	\raggedright - &
	\raggedright -
	\tabularnewline
\hline
	$1962$ &
	\raggedright J. \& A. Work, Queenamoan, Sandwick\sindex[exhibitor]{Work, J. \& A., Queenamoan, Sandwick} &
	\raggedright 6yo SH bull &
	\raggedright Easter Lovat Brando\sindex[beef]{Easter Lovat Brando} &
	\raggedright By Lawton Kandy; bought in January 1962 from Caithness; supreme champion at Dounby Show 1962-1964.
	\tabularnewline
\hline
	$1963$ &
	\raggedright T. Dearness, Southfield, Burray\sindex[exhibitor]{Dearness, T., Southfield, Burray} &
	\raggedright 4yo AA cow &
	\raggedright Butora of Kincardine\sindex[beef]{Butora of Kincardine} &
	\raggedright By Bessort of Kincardine, out of Buto if Kincardine; bought at Kincardine dispersal sale in 1961; supreme champion at 1962 \& 1963 'Hope Show.
	\tabularnewline
\hline
	$1964$ &
	\raggedright A. A. Learmonth, Howe, Shapinsay\sindex[exhibitor]{Learmonth, A. A., Howe, Shapinsay} &
	\raggedright 2yo black polled cross stot &
	\raggedright - &
	\raggedright Sold at Kirkwall Auction Mart for £231 to Mr D. G. Spence, Royal Hotel, Kirkwall; champion at 1963 Kirkwall fat stock show.
	\tabularnewline
\hline
	$1965$ &
	\raggedright R. R. Johnston, Trumland Farm, Rousay\sindex[exhibitor]{Johnston, R. R., Trumland Farm, Rousay} &
	\raggedright 2yo AA heifer &
	\raggedright Corbairdy Even Crescent\sindex[beef]{Corbairdy Even Crescent} &
	\raggedright By Earl of Cairnfield; bought at Cobairdy dispersal sale for 270gns; grand dam, Even Girl III, was twice champion at the Royal Highland Show.
	\tabularnewline
\hline
	$1966$ &
	\raggedright R. R. Johnston, Trumland Farm, Rousay\sindex[exhibitor]{Johnston, R. R., Trumland Farm, Rousay} &
	\raggedright 3yo AA cow &
	\raggedright Corbairdy Even Crescent\sindex[beef]{Corbairdy Even Crescent} &
	\raggedright 
	\tabularnewline
\hline
	$1967$ &
	\raggedright J. S. Baillie, Sebay, Tankerness\sindex[exhibitor]{Baillie, J. S., Sebay, Tankerness} &
	\raggedright 4yo AA bull &
	\raggedright Wester Lovat Eanomo\sindex[beef]{Wester Lovat Eanomo} &
	\raggedright By Gaffer Desman of Drumcliffe, out of Wester Lovat Essena 15th.
	\tabularnewline
\hline
	$1968$ &
	\raggedright J. S. Baillie, Sebay, Tankerness\sindex[exhibitor]{Baillie, J. S., Sebay, Tankerness} &
	\raggedright 4yo AA cow &
	\raggedright Oykell Effective\sindex[beef]{Oykell Effective} &
	\raggedright By Bosun of Haymount.
	\tabularnewline
\hline
	$1969$ &
	\raggedright D. Work \& Son, Ness, Shapinsay\sindex[exhibitor]{Work, D., \& Son, Ness, Shapinsay} &
	\raggedright 2yo black polled cross heifer in calf &
	\raggedright - &
	\raggedright By Jewra Eric of Buchaam.
	\tabularnewline
\hline
	$1970$ &
	\raggedright J. S. Baillie, Sebay, Tankerness\sindex[exhibitor]{Baillie, J. S., Sebay, Tankerness} &
	\raggedright 6yo AA bull &
	\raggedright Stype Ptolemy\sindex[beef]{Stype Ptolemy} &
	\raggedright By Newhouse Jewdo Eric, out of Stype Pride 29th; bought at Perth Feb 1970; 1st in class at Perth.
	\tabularnewline
\hline
	$1971$ &
	\raggedright T. S. Flett, Millhouse, Harray\sindex[exhibitor]{Flett, T. S., Millhouse, Harray} &
	\raggedright 2yo AA bull* &
	\raggedright Eversharp of Millhouse\sindex[beef]{Eversharp of Millhouse} &
	\raggedright By Jovial Eric of Millhouse.
	\tabularnewline
\hline
	$1972$ &
	\raggedright A. A. Learmonth, Howe, Shapinsay\sindex[exhibitor]{Learmonth, A. A., Howe, Shapinsay} &
	\raggedright 2yo black polled cross stot* &
	\raggedright - &
	\raggedright By Black Boris of Wittington.
	\tabularnewline
\hline
	$1973$ &
	\raggedright A. A. Learmonth, Howe, Shapinsay\sindex[exhibitor]{Learmonth, A. A., Howe, Shapinsay} &
	\raggedright 2yo black polled cross stot* &
	\raggedright - &
	\raggedright By Black Boris of Wittington.
	\tabularnewline
\hline
	$1974$ &
	\raggedright I. Flett \& Sons, Millhouse, Harray\sindex[exhibitor]{Flett, I. \& Sons, Millhouse, Harray} &
	\raggedright 2yo AA bull* &
	\raggedright Elmore of Millhouse\sindex[beef]{Elmore of Millhouse} &
	\raggedright By Eversharp of Millhouse.
	\tabularnewline
\hline
	$1975$ &
	\raggedright J. S. Baillie, Sebay, Tankerness\sindex[exhibitor]{Baillie, J. S., Sebay, Tankerness} &
	\raggedright 8yo black cross cow in calf* &
	\raggedright - &
	\raggedright By Wester Lovat Eanomo.
	\tabularnewline
\hline
	$1976$ &
	\raggedright S. \& P. Davidson, Skaill, Sandwick\sindex[exhibitor]{Davidson, S. \& P., Skaill, Sandwick} &
	\raggedright 3yo AA bull &
	\raggedright Jubilant Eric of Derculich\sindex[beef]{Jubilant Eric of Derculich} &
	\raggedright By Esteem of Balachan; bought at Perth in 1974 for 900gns.
	\tabularnewline
\hline
	$1977$ &
	\raggedright R. Flett, Fidge, Twatt\sindex[exhibitor]{Flett, R., Fidge, Twatt} &
	\raggedright 7yo blue-grey cow in milk* &
	\raggedright Stella\sindex[beef]{Stella} &
	\raggedright By Eurite of Inchoch, out of homebred cow.
	\tabularnewline
\hline
	$1978$ &
	\raggedright W. R. Baillie, Biggins, Toab\sindex[exhibitor]{Baillie, W. R., Biggins, Toab} &
	\raggedright 4yo CH bull &
	\raggedright Wincote Jasper\sindex[beef]{Wincote Jasper} &
	\raggedright By Bent Caribineer; bred by Lord Nelson of Stafford; bought at Northampton for 950gns.
	\tabularnewline
\hline
	$1979$ &
	\raggedright S. \& P. Davidson, Skaill, Sandwick\sindex[exhibitor]{Davidson, S. \& P., Skaill, Sandwick} &
	\raggedright 2yo AA bull &
	\raggedright Eranger of Bucham\sindex[beef]{Eranger of Bucham} &
	\multirow{2}{8cm}{By Blackman of Greenval (Canadian bred); $\frac{3}{4}$ canadian; bought privately in Aberdeen, early 1979, from Ogg of Strathallan.}
	\tabularnewline
\cline{1-4}
	$1980$ &
	\raggedright S. \& P. Davidson, Skaill, Sandwick\sindex[exhibitor]{Davidson, S. \& P., Skaill, Sandwick} &
	\raggedright 3yo AA bull &
	\raggedright Eranger of Bucham\sindex[beef]{Eranger of Bucham} &
	\tabularnewline
\hline
	$1981$ &
	\raggedright I. Flett \& Sons, Millhouse, Harray\sindex[exhibitor]{Flett, I., \& Sons, Millhouse, Harray} &
	\raggedright 5yo AA bull &
	\raggedright Ashley Jewdict Eric\sindex[beef]{Ashley Jewdict Eric} &
	\raggedright By Eroco Bankhead; bought at Perth 1978; 1st in class at Perth.
	\tabularnewline
\hline
	$1982$ &
	\raggedright W. R. Baillie, Biggings, Toab\sindex[exhibitor]{Baillie, W. R., Biggins, Toab} &
	\raggedright 8yo CH bull &
	\raggedright Wincote Jasper\sindex[beef]{Wincote Jasper} &
	\raggedright By Bent Caribineer; bred by Lord Nelson of Stafford; bought at Northampton for 950gns.
	\tabularnewline
\hline
	$1983$ &
	\raggedright D. W. Sinclair \& Co, Unigarth, Sandwick\sindex[exhibitor]{Sinclair, D. W., \& Co, Unigarth, Sandwick} &
	\raggedright 9yo AA cow in milk* &
	\raggedright Primlass of Unigarth\sindex[beef]{Primlass of Unigarth} &
	\raggedright By Elprovost of Eastfield, out of Pearl of Unigarth.
	\tabularnewline
\hline
	$1984$ &
	\raggedright W. R. Baillie, Biggings, Toab\sindex[exhibitor]{Baillie, W. R., Biggins, Toab} &
	\raggedright 8yo CHx cow &
	\raggedright Snowflake\sindex[beef]{Snowflake} &
	\raggedright By Kairsknowe Festival, out of CH cow Kathleen.
	\tabularnewline
\hline
	$1985$ &
	\raggedright Messrs Sinclair, Unigarth \& Wood, Garson\sindex[exhibitor]{Sinclair, Messrs Sinclair, Unigarth \& Wood, Garson}\sindex[exhibitor]{Wood, Messrs Sinclair, Unigarth \& Wood, Garson} &
	\raggedright 6yo AA bull &
	\raggedright G V Winton 44L\sindex[beef]{G V Winton 44L} &
	\multirow{2}{8cm}{By G V Canadian 7J out of G V Pride 40J; canadian bred, imported into UK by Mr Charles Oag, bought by exhibitors at dispersal sale in 1983 for 4500gns; champion AA at Royal Show in 1986.}
	\tabularnewline
\cline{1-4}
	$1986$ &%\rule{0pt}{7.5ex}&
	\raggedright Messrs Sinclair, Unigarth \& Wood, Garson\sindex[exhibitor]{Sinclair, Messrs Sinclair, Unigarth \& Wood, Garson}\sindex[exhibitor]{Wood, Messrs Sinclair, Unigarth \& Wood, Garson} &
	\raggedright 7yo AA bull &
	\raggedright G V Winton 44L\sindex[beef]{G V Winton 44L} &
	\tabularnewline
\hline
	$1987$ &
	\raggedright J. S. Baillie, Sebay, Tankerness\sindex[exhibitor]{Baillie, J. S., Sebay, Tankerness} &
	\raggedright 5yo AA cow &
	\raggedright Princess of Broompark\sindex[beef]{Princess of Broompark} &
	\raggedright By Ballycaher Noble, out of Princess 6th of Kinermony; bought from Charlie Ross, Broompark, Ross-shire.
	\tabularnewline
\hline
	$1988$ &
	\raggedright Messrs Davidson, Skaill, Sandwick\sindex[exhibitor]{Davidson, Messrs, Skaill, Sandwick} &
	\raggedright 3yo SH bull &
	\raggedright Glenisla Warlord\sindex[beef]{Glenisla Warlord} &
	\raggedright By Balmyle Universe, out of Balmyle Genoa 4th; bought at Perth February 1987 for 2600gns; reserve junior champion at Perth.
	\tabularnewline
\hline
	$1989$ &
	\raggedright Messrs Davidson, Skaill, Sandwick\sindex[exhibitor]{Davidson, Messrs, Skaill, Sandwick} &
	\raggedright 15mo AA bull* &
	\raggedright - &
	\raggedright By AA/AA Willyboy, out of Erora of Skaill.
	\tabularnewline
\hline
	$1990$ &
	\raggedright Messrs Davidson, Skaill, Sandwick\sindex[exhibitor]{Davidson, Messrs, Skaill, Sandwick} &
	\raggedright 2yo AA heifer in calf &
	\raggedright Nicks Delia\sindex[beef]{Nicks Delia} &
	\multirow{2}{8cm}{By DMM Esoteric, out of Tomil Delia.}
	\tabularnewline
\cline{1-4}
	$1991$ &
	\raggedright Messrs Davidson, Skaill, Sandwick\sindex[exhibitor]{Davidson, Messrs, Skaill, Sandwick} &
	\raggedright 3yo AA cow &
	\raggedright Nicks Delia\sindex[beef]{Nicks Delia} &
	\tabularnewline
\hline
	$1992$ &
	\raggedright S. \& J. D. Robertson, Saverock, St. Ola\sindex[exhibitor]{Robertson, S. \& J. D., Saverock, St. Ola} &
	\raggedright 8mo LMx heifer calf &
	\raggedright Roxanne\sindex[beef]{Roxanne} &
	\raggedright By LM bull Homebyers Escort, out of LMxAA homebred cow; sire purchased at Perth February 1991.
	\tabularnewline
\hline
	$1993$ &
	\raggedright J. Thomson, Garth, South Ronaldsay\sindex[exhibitor]{Thomson, J., Garth, South Ronaldsay} &
	\raggedright 16mo CHx heifer &
	\raggedright Caledonia\sindex[beef]{Caledonia} &
	\raggedright By CH bull Allanfauld Vagabond, out of LMx cow.
	\tabularnewline
\hline
	$1994$ &
	\raggedright R. Cursiter \& Son, Laga, Evie\sindex[exhibitor]{Cursiter, R. \& Son, Laga, Evie} &
	\raggedright 9mo LMx stot* &
	\raggedright Sean Boy\sindex[beef]{Sean Boy} &
	\raggedright By LM bull Crownhead Gladstone, out of homebred LMxHFxFR cow.
	\tabularnewline
\hline
	$1995$ &
	\raggedright J. Baillie, Sebay, Tankerness\sindex[exhibitor]{Baillie, J., Sebay, Tankerness} &
	\raggedright 8yo AA cow &
	\raggedright Jan Erica of Little Kilry\sindex[beef]{Jan Erica of Little Kilry} &
	\raggedright By Euroe H48 of Newcairnie, out of Rashiehall Juana Erica H13.
	\tabularnewline
\hline
	$1996$ &
	\raggedright L. Muir, Midhouse, Harray\sindex[exhibitor]{Muir, L., Midhouse, Harray} &
	\raggedright 20mo LMx stot &
	\raggedright Richard Z\sindex[beef]{Richard Z} &
	\raggedright By LM bull Muirwood Galaxy, out of AAxBB cow; bought from Richard Zawadski, Balfour Mains, Shapinsay.
	\tabularnewline
\hline
	$1997$ &
	\raggedright R. \& J. Johnson, Hewan, Shapinsay\sindex[exhibitor]{Johnson, R. \& J., Hewan, Shapinsay} &
	\raggedright 7yo cross cow in calf* &
	\raggedright - &
	\raggedright By Newhouse Banker, out of homebred cross cow.
	\tabularnewline
\hline
	$1998$ &
	\raggedright G. T. \& S. Coghill, Muce, Birsay\sindex[exhibitor]{Coghill, G. T. \& S., Muce, Birsay} &
	\raggedright 5yo CH cow in milk &
	\raggedright New Moan Iris\sindex[beef]{New Moan Iris} &
	\raggedright By Balthayoak Dalesman, out of New Moan Emma; bought from Jim Isbister, New Moan, Harray, in October 1997.
	\tabularnewline
\hline
	$1999$ &
	\raggedright Messrs Davidson, Skaill, Sandwick\sindex[exhibitor]{Davidson, Messrs, Skaill, Sandwick}  &
	\raggedright Yearling AA heifer* &
	\raggedright Skaill Diana\sindex[beef]{Skaill Diana} &
	\raggedright By Edinburgh of The Moss, out of Skaill Diana R4. 
	\tabularnewline
\hline
	$2000$ &
	\raggedright Messrs Davidson, Skaill, Sandwick\sindex[exhibitor]{Davidson, Messrs, Skaill, Sandwick} &
	\raggedright 8yo AA cow in calf* &
	\raggedright Skaill Diana P8\sindex[beef]{Skaill Diana P8} &
	\raggedright By Canadian AI bull MVHF Extra, out of Nicks Delia.
	\tabularnewline
\hline
	$2001$ &
	\multicolumn{4}{c|}{No Show due to Foot \& Mouth outbreak.}
	\tabularnewline
\hline
	$2002$ &
	\raggedright R. J. Taylor, Brencherhouse, Birsay\sindex[exhibitor]{Taylor, R. J., Brencherhouse, Birsay} &
	\raggedright Nov 2001 black LMx heifer* &
	\raggedright Taylor's Touch of Class\sindex[beef]{Taylor's Touch of Class} &
	\raggedright By AI bull Ronick Hawk, out of homebred BBxLM cow.
	\tabularnewline
\hline
	$2003$ &
	\raggedright L. Muir, Midhouse, Harray\sindex[exhibitor]{Muir, L., Midhouse, Harray} &
	\raggedright 18mo LMx stot &
	\raggedright Cameron\sindex[beef]{Cameron} &
	\raggedright By LM bull Weyland Peter, out of LMx cow; bought from Cogle \& Co, Newbigging, South Ronaldsay; supreme champion at 2003 County Show and supreme champion at 2002 'Hope show.
	\tabularnewline
\hline
	$2004$ &
	\raggedright R. \& J. Johnston, Hewan, Shapinsay\sindex[exhibitor]{Johnston, R. \& J., Hewan, Shapinsay} &
	\raggedright 5mo LMx stot* &
	\raggedright Sep\sindex[beef]{Sep} &
	\raggedright By LM bull Kype Perry, out of homebred $\frac{3}{4}$ LM cow.
	\tabularnewline
\hline
	$2005$ &
	\raggedright Messrs Davidson, Skaill, Sandwick\sindex[exhibitor]{Davidson, Messrs, Skaill, Sandwick} &
	\raggedright 16mo CH bull* &
	\raggedright Skaill Victor\sindex[beef]{Skaill Victor} &
	\raggedright By Offenbach, out of Rosette.
	\tabularnewline
\hline
	$2006$ &
	\raggedright Messrs Davidson, Skaill, Sandwick\sindex[exhibitor]{Davidson, Messrs, Skaill, Sandwick} &
	\raggedright 16mo CH heifer* &
	\raggedright Skaill Abbie\sindex[beef]{Skaill Abbie} &
	\raggedright By Nectragerc, out of Perche; supreme champion at 2006 Dounby Show.
	\tabularnewline
\hline
	$2007$ &
	\multicolumn{4}{c|}{No Show due to Foot \& Mouth outbreak.}
	\tabularnewline
\hline
	$2008$ &
	\raggedright W. R. Baillie, Biggings, Toab\sindex[exhibitor]{Baillie, W. R., Biggins, Toab} &
	\raggedright 2yo CH heifer* &
	\raggedright Baillieston Anthea\sindex[beef]{Baillieston Anthea} &
	\raggedright By Mowbraypark Umpire, out of Baillieston Umbreta.
	\tabularnewline
\hline
	$2009$ &
	\raggedright W. R. Baillie, Biggings, Toab\sindex[exhibitor]{Baillie, W. R., Biggins, Toab} &
	\raggedright 5yo CH cow-in-milk* &
	\raggedright Baillieston Vera\sindex[beef]{Baillieston Vera} &
	\raggedright By Moyness President, out of Baillieston Ola.
	\tabularnewline
\hline
	$2010$ &
	\raggedright Garson Farms, Garson, Sandwick\sindex[exhibitor]{Garson Farms, Garson, Sandwick} &
	\raggedright  LMx calf&
	\raggedright  Leo\sindex[beef]{Leo}&
	\raggedright By LM bull Tehix, out of BBxLM cow.
	\tabularnewline
\hline
	$2011$ &
	\raggedright R. \& J. Johnston, Hewan, Shapinsay\sindex[exhibitor]{Johnston, R. \& J., Hewan, Shapinsay} &
	\raggedright  &
	\raggedright  &
	\raggedright 
	\tabularnewline
\hline
\end{longtable}
