\begin{longtable}{|c|p{5.2cm}|p{3cm}|p{3cm}|p{8cm}|}
\hline
	\textbf{Year} &
	\textbf{Exhibitor} &
	\textbf{Champion} &
	\textbf{Name} &
	\textbf{Notes} 
	\tabularnewline
\hline
\endhead
	$1936$ &
	\raggedright James Esson, Holm of Grimbister, Firth\sindex[exhibitor]{Esson, James, Holm of Grimbister, Firth} &
	\raggedright Cross polled cow &
	\raggedright - &
	\raggedright -
	\tabularnewline
\hline
	$1937$ &
	\raggedright James Ritch, Hatston, St. Ola\sindex[exhibitor]{Ritch, James, Hatston, St. Ola} &
	\raggedright Cow or heifer &
	\raggedright - &
	\raggedright -
	\tabularnewline
\hline
	$1938$ &
	\raggedright James Esson, Holm of Grimbister, Firth\sindex[exhibitor]{Esson, James, Holm of Grimbister, Firth} &
	\raggedright Cross cow &
	\raggedright - &
	\raggedright Supreme champion in 1937.
	\tabularnewline
\hline
	$1939$ &
	\raggedright Mr Alfred Baikie, Hall of Tankerness\sindex[exhibitor]{Baikie, Mr Alfred, Hall of Tankerness} &
	\raggedright 2yo cross polled stot &
	\raggedright - &
	\raggedright -
	\tabularnewline
\hline
	\multicolumn{5}{|c|}{$1940-1944$  No show due to war.}
	\tabularnewline
\hline
	$1945$ &
	\raggedright ? &
	\raggedright  &
	\raggedright  &
	\raggedright 
	\tabularnewline
\hline
	$1946$ &
	\raggedright J. D. Clouston, Quatquoy, Firth\sindex[exhibitor]{Clouston, J. D., Quatquoy, Firth} &
	\raggedright Cow or heifer &
	\raggedright - &
	\raggedright -
	\tabularnewline
\hline
	$1947$ &
	\raggedright Robert Ritch, Kierfiold, Sandwick\sindex[exhibitor]{Ritch, Robert, Kierfiold, Sandwick} &
	\raggedright Cow or heifer &
	\raggedright - &
	\raggedright -
	\tabularnewline
\hline
	$1948$ &
	\raggedright J. D. Clouston, Quatquoy, Firth\sindex[exhibitor]{Clouston, J. D., Quatquoy, Firth} &
	\raggedright Cross cow &
	\raggedright - &
	\raggedright -
	\tabularnewline
\hline
	$1949$ &
	\raggedright J. D. Clouston, Quatquoy, Firth\sindex[exhibitor]{Clouston, J. D., Quatquoy, Firth} &
	\raggedright - &
	\raggedright - &
	\raggedright -
	\tabularnewline
\hline
	$1950$ &
	\raggedright Flett Bros, Kingshouse, Harray\sindex[exhibitor]{Flett Bros, Kingshouse, Harray} &
	\raggedright AA heifer &
	\raggedright - &
	\raggedright -
	\tabularnewline
\hline
	$1951$ &
	\raggedright Messrs T. Smith \& Son, Lower Cornquoy, Holm\sindex[exhibitor]{Smith, Messrs T. \& Son, Lower Cornquoy, Holm} &
	\raggedright Black cross cow &
	\raggedright - &
	\raggedright -
	\tabularnewline
\hline
	$1952$ &
	\raggedright Mr James Baillie, Sebay, Tankerness\sindex[exhibitor]{Baillie, Mr James, Sebay, Tankerness} &
	\raggedright 2yo cross heifer in calf &
	\raggedright - &
	\raggedright -
	\tabularnewline
\hline
	$1953$ &
	\raggedright Mr W. Manson, Horries, Toab\sindex[exhibitor]{Manson, Mr W., Horries, Toab} &
	\raggedright SH in calf heifer &
	\raggedright - &
	\raggedright By Ascreavie White Knight, out of Augusta Mary; unregistered; white.
	\tabularnewline
\hline
	$1954$ &
	\raggedright Mr W. Flett, Northbigging, Harray\sindex[exhibitor]{Flett, Mr W., Northbigging, Harray} &
	\raggedright Cross polled cow &
	\raggedright - &
	\raggedright -
	\tabularnewline
\hline
	$1955$ &
	\raggedright Mr James Baillie, Sebay, Tankerness\sindex[exhibitor]{Baillie, Mr James, Sebay, Tankerness} &
	\raggedright - &
	\raggedright - &
	\raggedright -
	\tabularnewline
\hline
	$1956$ &
	\raggedright Mr James Baillie, Sebay, Tankerness\sindex[exhibitor]{Baillie, Mr James, Sebay, Tankerness} &
	\raggedright 8yo AA cow &
	\raggedright Lady Irona of Auchencreivie\sindex[beef]{Lady Irona of Auchencreivie} &
	\multirow{2}{8cm}{-}
	\tabularnewline
\cline{1-4}
	$1957$ &
	\raggedright Mr James Baillie, Sebay, Tankerness\sindex[exhibitor]{Baillie, Mr James, Sebay, Tankerness} &
	\raggedright 9yo AA cow &
	\raggedright Lady Irona of Auchencreivie\sindex[beef]{Lady Irona of Auchencreivie} &
	\tabularnewline
\hline
	$1958$ &
	\raggedright J. G. Garrioch, Breckan, Costa, Evie\sindex[exhibitor]{Garrioch, J. G., Breckan, Costa, Evie} &
	\raggedright 2yo SH heifer in calf &
	\raggedright - &
	\raggedright By Calrossie Claymore.
	\tabularnewline
\hline
	$1959$ &
	\raggedright P. Davidson, Skaill, Sandwick\sindex[exhibitor]{Davidson, P., Skaill, Sandwick} &
	\raggedright 21mo AA bull &
	\raggedright - &
	\raggedright Supreme champion at 1959 Dounby Show.
	\tabularnewline
\hline
	$1960$ &
	\raggedright W. Ritch, Kierfiold, Sandwick\sindex[exhibitor]{Ritch, W., Kierfiold, Sandwick} &
	\raggedright 8yo blue-grey cow &
	\raggedright - &
	\raggedright Previous champion at County show and twice at Dounby show (years not given).
	\tabularnewline
\hline
	$1961$ &
	\raggedright Mr J. W. Allan, Leafea, Stromness\sindex[exhibitor]{Allan, Mr J. W., Leafea, Stromness} &
	\raggedright 5yo SH cow &
	\raggedright - &
	\raggedright By a Jean MacGillivray bull.
	\tabularnewline
\hline
	$1962$ &
	\raggedright A. A. Learmonth, Howe, Shapinsay\sindex[exhibitor]{Learmonth, A. A., Howe, Shapinsay} &
	\raggedright 5yo black polled cow* &
	\raggedright - &
	\raggedright Supreme champion at Shapinsay show 1960-1962.
	\tabularnewline
\hline
	$1963$ &
	\raggedright J. S. Baillie, Sebay, Tankerness\sindex[exhibitor]{Baillie, J. S., Sebay, Tankerness} &
	\raggedright 1yo AA heifer* &
	\raggedright Permain of Sebay\sindex[beef]{Permain of Sebay} &
	\raggedright By President of Broadleys, out of Cobairdy cow.
	\tabularnewline
\hline
	$1964$ &
	\raggedright T. Dearness, Southfield, Burray\sindex[exhibitor]{Dearness, T., Southfield, Burray} &
	\raggedright 4yo AA cow &
	\raggedright Butora of Kincardine\sindex[beef]{Butora of Kincardine} &
	\raggedright By Bessort of Kincardine, out of Buto if Kincardine; bought at Kincardine dispersal sale in 1961; supreme champion at 1962 \& 1963 'Hope Show.
	\tabularnewline
\hline
	$1965$ &
	\raggedright A. A. Learmonth, Howe, Shapinsay\sindex[exhibitor]{Learmonth, A. A., Howe, Shapinsay} &
	\raggedright 8yo black polled cow* &
	\raggedright - &
	\raggedright Supreme champion at 1965 Shapinsay show and on three other occassions; not clear of this is the same animal as in 1962.
	\tabularnewline
\hline
	$1966$ &
	\raggedright J. S. Baillie, Sebay, Tankerness\sindex[exhibitor]{Baillie, J. S., Sebay, Tankerness} &
	\raggedright 7yo AA cow in calf* &
	\raggedright Exasperate II of Kempsons\sindex[beef]{Exasperate II of Kempsons} &
	\raggedright Bought at Perth in 1965.
	\tabularnewline
\hline
	$1967$ &
	\raggedright J. S. Baillie, Sebay, Tankerness\sindex[exhibitor]{Baillie, J. S., Sebay, Tankerness} &
	\raggedright 3yo AA cow in calf &
	\raggedright Effective of Oykell\sindex[beef]{Effective of Oykell} &
	\raggedright By Boshun of Haymount.
	\tabularnewline
\hline
	$1968$ &
	\raggedright D. Work \& Son, Ness, Shapinsay\sindex[exhibitor]{Work, D. \& Son, Ness, Shapinsay} &
	\raggedright 5yo cross polled cow* &
	\raggedright - &
	\raggedright By A Fordhouse bull; supreme champion at Shapinsay show 1967-1968.
	\tabularnewline
\hline
	$1969$ &
	\raggedright T. S. Flett, Millhouse, Harray\sindex[exhibitor]{Flett, T. S., Millhouse, Harray} &
	\raggedright 8yo AA bull* &
	\raggedright Jovial Eric of Millhouse\sindex[beef]{Jovial Eric of Millhouse} &
	\raggedright By Black Prince of Greenyards; supreme champion at 1969 Dounby Show.
	\tabularnewline
\hline
	$1970$ &
	\raggedright M. W. T. Wood, Berridale, South Ronaldsay\sindex[exhibitor]{Wood, M. W. T., Berridale, South Ronaldsay} &
	\raggedright 7yo SH bull &
	\raggedright Erimus Solomon\sindex[beef]{Erimus Solomon} &
	\raggedright By a Westdrums bull; bought at Perth in 1965; red.
	\tabularnewline
\hline
	$1971$ &
	\raggedright E. Flett, Kingshouse, Harray\sindex[exhibitor]{Flett, E., Kingshouse, Harray} &
	\raggedright Polled SHx stot* &
	\raggedright - &
	\raggedright By SH bull, out of homebred cross cow; sire bred by Andrew Kerr.
	\tabularnewline
\hline
	$1972$ &
	\raggedright T. S. Flett, Millhouse, Harray\sindex[exhibitor]{Flett, T. S., Millhouse, Harray} &
	\raggedright 3yo AA bull* &
	\raggedright Everstrike of Millhouse\sindex[beef]{Everstrike of Millhouse} &
	\raggedright -
	\tabularnewline
\hline
	$1973$ &
	\raggedright J. S. Baillie, Sebay, Tankerness\sindex[exhibitor]{Baillie, J. S., Sebay, Tankerness} &
	\raggedright 3yo AA cow &
	\raggedright Ermonax of Eastfield\sindex[beef]{Ermonax of Eastfield} &
	\raggedright By Juanamax Eric of Douneside.
	\tabularnewline
\hline
	$1974$ &
	\raggedright J. Traill Thomson, Garson, Stromness\sindex[exhibitor]{Traill Thomson, J., Garson, Stromness} &
	\raggedright 5yo SH bull &
	\raggedright Woodhead Diamond\sindex[beef]{Woodhead Diamond} &
	\raggedright By Denend Golden Miller.
	\tabularnewline
\hline
	$1975$ &
	\raggedright J. R. Heddle, Westfield, Stromness\sindex[exhibitor]{Heddle, J. R., Westfield, Stromness} &
	\raggedright 5yo HF bull &
	\raggedright Dunure Obo\sindex[beef]{Dunure Obo} &
	\raggedright By Haven Bogle; bred ar Dunure Mains, Ayrshire; bought at Edinburgh; Hereford champion at 1973 Dounby Show.
	\tabularnewline
\hline
	$1976$ &
	\raggedright J. \& E. Flett, Northbigging, Harray\sindex[exhibitor]{Flett, J. \& E., Northbigging, Harray} &
	\raggedright 7yo cross cow in calf &
	\raggedright - &
	\raggedright By SH bull, out of cross cow.
	\tabularnewline
\hline
	$1977$ &
	\raggedright J. Gaudie \& Son, Craebreck, Holm\sindex[exhibitor]{Gaudie, J. \& Son, Craebreck, Holm} &
	\raggedright 4yo HF bull &
	\raggedright Wilcot I Bernard\sindex[beef]{Wilcot I Bernard} &
	\raggedright By Crickley I Compensation; bought at Edinburgh in 1977 for 520gns.
	\tabularnewline
\hline
	$1978$ &
	\raggedright D. Work \& Son, Ness, Shapinsay\sindex[exhibitor]{Work, D. \& Son, Ness, Shapinsay} &
	\raggedright 7yo cow in milk* &
	\raggedright - &
	\multirow{2}{8cm}{By SH bull Cavans Pablo, out of homebred cross cow; champion at Shapinsay show 1978-1980.}
	\tabularnewline
\cline{1-4}
	$1979$ &
	\raggedright D. Work \& Son, Ness, Shapinsay\sindex[exhibitor]{Work, D. \& Son, Ness, Shapinsay} &
	\raggedright 8yo cow in milk* &
	\raggedright - &
	\tabularnewline
\hline
	$1980$ &
	\raggedright I. Flett \& Sons, Millhouse, Harray\sindex[exhibitor]{Flett, I. \& Sons, Millhouse, Harray} &
	\raggedright 4yo AA bull &
	\raggedright Ashley Jewdick Eric\sindex[beef]{Ashley Jewdick Eric} &
	\raggedright By Eroco of Bankhead; 1st in class at Perth in 1978; bought for 1500gns
	\tabularnewline
\hline
	$1981$ &
	\raggedright D. Work \& Son, Ness, Shapinsay\sindex[exhibitor]{Work, D. \& Son, Ness, Shapinsay} &
	\raggedright 17mo CHx stot &
	\raggedright - &
	\raggedright By CH bull Tam's Minstrel.
	\tabularnewline
\hline
	$1982$ &
	\raggedright M. C. Wood \& Son, Garson, Sandwick\sindex[exhibitor]{Wood, M. C. \& Son, Garson, Sandwick} &
	\raggedright 5yo AAx cow in milk* &
	\raggedright - &
	\raggedright By Haymount, out of AAx cow.
	\tabularnewline
\hline
	$1983$ &
	\raggedright D. W. Sinclair \& Co, Unigarth, Sandwick\sindex[exhibitor]{Sinclair, D. W. \& Co, Unigarth, Sandwick} &
	\raggedright 6yo AAx cow* &
	\raggedright - &
	\raggedright By Elprovost of Eastfield, out of Homebred cross cow; sire was supreme champion at 1978 \& 1979 Dounby Show.
	\tabularnewline
\hline
	$1984$ &
	\raggedright D. Work \& Son, Ness, Shapinsay\sindex[exhibitor]{Work, D. \& Son, Ness, Shapinsay} &
	\raggedright 1yo pure AA stot &
	\raggedright - &
	\raggedright By Pernod of Classlochie, out of pure unregistered AA cow.
	\tabularnewline
\hline
	$1985$ &
	\raggedright J. S. Baillie, Sebay, Tankerness\sindex[exhibitor]{Baillie, J. S., Sebay, Tankerness} &
	\raggedright 3yo AA cow &
	\raggedright Princess of Broompark\sindex[beef]{Princess of Broompark} &
	\raggedright By Ballycaher Noble, out of Princess 6th of Kinermony; bought from Charlie Ross, Broompark, Ross-shire; supreme champion in 1987.
	\tabularnewline
\hline
	$1986$ &
	\raggedright W. G. Kirkpatrick \& Sons, Newhall, Stromness\sindex[exhibitor]{Kirkpatrick, W. G., \& Sons, Newhall, Stromness} &
	\raggedright 4yo cow in milk &
	\raggedright - &
	\raggedright By CHx bull Ron, out of AAx cow; bought from J. \& H. Flett, Boardhouse, Birsay.
	\tabularnewline
\hline
	$1987$ &
	\raggedright P. Hepburn, Messigate, Tankerness\sindex[exhibitor]{Hepburn, P., Messigate, Tankerness} &
	\raggedright CHx stot &
	\raggedright Ripper Bruce\sindex[beef]{Ripper Bruce} &
	\raggedright By Theodopulous, out of black cross cow; bred by Michael Hadlow, Doehouse, Sandwick.
	\tabularnewline
\hline
	$1988$ &
	\raggedright J. \& H. Flett, Boardhouse, Birsay\sindex[exhibitor]{Flett, J. \& H., Boardhouse, Birsay} &
	\raggedright AAx cow in calf* &
	\raggedright - &
	\raggedright By AA bull Proud Laddie of Carmains, out of AAx cow.
	\tabularnewline
\hline
	$1989$ &
	\raggedright J. S. Baillie, Sebay, Tankerness\sindex[exhibitor]{Baillie, J. S., Sebay, Tankerness} &
	\raggedright 3yo AA cow &
	\raggedright Princess of Broompark\sindex[beef]{Princess of Broompark} &
	\raggedright By Ballycaher Noble, out of Princess 6th of Kinermony; bought from Charlie Ross, Broompark, Ross-shire; supreme champion in 1987.
	\tabularnewline
\hline
	$1990$ &
	\raggedright E. Flett, Hurtiso, Holm\sindex[exhibitor]{Flett, E., Hurtiso, Holm} &
	\raggedright 7yo SH bull &
	\raggedright Chapleton Xile\sindex[beef]{Chapleton Xile} &
	\raggedright By Balmyle Thunder, out of a Princess Royal cow.
	\tabularnewline
\hline
	$1991$ &
	\raggedright Muir \& Sons, Gorn, Shapinsay\sindex[exhibitor]{Muir \& Sons, Gorn, Shapinsay} &
	\raggedright 8mo LMx stot &
	\raggedright Bond\sindex[beef]{Bond} &
	\raggedright By LM bull Shatton Pedro, out of CHxLM cow.
	\tabularnewline
\hline
	$1992$ &
	\raggedright Messrs Davidson, Skaill, Sandwick\sindex[exhibitor]{Davidson, Messrs, Skaill, Sandwick} &
	\raggedright 2yo AA heifer* &
	\raggedright Skaill Delia\sindex[beef]{Skaill Delia} &
	\raggedright By Windover Justifier, out of Nicks Delia.
	\tabularnewline
\hline
	$1993$ &
	\raggedright C. Gorn, Weddell, Burray\sindex[exhibitor]{Gorn, C., Weddell, Burray} &
	\raggedright 4yo AAx cow in milk &
	\raggedright Bluebell\sindex[beef]{Bluebell} &
	\raggedright By AA bull Burthleu Patriot (Canadian bred), out of blue-grey cow.
	\tabularnewline
\hline
	$1994$ &
	\raggedright W. R. Baillie, Biggings, Toab\sindex[exhibitor]{Baillie, W. R., Biggings, Toab} &
	\raggedright 18mo CH bull* &
	\raggedright Ballieston Howard\sindex[beef]{Ballieston Howard} &
	\raggedright By Cockrington Baron, out of Ballieston Frances.
	\tabularnewline
\hline
	$1995$ &
	\raggedright L. Muir, Midhouse, Harray\sindex[exhibitor]{Muir, L., Midhouse, Harray} &
	\raggedright black stot &
	\raggedright Charley Boy\sindex[beef]{Charley Boy} &
	\raggedright By Bourtie Eoin, out of AAx cow; bred by W. C. Merriman, Laithe, Sandwick; bought in spring 1995.
	\tabularnewline
\hline
	$1996$ &
	\raggedright Messrs Davidson, Skaill, Sandwick\sindex[exhibitor]{Davidson, Messrs, Skaill, Sandwick} &
	\raggedright 2yo AA heifer in calf* &
	\raggedright Skaill Delia T2\sindex[beef]{Skaill Delia T2} &
	\raggedright By Rito 2100, out of Skaill Delia O2.
	\tabularnewline
\hline
	$1997$ &
	\raggedright G. R. T. Scarth \& Co, Twatt Farm, Birsay\sindex[exhibitor]{Scarth, G. R. T. \& Co, Twatt Farm, Birsay} &
	\raggedright 8yo SH cow in milk* &
	\raggedright Cavans Princess Clarrisa\sindex[beef]{Cavans Princess Clarrisa} &
	\raggedright By Balmyle Zephyr, out of Cavans Princess Annette.
	\tabularnewline
\hline
	$1998$ &
	\raggedright W. R. Baillie, Biggings, Toab\sindex[exhibitor]{Baillie, W. R., Biggings, Toab} &
	\raggedright 2yo AA heifer in calf &
	\raggedright Lucy Gwen of Darmont\sindex[beef]{Lucy Gwen of Darmont} &
	\raggedright By TLA Northern Samurai, out of Argwen Lucy 82W; supreme champion at 1998 East Mainland Show.
	\tabularnewline
\hline
	$1999$ &
	\raggedright Cogle \& Co., Newbigging, South Ronaldsay\sindex[exhibitor]{Cogle \& Co, Newbigging, South Ronaldsay} &
	\raggedright 4mo LMx stot* &
	\raggedright Magnum\sindex[beef]{Magnum} &
	\raggedright By LM bull Starkley Magnum, out of homebred CHx cow.
	\tabularnewline
\hline
	$2000$ &
	\raggedright R. J. Taylor, Brencherhouse, Birsay\sindex[exhibitor]{Taylor, R. J., Brencherhouse, Birsay} &
	\raggedright 5mo LMx heifer &
	\raggedright Taylor's Babe\sindex[beef]{Taylor's Babe} &
	\raggedright By Hudskaills Gregory, out of BBxLM cow.
	\tabularnewline
\hline
	$2001$ &
	\multicolumn{4}{c|}{No Show due to Foot \& Mouth outbreak.} 
	\tabularnewline
\hline
	$2002$ &
	\raggedright R. Gilholm, Hammerbrake, Sanday\sindex[exhibitor]{Gilholm, R., Hammerbrake, Sanday} &
	\raggedright 8mo LMx heifer &
	\raggedright Jubilee Rose\sindex[beef]{Jubilee Rose} &
	\raggedright By LM bull Roughly Plover, out of BBx cow.
	\tabularnewline
\hline
	$2003$ &
	\raggedright Messrs Davidson, Skaill, Sandwick\sindex[exhibitor]{Davidson, Messrs, Skaill, Sandwick} &
	\raggedright 2yo AA bull* &
	\raggedright Skaill Express\sindex[beef]{Skaill Express} &
	\raggedright By Darling Cruz, out of Skaill Estella.
	\tabularnewline
\hline
	$2004$ &
	\raggedright Cogle \& Co., Newbigging, South Ronaldsay\sindex[exhibitor]{Cogle \& Co, Newbigging, South Ronaldsay} &
	\raggedright 5mo LMx stot* &
	\raggedright Julyan\sindex[beef]{Julyan} &
	\raggedright By LM bull Hools Scott, out of LMxBB cow.
	\tabularnewline
\hline
	$2005$ &
	\raggedright T. \& J. Leslie, Quoymorhouse, Shapinsay\sindex[exhibitor]{Leslie, T. \& J., Quoymorhouse, Shapinsay} &
	\raggedright 9mo LMx heifer calf &
	\raggedright Red Alert\sindex[beef]{Red Alert} &
	\raggedright By LM bull Lethendry Stevie, out of LMxBB heifer.
	\tabularnewline
\hline
	$2006$ &
	\raggedright L. Muir, Midhouse, Harray\sindex[exhibitor]{Muir, L., Midhouse, Harray} &
	\raggedright 21mo LM heifer &
	\raggedright Corrigal Vera\sindex[beef]{Corrigal Vera} &
	\raggedright By Broadmeadows Cannon, out of Newsham Judy.
	\tabularnewline
\hline
	$2007$ &
	\multicolumn{4}{c|}{No Show due to Foot \& Mouth outbreak.}
	\tabularnewline
\hline
	$2008$ &
	\raggedright J. S. Baillie, Sebay, Tankerness\sindex[exhibitor]{Baillie, J. S., Sebay, Tankerness} &
	\raggedright 9mo LMx stot &
	\raggedright Black Jack\sindex[beef]{Black Jack} &
	\raggedright By LM bull Loosebeare Amazon, out of AAx heifer.
	\tabularnewline
\hline
	$2009$ &
	\raggedright E. Flett, Hurtiso, Holm\sindex[exhibitor]{Flett, E., Hurtiso, Holm} &
	\raggedright 6yo SH bull&
	\raggedright Nearhouse James\sindex[beef]{Nearhouse James} &
	\raggedright By Balmyle Crackle, out of Nearhouse Jill.
	\tabularnewline
\hline
	$2010$ &
	\raggedright Phyllis M. Hepburn, Messigate, Tankerness\sindex[exhibitor]{Hepburn, P. M., Messigate, Tankerness} &
	\raggedright 6yo AA cow-in-milk* &
	\raggedright Burnside Barbara D160\sindex[beef]{Burnside Barbara D160} &
	\raggedright By Galcantray Predator, out of Barbara 3rd of Burnside. Supreme Champion at 2010 East Mainland Show.
	\tabularnewline
\hline
	$2011$ &
	\raggedright E. Flett, Hurtiso, Holm\sindex[exhibitor]{Flett, E., Hurtiso, Holm} &
	\raggedright 4yo SH bull &
	\raggedright Uppermill Bavarian\sindex[beef]{Uppermill Bavarian} &
	\raggedright By Hurtiso Caan, out of Uppermill Buttercup.
	\tabularnewline
\hline
\end{longtable}
