\begin{longtable}{|c|p{5.2cm}|p{3cm}|p{3cm}|p{8cm}|}
\hline
	\textbf{Year} &
	\textbf{Exhibitor} &
	\textbf{Champion} &
	\textbf{Name} &
	\textbf{Notes} 
	\tabularnewline
\hline
\endhead
	$1970$ &
	\raggedright D. Swannie, Midhouse, South Ronaldsay\sindex[exhibitor]{Swannie, D., Midhouse, South Ronaldsay} &
	\raggedright 8yo cow &
	\raggedright - &
	\raggedright By Drummer of Fordhouse; roan; champion at 1970 'Hope show.
	\tabularnewline
\hline
	$1971$ &
	\raggedright E. Flett, Kingshouse, Harray\sindex[exhibitor]{Flett, E., Kingshouse, Harray} &
	\raggedright SHx stot* &
	\raggedright - &
	\raggedright By SH bull, out of homebred cross cow.
	\tabularnewline
\hline
	$1972$ &
	\raggedright D. Swannie, Midhouse, South Ronaldsay\sindex[exhibitor]{Swannie, D., Midhouse, South Ronaldsay} &
	\raggedright - &
	\raggedright - &
	\raggedright -
	\tabularnewline
\hline
	$1973$ &
	\raggedright V. R. Slater, Breck, Orphir\sindex[exhibitor]{Slater, V. R., Breck, Orphir} &
	\raggedright - &
	\raggedright - &
	\raggedright -
	\tabularnewline
\hline
	$1974$ &
	\raggedright D. Swannie, Midhouse, South Ronaldsay\sindex[exhibitor]{Swannie, D., Midhouse, South Ronaldsay} &
	\raggedright 12yo cow &
	\raggedright - &
	\multirow{2}{8cm}{Coloured cross champion for 4th time.}
	\tabularnewline
\cline{1-4}
	$1975$ &
	\raggedright D. Swannie, Midhouse, South Ronaldsay\sindex[exhibitor]{Swannie, D., Midhouse, South Ronaldsay} &
	\raggedright 13yo cow &
	\raggedright - &
	\tabularnewline
\hline
	$1976$ &
	\raggedright J. W. Foubister, Hilton, Shapinsay\sindex[exhibitor]{Foubister, J. W., Hilton, Shapinsay} &
	\raggedright heifer calf &
	\raggedright - &
	\raggedright By CHxSH bull; sold at Kirkwall Auction Mart on Monday following show for 17395 to Mr Sutherland, Boroughstone Mains, Caithness.
	\tabularnewline
\hline
	$1977$ &
	\raggedright J. S. Baillie, Sebay, Tankerness\sindex[exhibitor]{Baillie, J. S., Sebay, Tankerness} &
	\raggedright - &
	\raggedright - &
	\raggedright -
	\tabularnewline
\hline
	$1978$ &
	\raggedright R. \& J. Johnston, Hewan, Shapinsay\sindex[exhibitor]{Johnston, R. \& J., Hewan, Shapinsay} &
	\raggedright CHx stot &
	\raggedright - &
	\raggedright -
	\tabularnewline
\hline
	$1979$ &
	\raggedright J. W. Hepburn, Burnside, Tankerness\sindex[exhibitor]{Hepburn, J. W., Burnside, Tankerness} &
	\raggedright 17mo CHx stot* &
	\raggedright - &
	\raggedright By CH bull Kernowe Festival, out of homebred cross cow; sire fetched 1710,000 at auction.
	\tabularnewline
\hline
	$1980$ &
	\raggedright G. R. Coghill \& Son, Newbigging, Birsay\sindex[exhibitor]{Coghill, G. R. \& Son, Newbigging, Birsay} &
	\raggedright 6yo cow in milk* &
	\raggedright - &
	\raggedright By Cacao, out of SHx cow.
	\tabularnewline
\hline
	$1981$ &
	\raggedright D. Work \& Son, Ness, Shapinsay\sindex[exhibitor]{Work, D. \& Son, Ness, Shapinsay} &
	\raggedright 17mo CHx stot &
	\raggedright - &
	\raggedright By CH bull Tam's Minstrel.
	\tabularnewline
\hline
	$1982$ &
	\raggedright D. Work \& Son, Ness, Shapinsay\sindex[exhibitor]{Work, D. \& Son, Ness, Shapinsay} &
	\raggedright 17mo CHx stot &
	\raggedright Raymond\sindex[beef]{Raymond} &
	\raggedright Bred by Mr Flaws, Nisthouse, Evie; bought at calf sale in October.
	\tabularnewline
\hline
	$1983$ &
	\raggedright J. W. Hepburn, Burnside, Tankerness\sindex[exhibitor]{Hepburn, J. W., Burnside, Tankerness} &
	\raggedright CHx heifer calf* &
	\raggedright - &
	\raggedright By CH bull Scottish Milord, out of pure homebred AA cow.
	\tabularnewline
\hline
	$1984$ &
	\raggedright W. R. Baillie, Biggings, Toab\sindex[exhibitor]{Baillie, W. R., Biggings, Toab} &
	\raggedright 8yo CHx cow &
	\raggedright Snowflake\sindex[beef]{Snowflake} &
	\raggedright By Kairsknowe Festival, out of CH cow Kathleen.
	\tabularnewline
\hline
	$1985$ &
	\raggedright W. R. Baillie, Biggings, Toab\sindex[exhibitor]{Baillie, W. R., Biggings, Toab} &
	\raggedright 3yo cow* &
	\raggedright - &
	\raggedright By Scottish Mercury, out of homebred cow.
	\tabularnewline
\hline
	$1986$ &
	\raggedright W. R. Baillie, Biggings, Toab\sindex[exhibitor]{Baillie, W. R., Biggings, Toab} &
	\raggedright 4yo cow* &
	\raggedright Lindsay\sindex[beef]{Lindsay} &
	\raggedright By Scottish Mercury, out of homebred cross cow Kathleen; it is not clear if this is the same animal as last year.
	\tabularnewline
\hline
	$1987$ &
	\raggedright P. Hepburn, Messigate, Tankerness\sindex[exhibitor]{Hepburn, P., Messigate, Tankerness} &
	\raggedright CHx stot &
	\raggedright Ripper Bruce\sindex[beef]{Ripper Bruce} &
	\raggedright By Theodopulous, out of black cross cow; bred by Michael Hadlow, Doehouse, Sandwick.
	\tabularnewline
\hline
	$1988$ &
	\raggedright D. Work \& Son, Ness, Shapinsay\sindex[exhibitor]{Work, D. \& Son, Ness, Shapinsay} &
	\raggedright - &
	\raggedright - &
	\raggedright -
	\tabularnewline
\hline
	$1989$ &
	\raggedright S. \& J. D. Robertson, Saverock, St. Ola\sindex[exhibitor]{Robertson, S. \& J. D., Saverock, St. Ola} &
	\raggedright - &
	\raggedright - &
	\raggedright -
	\tabularnewline
\hline
	$1990$ &
	\raggedright ? &
	\raggedright  &
	\raggedright  &
	\raggedright 
	\tabularnewline
\hline
	$1991$ &
	\raggedright Muir \& Sons, Gorn, Shapinsay\sindex[exhibitor]{} &
	\raggedright 8mo LMx stot &
	\raggedright Bond\sindex[beef]{Bond} &
	\raggedright By LM bull Shatton Pedro, out of CHxLM cow.
	\tabularnewline
\hline
	$1992$ &
	\raggedright S. \& J. D. Robertson, Saverock, St. Ola\sindex[exhibitor]{Robertson, S. \& J. D., Saverock, St. Ola} &
	\raggedright 8mo LMx heifer calf &
	\raggedright Roxanne\sindex[beef]{Roxanne} &
	\raggedright By LM bull Homebyers Escort, out of LMxAA homebred cow; sire purchased at Perth February 1991.
	\tabularnewline
\hline
	$1993$ &
	\raggedright J. Thomson, Garth, South Ronaldsay\sindex[exhibitor]{Thomson, J., Garth, South Ronaldsay} &
	\raggedright 16mo CHx heifer &
	\raggedright Caledonia\sindex[beef]{Caledonia} &
	\raggedright By CH bull Allanfauld Vagabond, out of LMx cow.
	\tabularnewline
\hline
	$1994$ &
	\raggedright R. Cursiter \& Son, Laga, Evie\sindex[exhibitor]{Cursiter, R. \& Son, Laga, Evie} &
	\raggedright 9mo LMx heifer &
	\raggedright Laga's Gem\sindex[beef]{Laga's Gem} &
	\raggedright By LM bull Crownhead Gladstone, out of 3/4 LM heifer; dam bought from Muir \& Sons, Gorn, Shapinsay.
	\tabularnewline
\hline
	$1995$ &
	\raggedright W. R. Baillie, Biggings, Toab\sindex[exhibitor]{Baillie, W. R., Biggings, Toab} &
	\raggedright 11mo LMx stot &
	\raggedright Red Alert\sindex[beef]{Red Alert} &
	\raggedright By LM bull Gringley Cavalier, out of LMxAA cow.
	\tabularnewline
\hline
	$1996$ &
	\raggedright J. A. Scott \& Co, Howe, Harray\sindex[exhibitor]{Scott, J. A. \& Co, Howe, Harray} &
	\raggedright 17mo CHx heifer* &
	\raggedright - &
	\raggedright By CH bull Seawell Goutte, out of homebred LMx cow.
	\tabularnewline
\hline
	$1997$ &
	\raggedright R. J. Taylor, Brencherhouse, Birsay\sindex[exhibitor]{Taylor, R. J., Brencherhouse, Birsay} &
	\raggedright calf's teeth heifer &
	\raggedright Tinkerbell\sindex[beef]{Tinkerbell} &
	\raggedright By Newfoulds Vagabond, out of 3/4 LM cow.
	\tabularnewline
\hline
	$1998$ &
	\raggedright Cogle \& Co, Newbigging, South Ronaldsay\sindex[exhibitor]{Cogle \& Co, Newbigging, South Ronaldsay} &
	\raggedright 4mo LMxCH stot &
	\raggedright - &
	\raggedright By Hools Lumu, out of CHx cow; supreme champion at 1998 'Hope show.
	\tabularnewline
\hline
	$1999$ &
	\raggedright Cogle \& Co, Newbigging, South Ronaldsay\sindex[exhibitor]{Cogle \& Co, Newbigging, South Ronaldsay} &
	\raggedright 4mo LMx stot* &
	\raggedright Magnum\sindex[beef]{Magnum} &
	\raggedright By LM bull Starkley Magnum, out of homebred CHx cow.
	\tabularnewline
\hline
	$2000$ &
	\raggedright R. Cursiter \& Son, Laga, Evie\sindex[exhibitor]{Cursiter, R. \& Son, Laga, Evie} &
	\raggedright 20mo LMx heifer* &
	\raggedright Laga's Thunderthighs\sindex[beef]{Laga's Thunderthighs} &
	\raggedright By LM bull Crownhead Gladstone, out of LMxHFxFR cow; supreme champion at 2000 Dounby Show.
	\tabularnewline
\hline
	$2001$ &
	\multicolumn{4}{c|}{No Show due to Foot \& Mouth outbreak.}
	\tabularnewline
\hline
	$2002$ &
	\raggedright L. Muir, Midhouse, Harray\sindex[exhibitor]{Muir, L., Midhouse, Harray} &
	\raggedright 8mo LMx heifer &
	\raggedright Harray Topper\sindex[beef]{Harray Topper} &
	\raggedright By LM bull Tanat Otter, out of homebred LMx heifer.
	\tabularnewline
\hline
	$2003$ &
	\raggedright L. Muir, Midhouse, Harray\sindex[exhibitor]{Muir, L., Midhouse, Harray} &
	\raggedright January 2002 LMx heifer* &
	\raggedright Steph\sindex[beef]{Steph} &
	\raggedright By LM bull Tanat Otter, out of LMx cow; supreme champion at 2003 Dounby Show.
	\tabularnewline
\hline
	$2004$ &
	\raggedright R. \& J. Johnston, Hewan, Shapinsay\sindex[exhibitor]{Johnston, R. \& J., Hewan, Shapinsay} &
	\raggedright 5mo LMx stot* &
	\raggedright Sep\sindex[beef]{Sep} &
	\raggedright By LM bull Kype Perry, out of homebred $\frac{3}{4}$ LM cow; supreme champion in 2004.
	\tabularnewline
\hline
	$2005$ &
	\raggedright T. \& J. Leslie, Quoymorhouse, Shapinsay\sindex[exhibitor]{Leslie, T. \& J., Quoymorhouse, Shapinsay} &
	\raggedright 9mo LMx heifer calf &
	\raggedright Red Alert\sindex[beef]{Red Alert} &
	\raggedright By LM bull Lethendry Stevie, out of LMxBB heifer.
	\tabularnewline
\hline
	$2006$ &
	\raggedright G. T. \& S. Coghill, Muce, Birsay\sindex[exhibitor]{Coghill, G. T. \& S., Muce, Birsay} &
	\raggedright 5mo BBx heifer calf* &
	\raggedright - &
	\raggedright By BB bull, out of homebred LMx cow.
	\tabularnewline
\hline
	$2007$ &
	\multicolumn{4}{c|}{No Show due to Foot \& Mouth outbreak.}
	\tabularnewline
\hline
	$2008$ &
	\raggedright R. J. Taylor, Brencherhouse, Birsay\sindex[exhibitor]{Taylor, R. J., Brencherhouse, Birsay} &	
		\raggedright 17mo LMx heifer* &
	\raggedright - &
	\raggedright By Ronick Hawk, out of homebred LMxBB cow; supreme champion at 2009 Dounby Show.
	\tabularnewline
\hline
	$2009$ &
	\raggedright T. \& J. Leslie, Quoymorhouse, Shapinsay\sindex[exhibitor]{Leslie, T. \& J., Quoymorhouse, Shapinsay} &	
		\raggedright 5mo CHx stot &
	\raggedright - &
	\raggedright By CH bull Ravensworth Ainsley, out of LMx cow.
	\tabularnewline
\hline
	$2010$ &
	\raggedright Garson Farms, Garson, Sandwick\sindex[exhibitor]{Garson Farms, Garson, Sandwick} &
	\raggedright  LMx calf&
	\raggedright  Leo\sindex[beef]{Leo}&
	\raggedright By LM bull Tehix, out of BBxLM cow; supreme champion.
	\tabularnewline
\hline
$2011$ &
	\raggedright R. \& J. Johnston, Hewan, Shapinsay\sindex[exhibitor]{Johnston, R. \& J., Hewan, Shapinsay} &
	\raggedright  &
	\raggedright  &
	\raggedright Supreme champion.
	\tabularnewline
\hline
\end{longtable}
