\begin{longtable}{|c|p{5.2cm}|p{3cm}|p{3cm}|p{8cm}|}
\hline
	\textbf{Year} &
	\textbf{Exhibitor} &
	\textbf{Champion} &
	\textbf{Name} &
	\textbf{Notes} 
	\tabularnewline
\hline
\endhead
	$1970$ &
	\raggedright D. Work \& Son, Ness, Shapinsay\sindex[exhibitor]{Work, D. \& Son, Ness, Shapinsay} &
	\raggedright 3yo cow &
	\raggedright - &
	\raggedright -
	\tabularnewline
\hline
	$1971$ &
	\raggedright D. Work \& Son, Ness, Shapinsay\sindex[exhibitor]{Work, D. \& Son, Ness, Shapinsay} &
	\raggedright 2 teeth stot* &
	\raggedright - &
	\raggedright By Jura Eric of Buchaam.
	\tabularnewline
\hline
	$1972$ &
	\raggedright A. A. Learmonth, Howe, Shapinsay\sindex[exhibitor]{Learmonth, A. A., Howe, Shapinsay} &
	\raggedright 2yo black polled cross stot* &
	\raggedright - &
	\raggedright By Black Boris of Wittington.
	\tabularnewline
\hline
	$1973$ &
	\raggedright A. A. Learmonth, Howe, Shapinsay\sindex[exhibitor]{Learmonth, A. A., Howe, Shapinsay} &
	\raggedright 2yo black polled cross stot* &
	\raggedright - &
	\raggedright By Black Boris of Wittington.
	\tabularnewline
\hline
	$1974$ &
	\raggedright John Scott Jnr, Roeberry, South Ronaldsay\sindex[exhibitor]{Scott, John Jnr, Roeberry, South Ronaldsay} &
	\raggedright 7yo cow &
	\raggedright - &
	\raggedright Bought from Burray; champion at 1974 'Hope show.
	\tabularnewline
\hline
	$1975$ &
	\raggedright J. S. Baillie, Sebay, Tankerness\sindex[exhibitor]{Baillie, J. S., Sebay, Tankerness} &
	\raggedright 8yo black cross cow in calf* &
	\raggedright - &
	\raggedright By Wester Lovat Eanomo.
	\tabularnewline
\hline
	$1976$ &
	\raggedright J. \& E. Flett, Northbigging, Harray\sindex[exhibitor]{Flett, J. \& E., Northbigging, Harray} &
	\raggedright 7yo cow in calf &
	\raggedright - &
	\raggedright By SH bull, out of cross cow; blue grey.
	\tabularnewline
\hline
	$1977$ &
	\raggedright R. Flett, Fidge, Twatt\sindex[exhibitor]{Flett, R., Fidge, Twatt} &
	\raggedright 7yo blue-grey cow in milk* &
	\raggedright Stella\sindex[beef]{Stella} &
	\raggedright By Eurite of Inchoch, out of homebred cow.
	\tabularnewline
\hline
	$1978$ &
	\raggedright D. Work \& Son, Ness, Shapinsay\sindex[exhibitor]{Work, D. \& Son, Ness, Shapinsay} &
	\raggedright 7yo cow in milk* &
	\raggedright - &
	\raggedright By SH bull Cavans Pablo, out of homebred cross cow; champion at Shapinsay show 1978-1980.
	\tabularnewline
\hline
	$1979$ &
	\raggedright D. Work \& Son, Ness, Shapinsay\sindex[exhibitor]{Work, D. \& Son, Ness, Shapinsay} &
	\raggedright 8yo cow in milk* &
	\raggedright - &
	\raggedright 
	\tabularnewline
\hline
	$1980$ &
	\raggedright J. W. Hepburn, Burnside, Tankerness\sindex[exhibitor]{Hepburn, J. W., Burnside, Tankerness} &
	\raggedright 10mo stot &
	\raggedright - &
	\raggedright By Weddenlie Evictor, out of pure (AA?) cow Brenda of Newlot.
	\tabularnewline
\hline
	$1981$ &
	\raggedright C. S. Gorn, Weddell, Burray\sindex[exhibitor]{Gorn, C. S., Weddell, Burray} &
	\raggedright 5yo cow in calf* &
	\raggedright - &
	\raggedright By Newhouse Prince 121st; supreme champion at 'Hope show 1980 \& 1981.
	\tabularnewline
\hline
	$1982$ &
	\raggedright M. C. Wood \& Son, Garson, Sandwick\sindex[exhibitor]{Wood, M. C. \& Son, Garson, Sandwick} &
	\raggedright 5yo AAx cow in milk* &
	\raggedright - &
	\raggedright By Haymount, out of AAx cow.
	\tabularnewline
\hline
	$1983$ &
	\raggedright D. W. Sinclair \& Co, Unigarth, Sandwick\sindex[exhibitor]{Sinclair, D. W. \& Co, Unigarth, Sandwick} &
	\raggedright 6yo AAx cow* &
	\raggedright - &
	\raggedright By Elprovost of Eastfield, out of Homebred cross cow; sire was supreme champion at 1978 \& 1979 Dounby Show.
	\tabularnewline
\hline
	$1984$ &
	\raggedright D. Work \& Son, Ness, Shapinsay\sindex[exhibitor]{Work, D. \& Son, Ness, Shapinsay} &
	\raggedright 1yo pure AA stot &
	\raggedright - &
	\raggedright By Pernod of Classlochie, out of pure unregistered AA cow.
	\tabularnewline
\hline
	$1985$ &
	\raggedright J. \& H. Flett, Boardhouse, Birsay\sindex[exhibitor]{Flett, J. \& H., Boardhouse, Birsay} &
	\raggedright 3yo cow &
	\raggedright Black Lady\sindex[beef]{Black Lady} &
	\raggedright By CHx bull Ron, out of Orkney black cross cow.
	\tabularnewline
\hline
	$1986$ &
	\raggedright W. G. Kirkpatrick \& Sons, Newhall, Stromness\sindex[exhibitor]{Kirkpatrick, W. G. \& Sons, Newhall, Stromness} &
	\raggedright 4yo cow in milk &
	\raggedright - &
	\raggedright By CHx bull Ron, out of AAx cow; bought from J. \& H. Flett, Boardhouse, Birsay.
	\tabularnewline
\hline
	$1987$ &
	\raggedright W. G. Kirkpatrick \& Sons, Vestrafiold, Sandwick\sindex[exhibitor]{Kirkpatrick, W. G. \& Sons, Vestrafiold, Sandwick} &
	\raggedright 5yo cow in milk &
	\raggedright - &
	\raggedright By CHx bull Ron, out of AAx cow; bought from J. \& H. Flett, Boardhouse, Birsay; not clear if this is the same animal as last year.
	\tabularnewline
\hline
	$1988$ &
	\raggedright J. \& H. Flett, Boardhouse, Birsay\sindex[exhibitor]{Flett, J. \& H., Boardhouse, Birsay} &
	\raggedright AAx cow in calf* &
	\raggedright - &
	\raggedright By AA bull Proud Laddie of Carmains, out of AAx cow.
	\tabularnewline
\hline
	$1989$ &
	\raggedright W. G. Kirkpatrick \& Sons, Vestrafiold, Sandwick\sindex[exhibitor]{Kirkpatrick, W. G. \& Sons, Vestrafiold, Sandwick} &
	\raggedright 8yo cow in milk &
	\raggedright - &
	\raggedright By CHx bull Ron, out of AAx cow; bought from J. \& H. Flett, Boardhouse, Birsay; not clear if this is the same animal as in 1986 or 1987.
	\tabularnewline
\hline
	$1990$ &
	\raggedright S. \& J. D. Robertson, Saverock, St Ola\sindex[exhibitor]{Robertson, S. \& J. D., Saverock, St Ola} &
	\raggedright 16mo LMx heifer &
	\raggedright - &
	\raggedright By Endovic Vick, out of AAx cow.
	\tabularnewline
\hline
	$1991$ &
	\raggedright J. \& H. Flett, Boardhouse, Birsay\sindex[exhibitor]{Flett, J. \& H., Boardhouse, Birsay} &
	\raggedright 5yo cow* &
	\raggedright Black Magic\sindex[beef]{Black Magic} &
	\raggedright By Proud Laddie of Carmains, out of AAx cow.
	\tabularnewline
\hline
	$1992$ &
	\raggedright Muir \& Son, Gorn, Shapinsay\sindex[exhibitor]{Muir \& Son, Gorn, Shapinsay} &
	\raggedright heifer showing calf's teeth &
	\raggedright - &
	\raggedright By Dukes Canton.
	\tabularnewline
\hline
	$1993$ &
	\raggedright C. Gorn, Weddell, Burray\sindex[exhibitor]{Gorn, C., Weddell, Burray} &
	\raggedright 4yo AAx cow in milk &
	\raggedright Bluebell\sindex[beef]{Bluebell} &
	\raggedright By AA bull Burthleu Patriot (Canadian bred), out of blue-grey cow.
	\tabularnewline
\hline
	$1994$ &
	\raggedright R. Cursiter \& Son, Laga, Evie\sindex[exhibitor]{Cursiter, R. \& Son, Laga, Evie} &
	\raggedright 9mo LMx stot* &
	\raggedright Sean Boy\sindex[beef]{Sean Boy} &
	\raggedright By LM bull Crownhead Gladstone, out of homebred LMxHFxFR cow.
	\tabularnewline
\hline
	$1995$ &
	\raggedright L. Muir, Midhouse, Harray\sindex[exhibitor]{Muir, L., Midhouse, Harray} &
	\raggedright black stot &
	\raggedright Charley Boy\sindex[beef]{Charley Boy} &
	\raggedright By Bourtie Eoin, out of AAx cow; bred by W. C. Merriman, Laithe, Sandwick; bought in spring 1995.
	\tabularnewline
\hline
	$1996$ &
	\raggedright L. Muir, Midhouse, Harray\sindex[exhibitor]{Muir, L., Midhouse, Harray} &
	\raggedright 20mo LMx stot &
	\raggedright Richard Z\sindex[beef]{Richard Z} &
	\raggedright By LM bull Muirwood Galaxy, out of AAxBB cow; bought from Richard Zawadski, Balfour Mains, Shapinsay.
	\tabularnewline
\hline
	$1997$ &
	\raggedright R. \& J. Johnson, Hewan, Shapinsay\sindex[exhibitor]{Johnson, R. \& J., Hewan, Shapinsay} &
	\raggedright 7yo cross cow in calf* &
	\raggedright - &
	\raggedright By Newhouse Banker, out of homebred cross cow.
	\tabularnewline
\hline
	$1998$ &
	\raggedright T. \& J. Leslie, Quoymorhouse, Shapinsay\sindex[exhibitor]{Leslie, T. \& J., Quoymorhouse, Shapinsay} &
	\raggedright 17mo heifer &
	\raggedright - &
	\raggedright By Hartside Jacko, out of LMx cow.
	\tabularnewline
\hline
	$1999$ &
	\raggedright Garson Farms, Sandwick\sindex[exhibitor]{Garson Farms, Sandwick} &
	\raggedright calf's teeth stot &
	\raggedright Beckham\sindex[beef]{Beckham} &
	\raggedright By Bailea Justice, out of LMxAA cow.
	\tabularnewline
\hline
	$2000$ &
	\raggedright R. J. Taylor, Brencherhouse, Birsay\sindex[exhibitor]{Taylor, R. J., Brencherhouse, Birsay} &
	\raggedright 5mo LMx heifer &
	\raggedright Taylor's Babe\sindex[beef]{Taylor's Babe} &
	\raggedright By Hudskaills Gregory, out of BBxLM cow.
	\tabularnewline
\hline
	$2001$ &
	\multicolumn{4}{c|}{No Show due to Foot \& Mouth outbreak.}
	\tabularnewline
\hline
	$2002$ &
	\raggedright R. J. Taylor, Brencherhouse, Birsay\sindex[exhibitor]{Taylor, R. J., Brencherhouse, Birsay} &
	\raggedright Nov 2001 black LMx heifer* &
	\raggedright Taylor's Touch of Class\sindex[beef]{Taylor's Touch of Class} &
	\raggedright By AI bull Ronick Hawk, out of homebred BBxLM cow.
	\tabularnewline
\hline
	$2003$ &
	\raggedright L. Muir, Midhouse, Harray\sindex[exhibitor]{Muir, L., Midhouse, Harray} &
	\raggedright 18mo LMx stot &
	\raggedright Cameron\sindex[beef]{Cameron} &
	\raggedright By LM bull Weyland Peter, out of LMx cow; bought from Cogle \& Co, Newbigging, South Ronaldsay; supreme champion at 2003 County Show and supreme champion at 2002 'Hope show.
	\tabularnewline
\hline
	$2004$ &
	\raggedright Cogle \& Co., Newbigging, South Ronaldsay\sindex[exhibitor]{Cogle \& Co, Newbigging, South Ronaldsay} &
	\raggedright 5mo LMx stot* &
	\raggedright Julyan\sindex[beef]{Julyan} &
	\raggedright By LM bull Hools Scott, out of LMxBB cow.
	\tabularnewline
\hline
	$2005$ &
	\raggedright G. T. \& S. Coghill, Muce, Birsay\sindex[exhibitor]{Coghill, G. T. \& S., Muce, Birsay} &
	\raggedright 2yo black polled cross heifer in calf* &
	\raggedright President's Princess\sindex[beef]{President's Princess} &
	\raggedright By Hekra Norseman, out of BBx cow; supreme champion 2005 Dounby Show.
	\tabularnewline
\hline
	$2006$ &
	\raggedright Garson Farms, Garson, Sandwick\sindex[exhibitor]{Garson Farms, Sandwick} &
	\raggedright 7mo BBx stot calf &
	\raggedright Garson Marie\sindex[beef]{Garson Marie} &
	\raggedright By BB bull Beesthorpe Thunderflash, out of LMx cow.
	\tabularnewline
\hline
	$2007$ &
	\multicolumn{4}{c|}{No Show due to Foot \& Mouth outbreak.}
	\tabularnewline
\hline
	$2008$ &
	\raggedright J. S. Baillie, Sebay, Tankerness\sindex[exhibitor]{Baillie, J. S., Sebay, Tankerness} &
	\raggedright 9mo LMx stot &
	\raggedright Black Jack\sindex[beef]{Black Jack} &
	\raggedright By LM bull Loosebeare Amazon, out of AAx heifer; reserve supreme champion.
	\tabularnewline
\hline
	$2009$ &
	\raggedright M. \& A. Lennie, Silverhall, Sanday\sindex[exhibitor]{Lennie, M. \& A., Silverhall, Sanday} &
	\raggedright 8mo LMx stot &
	\raggedright -&
	\raggedright By LM bull Malibu, out of $\frac{3}{4}$ LMx cow.
	\tabularnewline
\hline
	$2010$ &
	\raggedright K. \& M. Eunson, Braebuster Farm, Deerness\sindex[exhibitor]{Eunson, K. \& M., Braebuster Farm, Deerness} &
	\raggedright 8mo heifer calf &
	\raggedright Black Diamond&
	\raggedright By Westhall Uplands, out of BBx cow.
	\tabularnewline
\hline
	$2011$ &
	\raggedright  &
	\raggedright  &
	\raggedright &
	\raggedright 
	\tabularnewline
\hline
\end{longtable}
