\begin{longtable}{|c|p{5.2cm}|p{3cm}|p{3cm}|p{8cm}|}
\hline
	\textbf{Year} &
	\textbf{Exhibitor} &
	\textbf{Champion} &
	\textbf{Name} &
	\textbf{Notes} 
	\tabularnewline
\hline
\endhead
	$1970$ &
	\multicolumn{4}{c|}{?}
	\tabularnewline
\hline
	$1971$ &
	\multicolumn{4}{c|}{?}
	\tabularnewline
\hline
	$1972$ &
	\multicolumn{4}{c|}{?}
	\tabularnewline
\hline
	$1973$ &
	\multicolumn{4}{c|}{?}
	\tabularnewline
\hline
	$1974$ &
	\raggedright V. R. Slater, Breck, Orphir\sindex[exhibitor]{Slater, V. R., Breck, Orphir} &
	\raggedright - &
	\raggedright - &
	\raggedright -
	\tabularnewline
\hline
	$1975$ &
	\raggedright J. W. Hourston, Croval, Sandwick\sindex[exhibitor]{Hourston, J. W., Croval, Sandwick} &
	\raggedright - &
	\raggedright - &
	\raggedright -
	\tabularnewline
\hline
	$1976$ &
	\multicolumn{4}{c|}{?}
	\tabularnewline
\hline
	$1977$ &
	\raggedright S. \& P. Davidson, Skaill Farm, Sandwick\sindex[exhibitor]{Davidson, S. \& P., Skaill Farm, Sandwick} &
	\raggedright - &
	\raggedright - &
	\raggedright -
	\tabularnewline
\hline
	$1978$ &
	\multicolumn{4}{c|}{?}
	\tabularnewline
\hline
	$1979$ &
	\multicolumn{4}{c|}{?}
	\tabularnewline
\hline
	$1980$ &
	\multicolumn{4}{c|}{?}
	\tabularnewline
\hline
	$1981$ &
	\raggedright W. C. Merriman, Laithe, Sandwick\sindex[exhibitor]{Merriman, W. C., Laithe, Sandwick} &
	\raggedright 7yo cow* &
	\raggedright - &
	\raggedright By North Devon bull, out of homebred cross cow; sire bought from Bemersyde, Melrose.
	\tabularnewline
\hline
	$1982$ &
	\raggedright W. G. Kirkpatrick \& Sons, Newhall, Sandwick\sindex[exhibitor]{Kirkpatrick, W. G. \& Sons, Newhall, Sandwick} &
	\raggedright 1yo CHx heifer* &
	\raggedright - &
	\raggedright By Hanham Lodge, out of homebred SHx cow.
	\tabularnewline
\hline
	$1983$ &
	\raggedright W. C. Merriman, Laithe, Sandwick\sindex[exhibitor]{Merriman, W. C., Laithe, Sandwick} &
	\raggedright 8yo cow in milk* &
	\raggedright - &
	\multirow{2}{8cm}{By North Devon bull, out of homebred cross cow; sire bought from Bemersyde, Melrose.}
	\tabularnewline
\cline{1-4}
	$1984$ &
	\raggedright W. C. Merriman, Laithe, Sandwick\sindex[exhibitor]{Merriman, W. C., Laithe, Sandwick} &
	\raggedright 10yo cow in milk* &
	\raggedright - & 
	\tabularnewline
\hline
	$1985$ &
	\raggedright W. G. Kirkpatrick \& Sons, Newhall, Sandwick\sindex[exhibitor]{Kirkpatrick, W. G. \& Sons, Newhall, Sandwick} &
	\raggedright Stot &
	\raggedright - &
	\raggedright By Henham Lodge Jolyon, out of SH cow.
	\tabularnewline
\hline
	$1986$ &
	\raggedright M. S. Wood \& Co, Pow, Sandwick\sindex[exhibitor]{Wood, M. S. \& Co, Pow, Sandwick} &
	\raggedright 1yo SMx heifer &
	\raggedright - &
	\raggedright By SM bull, out of AAx cow; sire bought at Perth in October 1983.
	\tabularnewline
\hline
	$1987$ &
	\raggedright G. T. \& S. Coghill, Muce, Birsay\sindex[exhibitor]{Coghill, G. T. \& S., Muce, Birsay} &
	\raggedright March 1986 CHxAA heifer &
	\raggedright - &
	\raggedright By Bleslack Unique, out of Orkney bred AA cow; supreme champion in 1987.
	\tabularnewline
\hline
	$1988$ &
	\raggedright Garson Farms, Sandwick\sindex[exhibitor]{Garson Farms, Sandwick} &
	\raggedright CHx heifer* &
	\raggedright - &
	\raggedright By CH bull, out of AAx cow.
	\tabularnewline
\hline
	$1989$ &
	\raggedright G. T. \& S. Coghill, Muce, Birsay\sindex[exhibitor]{Coghill, G. T. \& S., Muce, Birsay} &
	\raggedright 15mo CHx heifer* &
	\raggedright - &
	\raggedright By CH bull, out of 5yo SMx cow.
	\tabularnewline
\hline
	$1990$ &
	\raggedright G. T. \& S. Coghill, Muce, Birsay\sindex[exhibitor]{Coghill, G. T. \& S., Muce, Birsay} &
	\raggedright Stot? &
	\raggedright - &
	\raggedright -
	\tabularnewline
\hline
	$1991$ &
	\raggedright S. \& F. Nicolson, Stenaday, Harray\sindex[exhibitor]{Nicolson, S. \& F., Stenaday, Harray} &
	\raggedright CHx stot calf &
	\raggedright - &
	\raggedright By CH bull, out of AAxFR cow.
	\tabularnewline
\hline
	$1992$ &
	\raggedright G. T. \& S. Coghill, Muce, Birsay\sindex[exhibitor]{Coghill, G. T. \& S., Muce, Birsay} &
	\raggedright 5mo CHx heifer &
	\raggedright - &
	\raggedright By CH bull Barksore Englander, out of SMx cow.
	\tabularnewline
\hline
	$1993$ &
	\raggedright T. Flett, Appietown, Rendall\sindex[exhibitor]{Flett, T., Appietown, Rendall} &
	\raggedright 15mo heifer &
	\raggedright - &
	\raggedright By LM bull, out of LMx cow; bred by Ivan Scott, Howe, Harray.
	\tabularnewline
\hline
	$1994$ &
	\raggedright R. Cursiter \& Son, Laga, Evie\sindex[exhibitor]{Cursiter, R. \& Son, Laga, Evie} &
	\raggedright 9mo LMx heifer* &
	\raggedright - &
	\raggedright By LM bull Crownhead Gladstone, out of $\frac{3}{4}$ LMx heifer bought from George Muir, Gorn, Shapinsay.
	\tabularnewline
\hline
	$1995$ &
	\raggedright G. T. \& S. Coghill, Muce, Birsay\sindex[exhibitor]{Coghill, G. T. \& S., Muce, Birsay} &
	\raggedright 5mo CHx stot* &
	\raggedright - &
	\raggedright By CH bull Barksore Englander, out of homebred AAxLM cow.
	\tabularnewline
\hline
	$1996$ &
	\raggedright J. \& A. Scott, Howe, Harray\sindex[exhibitor]{Scott, J. \& A., Howe, Harray} &
	\raggedright 17mo CHx heifer* &
	\raggedright - &
	\raggedright By CH bull Seawell Goutte, out of homebred LMx cow.
	\tabularnewline
\hline
	$1997$ &
	\raggedright T. Flett, Appietown, Rendall\sindex[exhibitor]{Flett, T., Appietown, Rendall} &
	\raggedright 8mo LMx stot &
	\raggedright Red McNiell\sindex[beef]{Red McNiell} &
	\raggedright By LM bull Skaill Impact, out of LMx cow.
	\tabularnewline
\hline
	$1998$ &
	\raggedright L. Muir, Midhouse, Harray\sindex[exhibitor]{Muir, L., Midhouse, Harray} &
	\raggedright 16mo LMx heifer &
	\raggedright Lady Tara\sindex[beef]{Lady Tara} &
	\raggedright By LM bull Bedelle Maurice, out of LMx cow; bred by Fersness Farms Eday; dam sired by Shatton Pedro.
	\tabularnewline
\hline
	$1999$ &
	\raggedright L. Muir, Midhouse, Harray\sindex[exhibitor]{Muir, L., Midhouse, Harray} &
	\raggedright 8mo stot* &
	\raggedright - &
	\raggedright By Hillhead Highway, out of LMx cow.
	\tabularnewline
\hline
	$2000$ &
	\raggedright R. Cursiter \& Son, Laga, Evie\sindex[exhibitor]{Cursiter, R. \& Son, Laga, Evie} &
	\raggedright 20mo LMx heifer* &
	\raggedright Laga's Thunderthighs\sindex[beef]{Laga's Thunderthighs} &
	\raggedright By LM bull Crownhead Gladstone out of homebred LMxHxF cow; supreme champion in 2000.
	\tabularnewline
\hline
	$2001$ &
	\multicolumn{4}{c|}{No show due to Foot \& Mouth outbreak.}
	\tabularnewline
\hline
	$2002$ &
	\raggedright L. Muir, Midhouse, Harray\sindex[exhibitor]{Muir, L., Midhouse, Harray} &
	\raggedright 8mo LMx calf &
	\raggedright Harray Topper\sindex[beef]{Harray Topper} &
	\raggedright By LM bull Tanat Otter, out of homebred LMx heifer.
	\tabularnewline
\hline
	$2003$ &
	\raggedright L. Muir, Midhouse, Harray\sindex[exhibitor]{Muir, L., Midhouse, Harray} &
	\raggedright 20mo LMx heifer* &
	\raggedright Steph\sindex[beef]{Steph} &
	\raggedright By LM bull Tanat Otter, out of LMx cow; supreme champion in 2003.
	\tabularnewline
\hline
	$2004$ &
	\raggedright G. T. \& S. Coghill, Muce, Birsay\sindex[exhibitor]{Coghill, G. T. \& S., Muce, Birsay} &
	\raggedright 5yo LMx cow*&
	\raggedright Lady Lou\sindex[beef]{Lady Lou} &
	\raggedright By LM bull Middledale Jeeves, out of homebred CHx cow.
	\tabularnewline
\hline
	$2005$ &
	\raggedright G. T. \& S. Coghill, Muce, Birsay\sindex[exhibitor]{Coghill, G. T. \& S., Muce, Birsay} &
	\raggedright 6yo cow in milk* &
	\raggedright Lady Lou\sindex[beef]{Lady Lou} &
	\raggedright By Middleton Jeeves, out of a homebred CHx cow.
	\tabularnewline
\hline
	$2006$ &
	\raggedright Laga Farms Ltd., Evie\sindex[exhibitor]{Laga Farms Ltd., Evie} &
	\raggedright 7mo stot calf* &
	\raggedright Laga's Goldfinger\sindex[beef]{Laga's Goldfinger} &
	\raggedright By Newstart Unlimited, out of a homebred LMx cow.
	\tabularnewline
\hline
	$2007$ &
	\multicolumn{4}{c|}{No Show due to Foot \& Mouth outbreak.}
	\tabularnewline
\hline
	$2008$ &
	\raggedright G. T. \& S. Coghill, Muce, Birsay\sindex[exhibitor]{Coghill, G. T. \& S., Muce, Birsay} &
	\raggedright 17mo BBx heifer*&
	\raggedright Flash Lady\sindex[beef]{Flash Lady} &
	\raggedright By BB bull Paulern Victor, out of homebred LMx cow; supreme champion.
	\tabularnewline
\hline
	$2009$ &
	\raggedright R. J. Taylor, Brencherhouse, Birsay\sindex[exhibitor]{Taylor, R. J., Brencherhouse, Birsay} &
	\raggedright 2$\frac{1}{2}$yo LMx heifer*&
	\raggedright Ruby\sindex[beef]{Ruby} &
	\raggedright By LM bull Ronick Hawk, out of homebred LMxBB cow; supreme champion.
	\tabularnewline
\hline
\end{longtable}
