\begin{longtable}{|c|p{5.2cm}|p{3cm}|p{3cm}|p{8cm}|}
\hline
	\textbf{Year} &
	\textbf{Exhibitor} &
	\textbf{Champion} &
	\textbf{Name} &
	\textbf{Notes} 
	\tabularnewline
\hline
\endhead
	$1970$ &
	\raggedright ? &
	\raggedright  &
	\raggedright  &
	\raggedright 
	\tabularnewline
\hline
	$1971$ &
	\raggedright T. S. Flett, Millhouse, Harray\sindex[exhibitor]{Flett, T. S., Millhouse, Harray} &
	\raggedright AA heifer calf* &
	\raggedright - &
	\raggedright By Panda of Millhouse, out of homebred cow; dam sired by Jovial Eric of Millhouse; supreme champion in 1971.
	\tabularnewline
\hline
	$1972$ &
	\raggedright ? &
	\raggedright  &
	\raggedright  &
	\raggedright 
	\tabularnewline
\hline
	$1973$ &
	\raggedright J. \& E. Flett, Northbigging, Harray\sindex[exhibitor]{Flett, J. \& E., Northbigging, Harray} &
	\raggedright 4yo cross-bred polled cow in calf &
	\raggedright - &
	\raggedright -
	\tabularnewline
\hline
	$1974$ &
	\raggedright J. \& H. Flett, Boardhouse, Birsay\sindex[exhibitor]{Flett, J. \& E., Northbigging, Harray} &
	\raggedright 6yo cow* &
	\raggedright - &
	\raggedright By Eclipse of Kingshouse.
	\tabularnewline
\hline
	$1975$ &
	\raggedright J. \& E. Flett, Northbigging, Harray\sindex[exhibitor]{Flett, J. \& E., Northbigging, Harray} &
	\raggedright 6yo SHxAA cow in calf* &
	\raggedright - &
	\raggedright By SH bull, out of AA cow; supreme champion in 1973.
	\tabularnewline
\hline
	$1976$ &
	\raggedright R. Flett, Fidge, Twatt\sindex[exhibitor]{Flett, R., Fidge, Twatt} &
	\raggedright 6yo black polled AAxSH cow in milk* &
	\raggedright Stella\sindex[beef]{Stella} &
	\raggedright By Eurite of Inchoch, out of homebred cow; being shown for the first time; supreme champion 1976.
	\tabularnewline
\hline
	$1977$ &
	\raggedright R. Flett, Fidge, Twatt\sindex[exhibitor]{Flett, R., Fidge, Twatt} &
	\raggedright 7yo blue polled cow in calf* &
	\raggedright - &
	\raggedright By Eurite of Inchoch; being shown for the first time; supreme champion in 1977.
	\tabularnewline
\hline
	$1978$ &
	\raggedright J. \& H. Flett, Boardhouse, Birsay\sindex[exhibitor]{Flett, J. \& H., Boardhouse, Birsay} &
	\raggedright 5yo cow in milk* &
	\raggedright Mayflower\sindex[beef]{Mayflower} &
	\raggedright By Eurite of Fidge.
	\tabularnewline
\hline
	$1979$ &
	\raggedright G. R. T. Scarth \& Co, Twatt Farm, Birsay\sindex[exhibitor]{Scarth, G. R. T. \& Co, Twatt Farm, Birsay} ? &
	\raggedright  &
	\raggedright  &
	\raggedright 
	\tabularnewline
\hline
	$1980$ &
	\raggedright V. R. Slater, Breck, Orphir\sindex[exhibitor]{Slater, V. R., Breck, Orphir} &
	\raggedright 2yo SHx heifer in calf* &
	\raggedright - &
	\raggedright By white SH bull.
	\tabularnewline
\hline
	$1981$ &
	\raggedright W. C. Merriman, Laithe, Sandwick\sindex[exhibitor]{Merriman, W. C., Laithe, Sandwick} &
	\raggedright 7yo cow* &
	\raggedright - &
	\raggedright By North Devon bull, out of homebred cross cow; sire bought from Bemersyde, Melrose.
	\tabularnewline
\hline
	$1982$ &
	\raggedright G. R. T. Scarth \& Co, Twatt Farm, Birsay\sindex[exhibitor]{Scarth, G. R. T. \& Co, Twatt Farm, Birsay} &
	\raggedright 7yo SH cow in calf* &
	\raggedright Cavans Waterloo Laura\sindex[beef]{Cavans Waterloo Laura} &
	\raggedright By Newton Talisman, out of Cavans Waterloo Pansy; supreme champion in 1982.
	\tabularnewline
\hline
	$1983$ &
	\raggedright M. C. Wood \& Son, Garson, Sandwick\sindex[exhibitor]{Wood, M. C. \& Son, Garson, Sandwick} &
	\raggedright 6yo AAx cow in milk* &
	\raggedright - &
	\raggedright -
	\tabularnewline
\hline
	$1984$ &
	\raggedright M. C. Wood \& Son, Garson, Sandwick\sindex[exhibitor]{Wood, M. C. \& Son, Garson, Sandwick} &
	\raggedright 5yo AA cow &
	\raggedright Wanerica of Garson\sindex[beef]{Wanerica of Garson} &
	\raggedright By Ashley Jubert Eric, out of Wanerica of Haymount; supreme champion in 1984.
	\tabularnewline
\hline
	$1985$ &
	\raggedright J. \& H. Flett, Boardhouse, Birsay\sindex[exhibitor]{Flett, J. \& H., Boardhouse, Birsay} &
	\raggedright 3yo AAx cow* &
	\raggedright Black Lady\sindex[beef]{Black Lady} &
	\raggedright By CHx bull Ron, out of Orkney bred black cow.
	\tabularnewline
\hline
	$1986$ &
	\raggedright W. G. Kirkpatrick \& Sons, Newhall, Stromness\sindex[exhibitor]{Kirkpatrick, W. G. \& Sons, Newhall, Stromness} &
	\raggedright 4yo AAx cow &
	\raggedright - &
	\raggedright By CHx bull Ron, out of Orkney bred black cow; bred by Boardhouse.
	\tabularnewline
\hline
	$1987$ &
	\raggedright G. T. \& S. Coghill, Muce, Birsay\sindex[exhibitor]{Coghill, G. T. \& S., Muce, Birsay} &
	\raggedright March 1986 CHxAA heifer &
	\raggedright - &
	\raggedright By Bleslack Unique, out of Orkney bred AA cow; supreme champion in 1987.
	\tabularnewline
\hline
	$1988$ &
	\raggedright J. \& H. Flett, Boardhouse, Birsay\sindex[exhibitor]{Flett, J. \& H., Boardhouse, Birsay} &
	\raggedright 2yo AAx heifer in milk &
	\raggedright - &
	\raggedright By Cairnmains Proud Laddie, out of AAx cow.
	\tabularnewline
\hline
	$1989$ &
	\raggedright G. T. \& S. Coghill, Muce, Birsay\sindex[exhibitor]{Coghill, G. T. \& S., Muce, Birsay} &
	\raggedright 15mo CHx heifer* &
	\raggedright - &
	\raggedright By CH bull, out of 5yo SMx cow.
	\tabularnewline
\hline
	$1990$ &
	\raggedright D. W. Sinclair \& Co, Unigarth, Sandwick\sindex[exhibitor]{Sinclair, D. W. \& Co, Unigarth, Sandwick} &
	\raggedright 6yo AA cow* &
	\raggedright Ethnic of Unigarth\sindex[beef]{Ethnic of Unigarth} &
	\raggedright By G V Winton 44L, out of Etana of Unigarth; sire was supreme champion in 1985 \& 1986; supreme champion in 1990.
	\tabularnewline
\hline
	$1991$ &
	\raggedright Messrs Davidson, Skaill Farm, Sandwick\sindex[exhibitor]{Davidson, Messrs, Skaill Farm, Sandwick} &
	\raggedright 3yo AA cow &
	\raggedright Nicks Delia\sindex[beef]{Nicks Delia} &
	\raggedright By DMM Esoteric, out of Tomil Delia; supreme champion in 1991.
	\tabularnewline
\hline
	$1992$ &
	\raggedright Messrs Davidson, Skaill Farm, Sandwick\sindex[exhibitor]{Davidson, Messrs, Skaill Farm, Sandwick} &
	\raggedright 2yo AA heifer in calf* &
	\raggedright Skaill Delia\sindex[beef]{Skaill Delia} &
	\raggedright By Windover Justifier, out of Nicks Delia; reserve best female AA at 1992 Royal Highland Show; supreme champion in 1992 \& 1993.
	\tabularnewline
\hline
	$1993$ &
	\raggedright Messrs Davidson, Skaill Farm, Sandwick\sindex[exhibitor]{Davidson, Messrs, Skaill Farm, Sandwick} &
	\raggedright 3yo AA cow* &
	\raggedright Skaill Delia\sindex[beef]{Skaill Delia} &
	\raggedright 
	\tabularnewline
\hline
	$1994$ &
	\raggedright Messrs Davidson, Skaill Farm, Sandwick\sindex[exhibitor]{Davidson, Messrs, Skaill Farm, Sandwick} &
	\raggedright 4yo cow* &
	\raggedright Skaill Delia\sindex[beef]{Skaill Delia} &
	\raggedright 
	\tabularnewline
\hline
	$1995$ &
	\raggedright Messrs Davidson, Skaill Farm, Sandwick\sindex[exhibitor]{Davidson, Messrs, Skaill Farm, Sandwick} &
	\raggedright 5yo AA cow* &
	\raggedright Skaill Delilah\sindex[beef]{Skaill Delilah} &
	\raggedright By Windover Justifier, out of Nicks Delia; supreme champion in 1994.
	\tabularnewline
\hline
	$1996$ &
	\raggedright Messrs Davidson, Skaill Farm, Sandwick\sindex[exhibitor]{Davidson, Messrs, Skaill Farm, Sandwick} &
	\raggedright 2yo AA heifer* &
	\raggedright Skaill Delia T2\sindex[beef]{Skaill Delia T2} &
	\raggedright By Rito 2100, out of Skaill Delia O2; dam was supreme champion in 1992, \& 1993; supreme champion in 1995.
	\tabularnewline
\hline
	$1997$ &
	\raggedright R. J. Taylor, Brencherhouse, Birsay\sindex[exhibitor]{Taylor, R. J., Brencherhouse, Birsay} &
	\raggedright 2yo black LMx heifer* &
	\raggedright Black Velvet\sindex[beef]{Black Velvet} &
	\raggedright By Shatton Pedro, out of homebred BBxLM cow; supreme champion in 1996.
	\tabularnewline
\hline
	$1998$ &
	\raggedright G. T. \& S. Coghill, Muce, Birsay\sindex[exhibitor]{Coghill, G. T. \& S., Muce, Birsay} &
	\raggedright 5yo CH cow &
	\raggedright New Moan Iris\sindex[beef]{New Moan Iris} &
	\raggedright By Balthayoak Dalesman, out of New Moan Emma; bought from Jim Isbister, New Moan, Harray in October 1997; supreme champion in 1997.
	\tabularnewline
\hline
	$1999$ &
	\raggedright L. Muir, Midhouse, Harray\sindex[exhibitor]{Muir, L., Midhouse, Harray} &
	\raggedright 7yo LM cow &
	\raggedright Poplars Heidi\sindex[beef]{Poplars Heidi} &
	\raggedright By Galbinny Ethan, out of Cowbridge Beauty; bred by Mrs R. Keeling, Poplars Farm, North Stowmarket, Suffolk; bought at annual LM sale, Carlisle, May 1999; supreme champion in 1999.
	\tabularnewline
\hline
	$2000$ &
	\raggedright R. Cursiter \& Son, Laga, Evie\sindex[exhibitor]{Cursiter, R. \& Son, Laga, Evie} &
	\raggedright 20mo LMx heifer* &
	\raggedright Laga's Thunderthighs\sindex[beef]{Laga's Thunderthighs} &
	\raggedright By LM bull Crownhead Gladstone, out of homebred LMxHxF cow; supreme champion in 2000.
	\tabularnewline
\hline
	$2001$ &
	\multicolumn{4}{c|}{No show due to Foot \& Mouth outbreak.}
	\tabularnewline
\hline
	$2002$ &
	\raggedright R. J. Taylor, Brencherhouse, Birsay\sindex[exhibitor]{Taylor, R. J., Brencherhouse, Birsay} &
	\raggedright November 2001 black LMx heifer* &
	\raggedright Taylor's Touch of Class\sindex[beef]{Taylor's Touch of Class} &
	\raggedright By AI bull Ronick Hawk, out of homebred BBxLM cow; supreme champion at 2002 County Show; supreme champion in 2002.
	\tabularnewline
\hline
	$2003$ &
	\raggedright L. Muir, Midhouse, Harray\sindex[exhibitor]{Muir, L., Midhouse, Harray} &
	\raggedright January 2002 LMx heifer* &
	\raggedright Steph\sindex[beef]{Steph} &
	\raggedright By Tanat Otter, out of LMx cow; supreme champion in 2003.
	\tabularnewline
\hline
	$2004$ &
	\raggedright L. Muir, Midhouse, Harray\sindex[exhibitor]{Muir, L., Midhouse, Harray} &
	\raggedright 1yo LMx heifer &
	\raggedright  Evelyn\sindex[beef]{Evelyn} &
	\raggedright By LM bull Ronick Hawk, out of LMxBB cow; bred by G. \& E. Wilson, Howequoy, Holm; bought at Orkney Livestock Association's bull and heifer sale.
	\tabularnewline
\hline
	$2005$ &
	\raggedright G. T. \& S. Coghill, Muce, Birsay\sindex[exhibitor]{Coghill, G. T. \& S., Muce, Birsay} &
	\raggedright 2yo black polled cross heifer in calf &
	\raggedright President's Princess\sindex[beef]{President's Princess} &
	\raggedright Supreme champion at 2005 Dounby Show.
	\tabularnewline
\hline
	$2006$ &
	\raggedright Messrs Davidson, Skaill, Sandwick\sindex[exhibitor]{Davidson, Messrs, Skaill, Sandwick} &
	\raggedright 16mo CH heifer* &
	\raggedright Skaill Abbie\sindex[beef]{Skaill Abbie} &
	\raggedright By Nectragerc, out of Perche; supreme champion, 2006.
	\tabularnewline
\hline
	$2007$ &
	\multicolumn{4}{c|}{No Show due to Foot \& Mouth outbreak.}
	\tabularnewline
\hline
	$2008$ &
	\raggedright G. T. \& S. Coghill, Muce, Birsay\sindex[exhibitor]{Coghill, G. T. \& S., Muce, Birsay} &
	\raggedright 17mo BBx heifer*&
	\raggedright Flash Lady\sindex[beef]{Flash Lady} &
	\raggedright By BB bull Paulern Victor, out of homebred LMx cow; supreme champion.
	\tabularnewline
\hline
	$2009$ &
	\raggedright R. J. Taylor, Brencherhouse, Birsay\sindex[exhibitor]{Taylor, R. J., Brencherhouse, Birsay} &
	\raggedright 2$\frac{1}{2}$yo LMx heifer*&
	\raggedright Ruby\sindex[beef]{Ruby} &
	\raggedright By LM bull Ronick Hawk, out of homebred LMxBB cow; supreme champion.
	\tabularnewline
\hline
\end{longtable}
