\begin{longtable}{|c|p{5.2cm}|p{3cm}|p{3cm}|p{8cm}|}
\hline
	\textbf{Year} &
	\textbf{Exhibitor} &
	\textbf{Champion} &
	\textbf{Name} &
	\textbf{Notes} 
	\tabularnewline
\hline
\endhead
	$1970$ &
	\raggedright T. S. Flett, Millhouse, Harray\sindex[exhibitor]{Flett, T. S., Millhouse, Harray} &
	\raggedright 9yo AA* &
	\raggedright Jovial Eric of Millhouse\sindex[beef]{Jovial Eric of Millhouse} &
	\raggedright By Black Prince of Greenyards; supreme champion at 1969 County Show.
	\tabularnewline
\hline
	$1971$ &
	\raggedright T. S. Flett, Millhouse, Harray\sindex[exhibitor]{Flett, T. S., Millhouse, Harray} &
	\raggedright 2yo AA* &
	\raggedright Everstrike of Millhouse\sindex[beef]{Everstrike of Millhouse} &
	\raggedright By Jovial Eric of Millhouse, out of Emma of Millhouse; supreme champion at 1971 County Show; sired bull sold for 9000gns at Perth.
	\tabularnewline
\hline
	$1972*$ &
	\raggedright T. S. Flett, Millhouse, Harray\sindex[exhibitor]{Flett, T. S., Millhouse, Harray} &
	\raggedright 1yo AA* &
	\raggedright Arnot of Millhouse\sindex[beef]{Arnot of Millhouse} &
	\raggedright By Jovial Eric of Millhouse, out of Annuity of Millhouse.
	\tabularnewline
\hline
	$1973$ &
	\raggedright J. Traill Thomson, Garson, Stromness\sindex[exhibitor]{Traill Thomson, J., Garson, Stromness} &
	\raggedright 4yo SH &
	\raggedright Woodhead Diamond\sindex[beef]{Woodhead Diamond} &
	\raggedright By Denend Golden Miller, out of Woodhead Gold Crocus; red roan.
	\tabularnewline
\hline
	$1974$ &
	\raggedright I. Flett \& Sons, Millhouse, Harray\sindex[exhibitor]{Flett, I. \& Sons, Millhouse, Harray} &
	\raggedright 6yo AA &
	\raggedright Elcho of Millhouse\sindex[beef]{Elcho of Millhouse} &
	\raggedright By Jovial Eric of Millhouse.
	\tabularnewline
\hline
	$1975*$ &
	\raggedright S. \& P. Davidson, Skaill Farm, Sandwick\sindex[exhibitor]{Davidson, S. \& P., Skaill Farm, Sandwick} &
	\raggedright 5yo SH &
	\raggedright Penan Mormond\sindex[beef]{Penan Mormond} &
	\raggedright By Penan King's Coronet; bred by Watt Taylor, Fraserburgh; roan.
	\tabularnewline
\hline
	$1976$ &
	\raggedright I. Flett \& Sons, Millhouse, Harray\sindex[exhibitor]{Flett, I. \& Sons, Millhouse, Harray} &
	\raggedright 4yo AA &
	\raggedright Elmore of Millhouse\sindex[beef]{Elmore of Millhouse} &
	\raggedright By Everstrike of Millhouse; supreme champion at 1974 County show; sire was supreme champion in 1972.
	\tabularnewline
\hline
	$1977$ &
	\raggedright S. \& P. Davidson, Skaill Farm, Sandwick\sindex[exhibitor]{Davidson, S. \& P., Skaill Farm, Sandwick} &
	\raggedright 4yo AA &
	\raggedright Jubilant Eric of Derculich\sindex[beef]{Jubilant Eric of Derculich} &
	\raggedright By Esteem of Balechum; bought at Perth in 1974 for 900gns; supreme champion at 1976 County Show; 4th in class at 1977 Royal Highland.
	\tabularnewline
\hline
	$1978$ &
	\raggedright D. W. Sinclair \& Co, Unigarth, Sandwick\sindex[exhibitor]{Sinclair, D. W. \& Co, Unigarth, Sandwick} &
	\raggedright 5yo AA &
	\raggedright Elprovost of Eastfield\sindex[beef]{Elprovost of Eastfield} &
	\raggedright By Newhouse Proud Prince; bred by T. H. Brewis, Eastfield; bought by Unigarth at Perth 1974 for 1100gns; 1st in class at Perth.
	\tabularnewline
\hline
	$1979*$ &
	\raggedright G. Argo, Kirbister, Birsay\sindex[exhibitor]{Argo, G., Kirbister, Birsay} &
	\raggedright 5yo AA &
	\raggedright Prudant of Durrow Abbey\sindex[beef]{Prudant of Durrow Abbey} &
	\raggedright By Justin 13th of Hillsgrove; bred in Ireland; champion at Dublin show; bought at Perth for 3600gns; purchased by Mr Argo for 2000gns.
	\tabularnewline
\hline
	$1980$ &
	\raggedright S. \& P. Davidson, Skaill Farm, Sandwick\sindex[exhibitor]{Davidson, S. \& P., Skaill Farm, Sandwick} &
	\raggedright 4yo AA &
	\raggedright Eranger of Buchaam\sindex[beef]{Eranger of Buchaam} &
	\raggedright By Blackman of Greenval (Canadian bred); bought privately in Aberdeen, early 1979 from Ogg of Strathallan; supreme champion at 1979 \& 1980 County Shows.
	\tabularnewline
\hline
	$1981*$ &
	\raggedright R. J. \& J. L. Gaudie, Netherskaill, Birsay\sindex[exhibitor]{Gaudie, R. J. \& J. L., Netherskaill, Birsay} &
	\raggedright 5yo HF &
	\raggedright Craebreck Boxer\sindex[beef]{Craebreck Boxer} &
	\raggedright By Free Town Baldwin; bred at Craebreck, Holm.
	\tabularnewline
\hline
	$1982$ &
	\raggedright I. Flett \& Sons, Millhouse, Harray\sindex[exhibitor]{Flett, I. \& Sons, Millhouse, Harray} &
	\raggedright 6yo AA &
	\raggedright Ashley Jewdict Eric\sindex[beef]{Ashley Jewdict Eric} &
	\raggedright By Eroco Bankhead; bought at Perth 1978; 1st in class at Perth.
	\tabularnewline
\hline
	$1983$ &
	\raggedright Messrs Davidson, Skaill \& Messrs Sinclair, Unigarth\sindex[exhibitor]{Davidson, Messrs, Skaill \& Messrs Sinclair, Unigarth}\sindex[exhibitor]{Sinclair, Messrs, Unigarth \& Messrs Davidson, Skaill} &
	\raggedright 3yo AA &
	\raggedright Black Game of Eastfield\sindex[beef]{Black Game of Eastfield} &
	\raggedright By Ballybrennan Profit (Irish bred), out of Blackbird of Southholm (Canadian bred); bought at Perth in February 1982.
	\tabularnewline
\hline
	$1984$ &
	\raggedright I. Flett \& Sons, Millhouse, Harray\sindex[exhibitor]{Flett, I. \& Sons, Millhouse, Harray} &
	\raggedright 6yo AA &
	\raggedright Electrify of Eastfield\sindex[beef]{Electrify of Eastfield} &
	\raggedright By Rivercrest Eston, out of Ethmaree; won championship prizes at 1983 Surrey \& S. England show; bought at Perth October 1983.
	\tabularnewline
\hline
	$1985$ &
	\raggedright Messrs Sinclair, Unigarth \& Messrs Wood, Garson\sindex[exhibitor]{Sinclair, Messrs, Unigarth \& Messrs Wood, Garson}\sindex[exhibitor]{Wood, Messrs, Garson \& Messrs Sinclair, Unigarth} &
	\raggedright 6yo AA &
	\raggedright G V Winton 44L\sindex[beef]{G V Winton 44L} &
	\raggedright By G V Canadian 7J, out of G V Pride 40J; canadian bred, imported into UK by Mr Charles Oag, bought by exhibitors at dispersal sale in 1983 for 4500gns; champion AA at Royal Show in 1986; supreme champion at 1985 \& 1986 County Shows.
	\tabularnewline
\hline
	$1986*$ &
	\raggedright W. G. Kirkpatrick \& Sons, Newhall, Stromness\sindex[exhibitor]{Kirkpatrick, W. G. \& Sons, Newhall, Stromness} &
	\raggedright CH &
	\raggedright Ballieston Universe\sindex[beef]{Ballieston Universe} &
	\raggedright By Wincote Jasper, out of Sway Ninette; bred by W. R. Baillie, Biggings, Toab; sire was supreme champion at 1978 \& 1982 County Show.
	\tabularnewline
\hline
	$1987$ &
	\raggedright I. Craigie \& Co, Hall of Clestrain\sindex[exhibitor]{Craigie, I. \& Co, Hall of Clestrain} &
	\raggedright 4yo SH &
	\raggedright Woodhead Wallace\sindex[beef]{Woodhead Wallace} &
	\raggedright By Newton Timothy, out of Woodhead Fair Clipper; bought at Perth in 1985.
	\tabularnewline
\hline
	$1988$ &
	\raggedright Messrs Davidson, Skaill Farm, Sandwick\sindex[exhibitor]{Davidson, Messrs, Skaill Farm, Sandwick} &
	\raggedright 3yo SH &
	\raggedright Glenisla Warlord\sindex[beef]{Glenisla Warlord} &
	\raggedright By Balmyle Universe, out of Balmyle Genoa 4th; bought at Perth, February 1987 for 2600gns; reserve junior champion at Perth; supreme champion at 1988 County Show.
	\tabularnewline
\hline
	$1989*$ &
	\raggedright Messrs Davidson, Skaill Farm, Sandwick\sindex[exhibitor]{Davidson, Messrs, Skaill Farm, Sandwick} &
	\raggedright 15mo AA* &
	\raggedright Emperor of Skaill\sindex[beef]{Emperor of Skaill} &
	\raggedright By AA/AA Willyboy, out of Erora of Skaill; supreme champion at 1989 County show.
	\tabularnewline
\hline
	$1990$ &
	\raggedright D. W. Sinclair \& Co, Unigarth, Sandwick\sindex[exhibitor]{Sinclair, D. W. \& Co, Unigarth, Sandwick} &
	\raggedright 2yo CH &
	\raggedright Royston Democrat\sindex[beef]{Royston Democrat} &
	\raggedright By Glenleary Attenhall.
	\tabularnewline
\hline
	$1991$ &
	\raggedright Garson Farms, Sandwick\sindex[exhibitor]{Garson Farms, Sandwick} &
	\raggedright 4yo AA &
	\raggedright Larkspur Clipper\sindex[beef]{Larkspur Clipper} &
	\raggedright By Harts Wild Turkey, out of Cerelie of Larkspur.
	\tabularnewline
\hline
	$1992$ &
	\raggedright J. \& N. Isbister, New Moan, Harray\sindex[exhibitor]{Isbister, J. \& N., New Moan, Harray} &
	\raggedright 3yo CH &
	\raggedright Balthayack Dalesman\sindex[beef]{Balthayack Dalesman} &
	\raggedright By Bowerhouse Topper, out of Balthayack Natalia.
	\tabularnewline
\hline
	$1993$ &
	\raggedright G. R. T. Scarth \& Co, Twatt Farm, Birsay\sindex[exhibitor]{Scarth, G. R. T. \& Co, Twatt Farm, Birsay} &
	\raggedright 3yo SH &
	\raggedright Balmyle Dynamo\sindex[beef]{Balmyle Dynamo} &
	\raggedright By Balmyle Action, out of Balmyle Kernel 3rd; bought as calf at foot at Balmyle dispersal sale in 1990.
	\tabularnewline
\hline
	$1994$ &
	\raggedright Messrs Davidson, Skaill Farm, Sandwick\sindex[exhibitor]{Davidson, Messrs, Skaill Farm, Sandwick} &
	\raggedright 1yo LM* &
	\raggedright Skaill Impact\sindex[beef]{Skaill Impact} &
	\raggedright By Bandside Viscount, out of Hampton Duchess.
	\tabularnewline
\hline
	$1995$ &
	\raggedright D. S. Easton, Quoyhalen, Quoyloo\sindex[exhibitor]{Easton, D. S., Quoyhalen, Quoyloo} &
	\raggedright 7yo LG &
	\raggedright Dirnanean Monarch\sindex[beef]{Dirnanean Monarch} &
	\raggedright By Benhar Knight, out of Dirnanean Anna.
	\tabularnewline
\hline
	$1996$ &
	\raggedright Garson Farms, Sandwick\sindex[exhibitor]{Garson Farms, Sandwick} &
	\raggedright 3yo CH* &
	\raggedright Garson Impression\sindex[beef]{Garson Impression} &
	\raggedright By Brampton Ace, out of Gredington Francesca.
	\tabularnewline
\hline
	$1997$ &
	\raggedright G. R. T. Scarth \& Co, Twatt Farm, Birsay\sindex[exhibitor]{Scarth, G. R. T. \& Co, Twatt Farm, Birsay} &
	\raggedright 8yo AA &
	\raggedright Heathlands Buzz Marty\sindex[beef]{Heathlands Buzz Marty} &
	\raggedright By Windover Justifier, out of Heathlands Buzz Melody; supreme champion at 1993 East Mainland show; bought from S. Harcus, Quanterness in 1995.
	\tabularnewline
\hline
	$1998$ &
	\raggedright D. W. Sinclair \& Co, Unigarth, Sandwick\sindex[exhibitor]{Sinclair D. W. \& Co, Unigarth, Sandwick} &
	\raggedright 2yo AA* &
	\raggedright Padre of Unigarth\sindex[beef]{Padre of Unigarth} &
	\raggedright By Windover of Haymount, out of Poppy N21 of Unigarth.
	\tabularnewline
\hline
	$1999$ &
	\raggedright Messrs Davidson, Skaill Farm, Sandwick\sindex[exhibitor]{Davidson, Messrs, Skaill Farm, Sandwick} &
	\raggedright AA calf &
	\raggedright - &
	\raggedright -
	\tabularnewline
\hline
	$2000$ &
	\raggedright G. R. T. Scarth \& Co, Twatt Farm, Birsay\sindex[exhibitor]{Scarth, G. R. T. \& Co, Twatt Farm, Birsay} &
	\raggedright 3yo SH &
	\raggedright Chapleton Masterkey\sindex[beef]{Chapleton Masterkey} &
	\raggedright By Tofts Romany, out of Chapleton Broadhooks H1; bought at Perth February 1999 for joint top price of 3500gns.
	\tabularnewline
\hline
	$2001$ &
	\multicolumn{4}{c|}{No show due to Foot \& Mouth outbreak.}
	\tabularnewline
\hline
	$2002$ &
	\raggedright Messrs Davidson, Skaill Farm, Sandwick\sindex[exhibitor]{Davidson, Messrs, Skaill Farm, Sandwick} &
	\raggedright 1yo AA* &
	\raggedright Skaill Domino\sindex[beef]{Skaill Domino} &
	\raggedright By Nightingale Regent, out of Skaill Diana U8; born April 2001; 4 full brothers sold for 10,000gns, 7,000gns, 5,000gns, and 4,000gns.
	\tabularnewline
\hline
	$2003$ &
	\raggedright Messrs Davidson, Skaill Farm, Sandwick\sindex[exhibitor]{Davidson, Messrs, Skaill Farm, Sandwick} &
	\raggedright 2yo AA* &
	\raggedright Skaill Express\sindex[beef]{Skaill Express} &
	\raggedright By Darling Cruz, out of Skaill Estella.
	\tabularnewline
\hline
	$2004$ &
	\raggedright J. C. Budge \& Co., Burness, Longhope\sindex[exhibitor]{Budge, J. C. \& Co., Burness, Longhope} &
	\raggedright $3\frac{1}{2}$yo SH &
	\raggedright Holmeere Alistair\sindex[beef]{Holmeere Alistair} &
	\raggedright By Chapleton Everest, out of Glenisla Uniclipper.
	\tabularnewline
\hline
	$2005$ &
	\raggedright Messrs Davidson, Skaill Farm, Sandwick\sindex[exhibitor]{Davidson, Messrs, Skaill Farm, Sandwick} &
	\raggedright  &
	\raggedright  &
	\raggedright Continental breed.
	\tabularnewline
\hline
	$2006$ &
	\raggedright L. Spence, Spengar, Sandwick\sindex[exhibitor]{Spence, L., Spengar, Sandwick} &
	\raggedright CH bull &
	\raggedright - &
	\raggedright -
	\tabularnewline
\hline
	$2007$ &
	\multicolumn{4}{c|}{No Show due to Foot \& Mouth outbreak.}
	\tabularnewline
\hline
	$2008$ &
	\raggedright Messrs Davidson, Skaill, Sandwick\sindex[exhibitor]{Davidson, Messrs, Skaill, Sandwick} &
	\raggedright 15mo AA bull* &
	\raggedright Skaill Eric\sindex[beef]{Skaill Eric} &
	\raggedright By Blelack Blackstock, out of Skaill Aurora; champion pure-bred native at County Show.
	\tabularnewline
\hline
	$2009$ &
	\raggedright Laga Farms Ltd., Laga, Evie\sindex[exhibitor]{Laga Farms Ltd., Laga, Evie} &
	\raggedright -&
	\raggedright -&
	\raggedright -
	\tabularnewline
\hline
\end{longtable}
