\begin{longtable}{|c|p{5.2cm}|p{3cm}|p{3cm}|p{8cm}|}
\hline
	\textbf{Year} &
	\textbf{Exhibitor} &
	\textbf{Champion} &
	\textbf{Name} &
	\textbf{Notes} 
	\tabularnewline
\hline
\endhead
	$1936$ &
	\raggedright W. Ritch, Kierfiold, Sandwick\sindex[exhibitor]{Ritch, W., Kierfiold, Sandwick} &
	\raggedright AA bull &
	\raggedright - &
	\raggedright -
	\tabularnewline
\hline
	$1937$ &
	\raggedright R. Learmonth, Saither, Dounby\sindex[exhibitor]{Learmonth, R., Saither, Dounby} &
	\raggedright AA cow &
	\raggedright - &
	\raggedright Dam of champion.
	\tabularnewline
\hline
	$1938$ &
	\raggedright R. Learmonth, Saither, Dounby\sindex[exhibitor]{Learmonth, R., Saither, Dounby} &
	\raggedright AA cow &
	\raggedright - &
	\raggedright -
	\tabularnewline
\hline
	$1939$ &
	\raggedright Mr Ernest W. Flett, Smith's, Dounby\sindex[exhibitor]{Flett, Mr Ernest W., Smith's, Dounby} &
	\raggedright blue cross cow &
	\raggedright - &
	\raggedright -
	\tabularnewline
\hline
	\multicolumn{5}{|c|}{$1940 - 1944 $  No show due to war.}
	\tabularnewline
\hline
	$1945$ &
	\raggedright G. Corrigal, West Ballarat, Harray\sindex[exhibitor]{Corrigal, G., West Ballarat, Harray} &
	\raggedright - &
	\raggedright - &
	\raggedright -
	\tabularnewline
\hline
	$1946$ &
	\raggedright R. Ritch \& Son\sindex[exhibitor]{Ritch, R. \& Son} &
	\raggedright - &
	\raggedright - &
	\raggedright -
	\tabularnewline
\hline
	$1947$ &
	\raggedright Mrs. Spence, Schoolhouse, Birsay\sindex[exhibitor]{Spence, Mrs., Schoolhouse, Birsay} &
	\raggedright - &
	\raggedright - &
	\raggedright -
	\tabularnewline
\hline
	$1948$ &
	\raggedright J. D. Clouston, Quatquoy, Firth\sindex[exhibitor]{Clouston, J. D., Quatquoy, Firth} &
	\raggedright - &
	\raggedright - &
	\raggedright -
	\tabularnewline
\hline
	$1949$ &
	\raggedright J. Corrigal, Geroin,  Harray\sindex[exhibitor]{Corrigal, J., Geroin,  Harray} &
	\raggedright 3yo cross stot &
	\raggedright - &
	\raggedright -
	\tabularnewline
\hline
	$1950$ &
	\raggedright W. Flett\sindex[exhibitor]{Flett, W.} &
	\raggedright - &
	\raggedright - &
	\raggedright -
	\tabularnewline
\hline
	$1951$ &
	\raggedright J. D. Clouston, Quatquoy, Firth\sindex[exhibitor]{Clouston, J. D., Quatquoy, Firth} &
	\raggedright - &
	\raggedright - &
	\raggedright -
	\tabularnewline
\hline
	$1952$ &
	\raggedright Messrs Work, Queenamoan, Sandwick\sindex[exhibitor]{Work, Messrs, Queenamoan, Sandwick} &
	\raggedright SH cow &
	\raggedright - &
	\raggedright Previously best cow or heifer.
	\tabularnewline
\hline
	$1953$ &
	\raggedright Mr G. Corrigal, West Ballarat, Harray\sindex[exhibitor]{Corrigal, Mr. G., West Ballarat, Harray} &
	\raggedright 7yo polled cross cow &
	\raggedright - &
	\raggedright -
	\tabularnewline
\hline
	$1954$ &
	\raggedright J. D. Clouston, North Quatquoy, Firth\sindex[exhibitor]{Clouston, J. D., North Quatquoy, Firth} &
	\raggedright 4yo AAx cow &
	\raggedright - &
	\raggedright By AA bull, out of cross cow.
	\tabularnewline
\hline
	$1955$ &
	\raggedright Flett Bros., Kingshouse, Harray\sindex[exhibitor]{Flett Bros., Kingshouse, Harray} &
	\raggedright 6yo cross polled cow &
	\raggedright - &
	\raggedright Supreme champion in 1956.
	\tabularnewline
\hline
	$1956$ &
	\raggedright W. Flett, North Bigging, Harray\sindex[exhibitor]{Flett, W., North Bigging, Harray} &
	\raggedright Cross cow &
	\raggedright - &
	\raggedright -
	\tabularnewline
\hline
	$1957$ &
	\raggedright W. Flett, North Bigging, Harray\sindex[exhibitor]{Flett, W., North Bigging, Harray} &
	\raggedright Polled cow in calf* &
	\raggedright - &
	\raggedright -
	\tabularnewline
\hline
	$1958$ &
	\raggedright W. Flett, North Bigging, Harray\sindex[exhibitor]{Flett, W., North Bigging, Harray} &
	\raggedright 11yo black polled cross cow in calf* &
	\raggedright - &
	\raggedright By Black Barra of Kingshouse.
	\tabularnewline
\hline
	$1959$ &
	\raggedright Flett Bros., Kingshouse, Harray\sindex[exhibitor]{Flett Bros., Kingshouse, Harray} &
	\raggedright 5yo cross cow &
	\raggedright - &
	\raggedright By a bull bred by Beaton, Mains of Glack; dam was supreme champion in 1956.
	\tabularnewline
\hline
	$1960$ &
	\raggedright W. Ritch, Kierfiold, Sandwick\sindex[exhibitor]{Ritch, W., Kierfiold, Sandwick} &
	\raggedright 8yo blue-grey cross polled cow &
	\raggedright - &
	\raggedright Supreme champion in 1957 \& 1958; supreme champion at 1957 County Show.
	\tabularnewline
\hline
	$1961$ &
	\raggedright D. W. Sinclair, Unigarth, Sandwick\sindex[exhibitor]{Sinclair, D. W., Unigarth, Sandwick} &
	\raggedright 2yo AA heifer &
	\raggedright - &
	\raggedright By Judd Eric of Cardyscraig.
	\tabularnewline
\hline
	$1962$ &
	\raggedright Flett Bros, Kingshouse, Harray\sindex[exhibitor]{Flett Bros, Kingshouse, Harray} &
	\raggedright 8yo cross cow in milk* &
	\raggedright - &
	\raggedright By a Hampton Lucy bull.
	\tabularnewline
\hline
	$1963$ &
	\raggedright M. C. Wood, Garson, Sandwick\sindex[exhibitor]{Wood, M. C., Garson, Sandwick} &
	\raggedright 10yo black polled cross cow &
	\raggedright - &
	\raggedright Supreme champion at 1961 County Show.
	\tabularnewline
\hline
	$1964$ &
	\raggedright R. Flett, Fidge, Twatt\sindex[exhibitor]{Flett, R., Fidge, Twatt} &
	\raggedright 4.5yo AA cow &
	\raggedright Esme of Durris\sindex[beef]{Esme of Durris} &
	\raggedright Bred at Drumoak, bought at autumn sales in Perth, 1963.
	\tabularnewline
\hline
	$1965$ &
	\raggedright T. S. Flett, Millhouse, Harray\sindex[exhibitor]{Flett, T. S., Millhouse, Harray} &
	\raggedright 7yo blue-grey polled cross cow in milk* &
	\raggedright - &
	\raggedright -
	\tabularnewline
\hline
	$1966$ &
	\raggedright W. Learmonth, Saither, Dounby\sindex[exhibitor]{Learmonth, W., Saither, Dounby} &
	\raggedright 2yo cross heifer* &
	\raggedright - &
	\raggedright By a Harviesoun bull.
	\tabularnewline
\hline
	$1967$ &
	\raggedright C. \& S. Meadows, Gairsty, Marwick\sindex[exhibitor]{Meadows, C. \& S., Gairsty, Marwick} &
	\raggedright 1yo SH heifer &
	\raggedright - &
	\raggedright By Arbennie Hyperion; bred by A. J. D. Spence, Cavan, Birsay; given by Mrs. Spence as a wedding present.
	\tabularnewline
\hline
	$1968$ &
	\raggedright M. C. Wood \& Sons, Garson, Sandwick\sindex[exhibitor]{Wood, M. C. \& Sons, Garson, Sandwick} &
	\raggedright 7yo blue-grey polled cow &
	\raggedright - &
	\raggedright -
	\tabularnewline
\hline
	$1969$ &
	\raggedright T. S. Flett, Millhouse, Harray\sindex[exhibitor]{Flett, T. S., Millhouse, Harray} &
	\raggedright - &
	\raggedright - &
	\raggedright -
	\tabularnewline
\hline
	$1970$ &
	\raggedright E. J. Sinclair, Holland, Finstown\sindex[exhibitor]{Sinclair, E. J., Holland, Finstown} &
	\raggedright 8yo SH bull &
	\raggedright Marden Best\sindex[beef]{Marden Best} &
	\raggedright By Findowerie Alls Well, out of Marden Broadhooks 22nd; bred by Sir Peter Greenwell, Woodbridge, Suffolk; bought privately in February 1970 from John M. Sleigh, Tarves, Aberdeenshire; former prize winner at Royal Highland. 
	\tabularnewline
\hline
	$1971$ &
	\raggedright J. \& E. Flett, Northbigging, Harray\sindex[exhibitor]{Flett, J. \& E., Northbigging, Harray} &
	\raggedright 2yo blue heifer &
	\raggedright - &
	\raggedright -
	\tabularnewline
\hline
	$1972$ &
	\raggedright T. S. Flett, Millhouse, Harray\sindex[exhibitor]{Flett, T. S., Millhouse, Harray} &
	\raggedright 1yo AA bull* &
	\raggedright Arnot of Millhouse\sindex[beef]{Arnot of Millhouse} &
	\raggedright By Jovial Eric of Millhouse, out of Annuity of Millhouse.
	\tabularnewline
\hline
	$1973$ &
	\raggedright J. Traill Thomson, Garson, Stromness\sindex[exhibitor]{Traill Thomson, J., Garson, Stromness} &
	\raggedright 4yo SH bull &
	\raggedright Woodhead Diamond\sindex[beef]{Woodhead Diamond} &
	\raggedright By Denend Golden Miller, out of Woodhead Gold Crocus; red roan.
	\tabularnewline
\hline
	$1974$ &
	\raggedright J. \& H. Flett, Boardhouse, Birsay\sindex[exhibitor]{Flett, J. \& H., Boardhouse, Birsay} &
	\raggedright 6yo cow* &
	\raggedright - &
	\raggedright By Eclipse of Kingshouse.
	\tabularnewline
\hline
	$1975$ &
	\raggedright J. \& E. Flett, Northbigging, Harray\sindex[exhibitor]{Flett, J. \& E., Northbigging, Harray} &
	\raggedright 6yo SHxAA cow in calf* &
	\raggedright - &
	\raggedright By SH bull, out of AA cow; supreme champion in 1973.
	\tabularnewline
\hline
	$1976$ &
	\raggedright I. Flett \& Sons, Millhouse, Harray\sindex[exhibitor]{Flett, I. \& Sons, Millhouse, Harray} &
	\raggedright 4yo AA bull &
	\raggedright Elmore of Millhouse\sindex[beef]{Elmore of Millhouse} &
	\raggedright By Everstrike of Millhouse; supreme champion at 1974 County show; sire was supreme champion in 1972.
	\tabularnewline
\hline
	$1977$ &
	\raggedright S. \& P. Davidson, Skaill Farm, Sandwick\sindex[exhibitor]{Davidson, S. \& P., Skaill Farm, Sandwick} &
	\raggedright 4yo AA bull &
	\raggedright Jubilant Eric of Derculich\sindex[beef]{Jubilant Eric of Derculich} &
	\raggedright By Esteem of Balechum; bought at Perth in 1974 for 900gns; supreme champion at 1976 County Show; 4th in class at 1977 Royal Highland.
	\tabularnewline
\hline
	$1978$ &
	\raggedright J. \& H. Flett, Boardhouse, Birsay\sindex[exhibitor]{Flett, J. \& H., Boardhouse, Birsay} &
	\raggedright 5yo cow in milk* &
	\raggedright Mayflower\sindex[beef]{Mayflower} &
	\raggedright By Eurite of Fidge.
	\tabularnewline
\hline
	$1979$ &
	\raggedright G. Argo, Kirbister, Birsay\sindex[exhibitor]{Argo, G., Kirbister, Birsay} &
	\raggedright 5yo AA bull &
	\raggedright Prudant of Durrow Abbey\sindex[beef]{Prudant of Durrow Abbey} &
	\raggedright By Justin 13th of Hillsgrove; bred in Ireland; champion at Dublin show; bought at Perth for 3600gns; purchased by Mr Argo for 2000gns.
	\tabularnewline
\hline
	$1980$ &
	\raggedright V. R. Slater, Breck, Orphir\sindex[exhibitor]{Slater, V. R., Breck, Orphir} &
	\raggedright 2yo SHx heifer in calf* &
	\raggedright - &
	\raggedright By white SH bull.
	\tabularnewline
\hline
	$1981$ &
	\raggedright W. C. Merriman, Laithe, Sandwick\sindex[exhibitor]{Merriman, W. C., Laithe, Sandwick} &
	\raggedright 7yo cow* &
	\raggedright - &
	\raggedright By North Devon bull, out of homebred cross cow; sire bought from Bemersyde, Melrose.
	\tabularnewline
\hline
	$1982$ &
	\raggedright M. C. Wood \& Son, Garson, Sandwick\sindex[exhibitor]{Wood, M. C. \& Son, Garson, Sandwick} &
	\raggedright 5yo AAx cow in milk* &
	\raggedright - &
	\multirow{2}{8cm}{Same animal both years.}
	\tabularnewline
\cline{1-4}
	$1983$ &
	\raggedright M. C. Wood \& Son, Garson, Sandwick\sindex[exhibitor]{Wood, M. C. \& Son, Garson, Sandwick} &
	\raggedright 6yo AAx cow in milk* &
	\raggedright - &
	\tabularnewline
\hline
	$1984$ &
	\raggedright W. C. Merriman, Laithe, Sandwick\sindex[exhibitor]{Merriman, W. C., Laithe, Sandwick} &
	\raggedright 10yo cow in milk* &
	\raggedright - &
	\raggedright By North Devon bull, out of homebred cross cow; sire bought from Bemersyde, Melrose.
	\tabularnewline
\hline
	$1985$ &
	\raggedright J. \& H. Flett, Boardhouse, Birsay\sindex[exhibitor]{Flett, J. \& H., Boardhouse, Birsay} &
	\raggedright 3yo AAx cow* &
	\raggedright Black Lady\sindex[beef]{Black Lady} &
	\raggedright By CHx bull Ron, out of Orkney bred black cow.
	\tabularnewline
\hline
	$1986$ &
	\raggedright W. G. Kirkpatrick \& Sons, Newhall, Stromness\sindex[exhibitor]{Kirkpatrick, W. G. \& Sons, Newhall, Stromness} &
	\raggedright 4yo AAx cow &
	\raggedright - &
	\raggedright By CHx bull Ron, out of Orkney bred black cow; bred by Boardhouse.
	\tabularnewline
\hline
	$1987$ &
	\raggedright J. \& H. Flett, Boardhouse, Birsay\sindex[exhibitor]{Flett, J. \& H., Boardhouse, Birsay} &
	\raggedright 5yo AAx cow* &
	\raggedright Black Lady\sindex[beef]{Black Lady} &
	\raggedright By CHx bull Ron, out of Orkney bred black cow.
	\tabularnewline
\hline
	$1988$ &
	\raggedright J. \& H. Flett, Boardhouse, Birsay\sindex[exhibitor]{Flett, J. \& H., Boardhouse, Birsay} &
	\raggedright 2yo AAx heifer in milk &
	\raggedright - &
	\raggedright By Cairnmains Proud Laddie, out of AAx cow.
	\tabularnewline
\hline
	$1989$ &
	\raggedright G. T. \& S. Coghill, Muce, Birsay\sindex[exhibitor]{Coghill, G. T. \& S., Muce, Birsay} &
	\raggedright 15mo CHx heifer* &
	\raggedright - &
	\raggedright By CH bull, out of 5yo SMx cow.
	\tabularnewline
\hline
	$1990$ &
	\raggedright D. W. Sinclair \& Co, Unigarth, Sandwick\sindex[exhibitor]{Sinclair, D. W. \& Co, Unigarth, Sandwick} &
	\raggedright 2yo CH bull &
	\raggedright Royston Democrat\sindex[beef]{Royston Democrat} &
	\raggedright By Glenleary Attenhall.
	\tabularnewline
\hline
	$1991$ &
	\raggedright Garson Farms, Sandwick\sindex[exhibitor]{Garson Farms, Sandwick} &
	\raggedright 4yo AA bull &
	\raggedright Larkspur Clipper\sindex[beef]{Larkspur Clipper} &
	\raggedright By Harts Wild Turkey, out of Cerelie of Larkspur.
	\tabularnewline
\hline
	$1992$ &
	\raggedright J. \& H. Flett, Boardhouse, Birsay\sindex[exhibitor]{Flett, J. \& H., Boardhouse, Birsay} &
	\raggedright 6yo cow* &
	\raggedright Black Magic\sindex[beef]{Black Magic} &
	\raggedright By Proud Laddie of Cairnmains, out of AAx cow.
	\tabularnewline
\hline
	$1993$ &
	\raggedright S. \& F. Nicolson, Stenaday, Harray\sindex[exhibitor]{Nicolson, S. \& F., Stenaday, Harray} &
	\raggedright 2yo LM heifer in calf &
	\raggedright Mountrock Golden\sindex[beef]{Mountrock Golden} &
	\raggedright By Dali, out of Mountrock Bessie.
	\tabularnewline
\hline
	$1994$ &
	\raggedright Messrs Davidson, Skaill Farm, Sandwick\sindex[exhibitor]{Davidson, Messrs, Skaill Farm, Sandwick} &
	\raggedright 4yo AA cow* &
	\raggedright Skaill Delia\sindex[beef]{Skaill Delia} &
	\raggedright By Windover Justifier, out of Nicks Delia; supreme champion in 1995.
	\tabularnewline
\hline
	$1995$ &
	\raggedright G. T. \& S. Coghill, Muce, Birsay\sindex[exhibitor]{Coghill, G. T. \& S., Muce, Birsay} &
	\raggedright 5mo CHx stot* &
	\raggedright - &
	\raggedright By CH bull Barksore Englander, out of homebred AAxLM cow.
	\tabularnewline
\hline
	$1996$ &
	\raggedright L. Muir, Midhouse, Harray\sindex[exhibitor]{Muir, L., Midhouse, Harray} &
	\raggedright 20mo LMx stot &
	\raggedright - &
	\raggedright By Muirwood Galaxy, out of AAxBB cow; bred by Richard Zawadski, Balfour Mains, Shapinsay.
	\tabularnewline
\hline
	$1997$ &
	\raggedright G. T. \& S. Coghill, Muce, Birsay\sindex[exhibitor]{Coghill, G. T. \& S., Muce, Birsay} &
	\raggedright 2yo LM heifer in calf &
	\raggedright Holly Little Gem\sindex[beef]{Holly Little Gem} &
	\raggedright By Hartside Glen, out of Holly Topas.
	\tabularnewline
\hline
	$1998$ &
	\raggedright D. W. Sinclair \& Co, Unigarth, Sandwick\sindex[exhibitor]{Sinclair, D. W. \& Co, Unigarth, Sandwick} &
	\raggedright 2yo AA bull* &
	\raggedright Padre of Unigarth\sindex[beef]{Padre of Unigarth} &
	\raggedright By Windover of Haymount, out of Poppy N21 of Unigarth.
	\tabularnewline
\hline
	$1999$ &
	\raggedright T. Flett, Appietown, Rendall\sindex[exhibitor]{Flett, T., Appietown, Rendall} &
	\raggedright 18mo LMx heifer* &
	\raggedright Viking Lady\sindex[beef]{Viking Lady} &
	\raggedright By Skaill Impact, out of AA cow.
	\tabularnewline
\hline
	$2000$ &
	\raggedright G. T. \& S. Coghill, Muce, Birsay\sindex[exhibitor]{Coghill, G. T. \& S., Muce, Birsay} &
	\raggedright 7yo CH cow &
	\raggedright New Moan Iris\sindex[beef]{New Moan Iris} &
	\raggedright By Balthayoak Dalesman, out of New Moan Emma; bought from Jim Isbister, New Moan, Harray in October 1997; supreme champion in 1998.
	\tabularnewline
\hline
	$2001$ &
	\multicolumn{4}{c|}{No show due to Foot \& Mouth outbreak.}
	\tabularnewline
\hline
	$2002$ &
	\raggedright L. Muir, Midhouse, Harray\sindex[exhibitor]{Muir, L., Midhouse, Harray} &
	\raggedright 8mo LMx calf &
	\raggedright Harray Topper\sindex[beef]{Harray Topper} &
	\raggedright By LM bull Tanat Otter, out of homebred LMx heifer.
	\tabularnewline
\hline
	$2003$ &
	\raggedright Messrs Davidson, Skaill Farm, Sandwick\sindex[exhibitor]{Davidson, Messrs, Skaill Farm, Sandwick} &
	\raggedright 2yo AA bull* &
	\raggedright Skaill Express\sindex[beef]{Skaill Express} &
	\raggedright By Darling Cruz, out of Skaill Estella.
	\tabularnewline
\hline
	$2004$ &
	\raggedright G. T. \& S. Coghill, Muce, Birsay\sindex[exhibitor]{Coghill, G. T. \& S., Muce, Birsay} &
	\raggedright 5yo LMx cow*&
	\raggedright Lady Lou\sindex[beef]{Lady Lou} &
	\raggedright By LM bull Middledale Jeeves, out of homebred CHx cow.
	\tabularnewline
\hline
	$2005$ &
	\raggedright G. \& C. Flett, Leary, Birsay\sindex[exhibitor]{Flett, G. \& C., Leary, Birsay} &
	\raggedright 10mo LM heifer calf* &
	\raggedright Leary Velvet\sindex[beef]{Leary Velvet} &
	\raggedright By Middledale Perfectionist, out of Leary Randy.
	\tabularnewline
\hline
	$2006$ &
	\raggedright Garson Farms, Garson, Sandwick\sindex[exhibitor]{Garson Farms, Garson, Sandwick} &
	\raggedright 7mo BBx heifer calf* &
	\raggedright - &
	\raggedright By BB bull Beesthorpe Thunderflash, out of LMx cow.
	\tabularnewline
\hline
	$2007$ &
	\multicolumn{4}{c|}{No Show due to Foot \& Mouth outbreak.}
	\tabularnewline
\hline
	$2008$ &
	\raggedright R. J. Taylor, Brencherhouse, Birsay\sindex[exhibitor]{Taylor, R. J., Brencherhouse, Birsay} &	
	\raggedright 17mo LMx heifer* &
	\raggedright Ruby\sindex[beef]{Ruby} &
	\raggedright By LM bull Ronick Hawk, out of homebred LMxBB cow; supreme champion in 2009.
	\tabularnewline
\hline
	$2009$ &
	\raggedright L. Muir, Midhouse, Harray\sindex[exhibitor]{Muir, L., Midhouse, Harray} &	
	\raggedright March-born LMx heifer &
	\raggedright Lynwen\sindex[beef]{Lynwen} &
	\raggedright By LM bull Emslies Auctioneer, out of LMx cow; bred by Harry Emslie.
	\tabularnewline
\hline
\end{longtable}
