\begin{longtable}{|c|p{5.2cm}|p{3cm}|p{3cm}|p{8cm}|}
\hline
	\textbf{Year} &
	\textbf{Exhibitor} &
	\textbf{Champion} &
	\textbf{Name} &
	\textbf{Notes} 
	\tabularnewline
\hline
\endhead
	$1987$ &
	\raggedright W. R. Baillie, Biggings, Toab\sindex[exhibitor]{Baillie, W. R., Biggings, Toab} &
	\raggedright CHV ram lamb* &
	\raggedright - &
	\raggedright By Braeval Banker, out of homebred ewe.
	\tabularnewline
\hline
	$1988$ &
	\raggedright W. G. Kirkpatrick, Newhall, Stromness\sindex[exhibitor]{Kirkpatrick, W. G., Newhall, Stromness} &
	\raggedright 2-shear ewe* &
	\raggedright - &
	\raggedright By Braeval Super Tup, out of dam sired by Breck Trademark; 2nd in class at 1989 Highland Show.
	\tabularnewline
\hline
	$1989$ &
	\raggedright Heidi Hourston, Skelbister, Orphir\sindex[exhibitor]{Hourston, Heidi, Skelbister, Orphir} &
	\raggedright BL ewe lamb &
	\raggedright - &
	\raggedright -
	\tabularnewline
\hline
	$1990$ &
	\raggedright D. \& D. J. Eunson, Halley, Deerness\sindex[exhibitor]{Eunson, D. \& D. J., Halley, Deerness} &
	\raggedright 3yo TX ewe* &
	\raggedright - &
	\raggedright By Fairmount Navigator.
	\tabularnewline
\hline
	$1991$ &
	\raggedright Fraser Balfour, Breck Farm, Rendall\sindex[exhibitor]{Balfour, Fraser, Breck Farm, Rendall} &
	\raggedright CHL ewe &
	\raggedright - &
	\raggedright By Manxman Nessie; bought from Ian Innes' flock in Tullochallum, Dufftown in 1989.
	\tabularnewline
\hline
	$1992$ &
	\raggedright W. G. Kirkpatrick, Newhall, Stromness\sindex[exhibitor]{Kirkpatrick, W. G., Newhall, Stromness} &
	\raggedright CHV ewe lamb &
	\raggedright - &
	\raggedright By Smiddyquoy Super Tup, dam sired by Lynegar Likely Lad.
	\tabularnewline
\hline
	$1993$ &
	\raggedright J. \& E. Wishart, Newbigging, Harray\sindex[exhibitor]{Wishart, J. \& E., Newbigging, Harray} &
	\raggedright CHV shearling ram &
	\raggedright - &
	\raggedright By Bardnaclavan Buccaneer, out of dam sired by Smiddyquoy Haystacks (supreme champion at 1988 Caithness Show).
	\tabularnewline
\hline
	$1994$ &
	\raggedright W. G. Kirkpatrick \& Sons, Newhall, Stromness\sindex[exhibitor]{Kirkpatrick, W. G., Newhall, Stromness} &
	\raggedright CHV shearling ram &
	\raggedright - &
	\raggedright By Bardnackran Buccaneer, out of Lynigar Likely Lad.
	\tabularnewline
\hline
	$1995$ &
	\raggedright Mrs Doris Eunson, Halley, Deerness\sindex[exhibitor]{Eunson, Mrs Doris, Halley, Deerness} &
	\raggedright 4-shear TX ewe* &
	\raggedright - &
	\raggedright By Cambwell Uppercut, out of homebred ewe.
	\tabularnewline
\hline
	$1996$ &
	\raggedright J. Cromarty, Roadside, Toab\sindex[exhibitor]{Cromarty, J., Roadside, Toab} &
	\raggedright 2-shear ram* &
	\raggedright Roadside Titan\sindex[sheep]{Roadside Titan} &
	\raggedright By a Roundhill ram, out of a Balig dam.
	\tabularnewline
\hline
	$1997$ &
	\raggedright Graham Heddle, Westfield, Stromness\sindex[exhibitor]{Heddle, Graham, Westfield, Stromness} &
	\raggedright SF ewe lamb* &
	\raggedright - &
	\raggedright By Muiresk Dazzler, out of homebred ewe sired by Westfield Capstan.
	\tabularnewline
\hline
	$1998$ &
	\raggedright Heidi Hourston, Skelbister, Orphir\sindex[exhibitor]{Hourston, Heidi, Skelbister, Orphir} &
	\raggedright SF ram lamb &
	\raggedright - &
	\raggedright By Muiresk Medallion, out of Roma Romatoswie.
	\tabularnewline
\hline
	$1999$ &
	\raggedright W. S. Sinclair, 25 John Street, Stromness\sindex[exhibitor]{Sinclair, W. S., 25 John Street, Stromness} &
	\raggedright TX gimmer* &
	\raggedright - &
	\raggedright By Haddo Concorde, out of homebred ewe sired by Claircot Yokel (a previous County Show champion).
	\tabularnewline
\hline
	$2000$ &
	\raggedright Heidi Hourston, Skelbister, Orphir\sindex[exhibitor]{Hourston, Heidi, Skelbister, Orphir} &
	\raggedright SF gimmer &
	\raggedright - &
	\raggedright By Muiresk Medallion.
	\tabularnewline
\hline
	$2001$ &
	\multicolumn{4}{c|}{No Show due to Foot \& Mouth outbreak.}
	\tabularnewline
\hline
	$2002$ &
	\raggedright Robbie Rendall, Longhouse, Westray\sindex[exhibitor]{Rendall, Robbie, Longhouse, Westray} &
	\raggedright TX gimmer &
	\raggedright - &
	\raggedright By Thinacres Grendale, out of Ettrick Drambuie.
	\tabularnewline
\hline
	$2003$ &
	\raggedright Sheena Coghill, Muce, Birsay\sindex[exhibitor]{Coghill, Sheena, Muce, Birsay} &
	\raggedright 3yo CHL ewe* &
	\raggedright - &
	\raggedright -
	\tabularnewline
\hline
	$2004$ &
	\raggedright Jim Leitch, Feolquoy, Evie\sindex[exhibitor]{Leitch, Jim, Feolquoy, Evie} &
	\raggedright 6mo TX ewe lamb* &
	\raggedright - &
	\raggedright By Templand Impeccable, out of homebred ewe.
	\tabularnewline
\hline
	$2005$ &
	\raggedright A. \& V. Copland, Overhouse, Harray\sindex[exhibitor]{Copland, A. \& V., Overhouse, Harray} &
	\raggedright TX gimmer* &
	\raggedright - &
	\raggedright By Durrisdeer Instructor, out of homebred ewe by Cambwell Ferrari.
	\tabularnewline
\hline
	$2006$ &
	\raggedright Heidi Hourston, Skelbister, Orphir\sindex[exhibitor]{Hourston, Heidi, Skelbister, Orphir} &
	\raggedright 5-crop SF ewe &
	\raggedright - &
	\raggedright By Muiresk Medallion, out of ewe by Romatoski Roamer.
	\tabularnewline
\hline
	$2007$ &
	\multicolumn{4}{c|}{No Show due to Foot \& Mouth outbreak.}
	\tabularnewline
\hline
		$2008$ &
		\raggedright Heather Hourston, Skelbister, Orphir\sindex[exhibitor]{Hourston, Heather, Skelbister, Orphir} &
		\raggedright 6mo TX ram lamb* &
		\raggedright - &
		\raggedright By Glenside Nibscott, out of a homebred Haddo ewe.
		\tabularnewline
\hline
\end{longtable}
