\begin{longtable}{|c|p{5.2cm}|p{3cm}|p{3cm}|p{8cm}|}
\hline
	\textbf{Year} &
	\textbf{Exhibitor} &
	\textbf{Champion} &
	\textbf{Name} &
	\textbf{Notes} 
	\tabularnewline
\hline
\endhead
	$1998$ &
	\raggedright Messrs Rosie, Quoybond, South Ronaldsay\sindex[exhibitor]{Rosie, Messrs, Quoybond, South Ronaldsay} &
	\raggedright 4yo BB bull* &
	\raggedright Orkney Blues Lucas\sindex[beef]{Orkney Blues Lucas} &
	\raggedright By Greenside Fantastic, out of Waltnewton Hannah.
	\tabularnewline
\hline
	$1999$ &
	\raggedright J. W. Taylor \& Sons, Aikers, South Ronaldsay\sindex[exhibitor]{Taylor, J. W. \& Sons, Aikers, South Ronaldsay} &
	\raggedright - &
	\raggedright - &
	\raggedright -
	\tabularnewline
\hline
	$2000$ &
	\raggedright Messrs Rosie, Quoybond, South Ronaldsay\sindex[exhibitor]{Rosie, Messrs, Quoybond, South Ronaldsay} &
	\raggedright 17mo BB heifer* &
	\raggedright Orkney Blues Rosie\sindex[beef]{Orkney Blues Rosie} &
	\raggedright By Orkney Blues Lucas, out of Orkney Blues Leonora. 
	\tabularnewline
\hline
	$2001$ &
	\multicolumn{4}{c|}{No Show due to Foot \& Mouth outbreak.}
	\tabularnewline
\hline
	$2002$ &
	\multicolumn{4}{c|}{No entries forward.}
	\tabularnewline
\hline
	$2003$ &
	\raggedright A. \& A. Foubister, Netherton, Holm\sindex[exhibitor]{Foubister, A. \& A., Netherton, Holm} &
	\raggedright BB in calf heifer &
	\raggedright - &
	\raggedright -
	\tabularnewline
\hline
	$2004$ &
	\raggedright A. \& A. Foubister, Netherton, Holm\sindex[exhibitor]{Foubister, A. \& A., Netherton, Holm} &
	\raggedright 3yo BB cow in calf &
	\raggedright Ridge Dean Sensation\sindex[beef]{Ridge Dean Sensation} &
	\multirow{2}{8cm}{By Ridge Dean Mahogany, out of Ridge Dean Fergie; bought in 2002 from a Ridge Dean production sale at Carlisle.}
	\tabularnewline
\cline{1-4}
	$2005$ &
	\raggedright A.\& A. Foubister, Netherton, Holm\sindex[exhibitor]{Foubister, A. \& A., Netherton, Holm} &
	\raggedright 4yo BB cow-in-milk &
	\raggedright Ridge Dean Sensation\sindex[beef]{Ridge Dean Sensation}  &
	\tabularnewline
\hline
	$2006$ &
	\raggedright A.\& A. Foubister, Netherton, Holm\sindex[exhibitor]{Foubister, A. \& A., Netherton, Holm} &
	\raggedright 8mo BB bull calf &
	\raggedright Graemshall Alphonse\sindex[beef]{Graemshall Alphonse} &
	\raggedright By Dafydd D'Ochain, out of Ridge Dean Sensation.
	\tabularnewline
\hline
	$2007$ &
	\multicolumn{4}{c|}{No Show due to Foot \& Mouth outbreak.}
	\tabularnewline
\hline
	$2008$ &
	\raggedright Balfour Baillie, Sebay Cottage, Tankerness\sindex[exhibitor]{Baillie, Balfour, Sebay Cottage, Tankerness} &
	\raggedright  3yo BB cow&
	\raggedright Oxcroft Adora\sindex[beef]{Oxcroft Adora} &
	\raggedright By Radar Van Terbeck, out of Oxcroft Nymph; champion BB at East Mainland Show.
	\tabularnewline
\hline
	$2009$ &
	\raggedright K. Eunson, Braebuster Farm, Deerness\sindex[exhibitor]{Eunson, K., Braebuster Farm, Deerness} &
	\raggedright  20mo BB bull&
	\raggedright Denwick Commando\sindex[beef]{Denwick Commando} &
	\raggedright By Bringlee Volkawagon, out of Paulern Preston.
	\tabularnewline
\hline
	$2010$ &
	\raggedright  K. \& M. Eunson, Braebuster Farm, Deerness\sindex[exhibitor]{Eunson, K. \& M., Braebuster Farm, Deerness}&
	\raggedright  2yo BB in-calf-heifer&
	\raggedright Oxcroft Dotty\sindex[beef]{Oxcroft Dotty} &
	\raggedright By Empire D'Ochain, out of Oxcroft Ader.
	\tabularnewline
\hline
	$2011$ &
	\raggedright  &
	\raggedright  &
	\raggedright  &
	\raggedright 
	\tabularnewline
\hline

\end{longtable}
